### 2017-03-16 ms.tex
I began the repository for a KIC 1255 paper on the 61-inch photometry.

% manuscript produces a one-column, double-spaced document:
%\documentclass[12pt,preprint]{aastex}
\documentclass[twocolumn]{aastex61}
%\documentclass[iop]{emulateapj}

% preprint2 produces a double-column, single-spaced document:
%\documentclass[preprint2]{aastex}

%Packages
%\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}

\usepackage{natbib}
\usepackage[caption=false]{subfig}
\usepackage{amsmath,amssymb}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\degree}{$^\circ$}
\newcommand{\vtan}{$V_{tan}$}
\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\msun}{M$_{\sun}$}
\newcommand{\rjup}{R$_{Jup}$}
\newcommand{\ldl}{$\lambda/{\Delta}{\lambda}$}
\newcommand{\lsun}{L$_{\sun}$}
\newcommand{\lbol}{$\log_{10}{L_{bol}/L_{\sun}}$}
\newcommand{\teff}{T$_{eff}$}
\newcommand{\logg}{$\log{g}$}
\newcommand{\fsed}{$f_{sed}$}
\newcommand{\kzz}{$K_{zz}$}
\newcommand{\meth}{CH$_4$}
\newcommand{\wat}{H$_2$O}
\newcommand{\sha}{KIC 1255 b}
\newcommand{\shStar}{KIC 1255}

%\slugcomment{To be submitted to MNRAS}

\shorttitle{KIC 12557548 b Long Term Followup}
\shortauthors{Schlawin et al.}

\begin{document}

\title{Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\correspondingauthor{E. Schlawin}
\email{eas342@email.arizona.edu}

\author{E. Schlawin}
\affiliation{Steward Observatory, Tucson AZ 85721}

\author{Betsy Green?}
\affiliation{Steward Observatory, Tucson AZ 85721}

\author{J. Teske?}
\affiliation{Carnegie Observatories, 813 Santa Barbara Street, Pasadena, CA 91101, USA}

\author{S. Rappaport?}
\affiliation{MIT}

\author{R. van Lieshout?}
\affiliation{Institute of Astronomy - University of Cambridge}

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
\end{abstract}

\keywords{stars: atmospheres -- stars: individual (\objectname{KIC 12557548}) -- stars: variables: general}

\section{Introduction}

\section{Conclusions}\label{sec:conclusions}

\section{Acknowledgements}
Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the Kuiper 61-inch telescope.
MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
This research made use of the \texttt{astropy} package \citep{astropy2013}.

%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

%% The equation environment wil produce a numbered display equation.

%% The \notetoeditor{TEXT} command allows the author to communicate
%% information to the copy editor.  This information will appear as a
%% footnote on the printed copy for the manuscript style file.  Nothing will
%% appear on the printed copy if the preprint or
%% preprint2 style files are used.

%% The eqnarray environment produces multi-line display math. The end of
%% each line is marked with a \\. Lines will be numbered unless the \\
%% is preceded by a \nonumber command.
%% Alignment points are marked by ampersands (&). There should be two
%% ampersands (&) per line.

%% Putting eqnarrays or equations inside the mathletters environment groups
%% the enclosed equations by letter. For instance, the eqnarray below, instead
%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%% LaTeX the paper and look at the output to see the results.

%% This section contains more display math examples, including unnumbered
%% equations (displaymath environment). The last paragraph includes some
%% examples of in-line math featuring a couple of the AASTeX symbol macros.

%% The displaymath environment will produce the same sort of equation as
%% the equation environment, except that the equation will not be numbered
%% by LaTeX.
%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.

%% Included in this acknowledgments section are examples of the
%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
%% argument when you want to print the url directly in the text. Otherwise,
%% use either \url or \anchor, with the HREF as the first argument and the
%% text to be printed in the second.

\acknowledgments

%% To help institutions obtain information on the effectiveness of their
%% telescopes, the AAS Journals has created a group of keywords for telescope
%% facilities. A common set of keywords will make these types of searches
%% significantly easier and more accurate. In addition, they will also be
%% useful in linking papers together which utilize the same telescopes
%% within the framework of the National Virtual Observatory.
%% See the AASTeX Web site at http://aastex.aas.org/
%% for information on obtaining the facility keywords.

%% After the acknowledgments section, use the following syntax and the
%% \facility{} macro to list the keywords of facilities used in the research
%% for the paper.  Each keyword will be checked against the master list during
%% copy editing.  Individual instruments or configurations can be provided 
%% in parentheses, after the keyword, but they will not be verified.

%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc.

\appendix

\section{Original Light Curves}

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\bibliographystyle{apj}
\bibliography{ms}

%\clearpage

%% Use the figure environment and \plotone or \plottwo to include
%% figures and captions in your electronic submission.
%% To embed the sample graphics in
%% the file, uncomment the \plotone, \plottwo, and
%% \includegraphics commands
%%
%% If you need a layout that cannot be achieved with \plotone or
%% \plottwo, you can invoke the graphicx package directly with the
%% \includegraphics command or use \plotfiddle. For more information,
%% please see the tutorial on "Using Electronic Art with AASTeX" in the
%% documentation section at the AASTeX Web site, http://aastex.aas.org/
%%
%% The examples below also include sample markup for submission of
%% supplemental electronic materials. As always, be sure to check
%% the instructions to authors for the journal you are submitting to
%% for specific submissions guidelines as they vary from
%% journal to journal.

%% This example uses \plotone to include an EPS file scaled to
%% 80% of its natural size with \epsscale. Its caption
%% has been written to indicate that additional figure parts will be
%% available in the electronic journal.

%\begin{figure}
%\epsscale{.80}
%\plotone{f1.eps}
%\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
%in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
%\end{figure}

%\clearpage

%% Here we use \plottwo to present two versions of the same figure,
%% one in black and white for print the other in RGB color
%% for online presentation. Note that the caption indicates
%% that a color version of the figure will be available online.
%%

%\begin{figure}
%\plottwo{f2.eps}{f2_color.eps}
%\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
%See the electronic edition of the Journal for a color version 
%of this figure.\label{fig2}}
%\end{figure}

%% This figure uses \includegraphics to scale and rotate the still frame
%% for an mpeg animation.

%\begin{figure}
%\includegraphics[angle=90,scale=.50]{f3.eps}
%\caption{Animation still frame taken from \citet{kim03}.
%This figure is also available as an mpeg
%animation in the electronic edition of the
%{\it Astrophysical Journal}.}
%\end{figure}

%% If you are not including electonic art with your submission, you may
%% mark up your captions using the \figcaption command. See the
%% User Guide for details.
%%
%% No more than seven \figcaption commands are allowed per page,
%% so if you have more than seven captions, insert a \clearpage
%% after every seventh one.

%% Tables should be submitted one per page, so put a \clearpage before
%% each one.

%% Two options are available to the author for producing tables:  the
%% deluxetable environment provided by the AASTeX package or the LaTeX
%% table environment.  Use of deluxetable is preferred.
%%

%% Three table samples follow, two marked up in the deluxetable environment,
%% one marked up as a LaTeX table.

%% In this first example, note that the \tabletypesize{}
%% command has been used to reduce the font size of the table.
%% We also use the \rotate command to rotate the table to
%% landscape orientation since it is very wide even at the
%% reduced font size.
%%
%% Note also that the \label command needs to be placed
%% inside the \tablecaption.

%% This table also includes a table comment indicating that the full
%% version will be available in machine-readable format in the electronic
%% edition.

%% If you use the table environment, please indicate horizontal rules using
%% \tableline, not \hline.
%% Do not put multiple tabular environments within a single table.
%% The optional \label should appear inside the \caption command.

%% If the table is more than one page long, the width of the table can vary
%% from page to page when the default \tablewidth is used, as below.  The
%% individual table widths for each page will be written to the log file; a
%% maximum tablewidth for the table can be computed from these values.
%% The \tablewidth argument can then be reset and the file reprocessed, so
%% that the table is of uniform width throughout. Try getting the widths
%% from the log file and changing the \tablewidth parameter to see how
%% adjusting this value affects table formatting.

%% The \dataset{} macro has also been applied to a few of the objects to
%% show how many observations can be tagged in a table.

%% Tables may also be prepared as separate files. See the accompanying
%% sample file table.tex for an example of an external table file.
%% To include an external file in your main document, use the \input
%% command. Uncomment the line below to include table.tex in this
%% sample file. (Note that you will need to comment out the \documentclass,
%% \begin{document}, and \end{document} commands from table.tex if you want
%% to include it in this document.)

%% \input{table}

%% The following command ends your manuscript. LaTeX will ignore any text
%% that appears after it.

\end{document}

%%
%% End of file `sample.tex'.

### 2017-03-18 ms.tex
I started an observations summary table.
I edited the introduction and some references.

@@
 \section{Introduction}
+The disintegrating planet candidate KIC 12557548 b \citep{rappaport} was the first discovery of a planet candidate causes wildly varying dust obscuration of its host star.
+It is now one of many systems that are proposed to be disintegrating planets that are rapidly losing dust that is seen as obscurations toward the host star.
+
+The Kepler spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
+During this time, the transit depths averaged around (??0.55\%) but varied stochastically from just one 15.7 hour orbit to the next.
+\citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
+There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month.
+
+Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
+\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
+This was evidence that the observations all fell during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
+We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.
+
+\section{Observations}
+We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
+
+\begin{deluxetable*}{lr}
+\tablecaption{List of observations}\label{tab:obsList}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Date} & Comment \\
+UT & \\
+ }
+\startdata
+UT 2016-06-10 & Clouds \\
+UT 2016-06-12 & Good \\
+UT 2016-06-14 & Good \\
+UT 2016-07-12 & Good \\
+UT 2016-07-14 & Good \\
+UT 2016-07-16 & Good \\
+\enddata
+\tablenotetext{}{Obs Summary.}
+\end{deluxetable*}
 
@@
 Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
-Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the Kuiper 61-inch telescope.
+Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the 61-inch Kuiper telescope on Mt Bigelow.
 MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.

### 2017-03-19 ms.tex
I started a summary table of all observations.

@@
 The Kepler spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
-During this time, the transit depths averaged around (??0.55\%) but varied stochastically from just one 15.7 hour orbit to the next.
+During this time, the transit depths averaged around $\sim$0.6\% but varied stochastically from just one 15.7 hour orbit to the next.
 \citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
@@
 \tablehead{
-\colhead{Date} & Comment \\
-UT & \\
+\colhead{Date} &
+\colhead{Comment} \\
+\colhead{UT} & \\
  }
 \startdata
-UT 2016-06-10 & Clouds \\
-UT 2016-06-12 & Good \\
-UT 2016-06-14 & Good \\
-UT 2016-07-12 & Good \\
-UT 2016-07-14 & Good \\
-UT 2016-07-16 & Good \\
+2016-06-10 & Clouds \\
+2016-06-12 & Good \\
+2016-06-14 & Good \\
+2016-07-12 & Good \\
+2016-07-14 & Good \\
+2016-07-16 & Good \\
 \enddata
-\tablenotetext{}{Obs Summary.}
+\tablenotetext{}{Summary of observations in this work.}
+\end{deluxetable*}
+
+\section{Previous Observations}
+
+\begin{deluxetable*}{lrrrr}
+\tablecaption{List of published observations}\label{tab:obsList}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Date Start} &
+\colhead{Date End} &
+\colhead{Observatory} &
+\colhead{Filter} &
+\colhead{Reference(s)} \\
+UT & UT & & & \\
+ }
+\startdata
+2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
+2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
+2013-08-13 & 2013-09-03 & IRTF & $g'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
+2014-08-14 & 2013-09-04 & IRTF & $g'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
+\enddata
+\tablenotetext{}{Summary of published observations of \sha.}
 \end{deluxetable*}

### 2017-03-20 ms.tex
I made a crude initial time series for the 2016-06-12 data using python's photutils.

@@
 \end{deluxetable*}
+
+\section{Time Series}
+
+As an initial start, I created a time series for the night of UT 2016-06-12.
+I used aperture photometry with a source radius of 4 pixels, an inner aperture annulus of 5 pixels and an outer aperture radius of 8 pixels for the background.
+I choose 6 reference stars of similar brightness and which were nearby the source on the CCD.
+I use the \texttt{photutils} python package for the aperture photometry.
+The resulting raw time series can be seen in \ref{fig:initTseries}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{initial_t_series.pdf}
+\caption{Quick raw time series for UT 2016-06-12. No aperture centering was done (there were fixed apertures with time).
+No bias or flat field corrections were applied.}\label{fig:initTseries}
+\end{centering}
+\end{figure}
 

### 2017-03-21 ms.tex
I added an improved time series with aperture corrections applied.

@@
 No bias or flat field corrections were applied.}\label{fig:initTseries}
+\end{centering}
+\end{figure}
+
+The initial time series has huge fluctuations (and even goes negative! due to poor aperture centering at the start).
+I used \texttt{photutils.centroid\_2g} to do 2D Gaussian centroiding to choose the aperture positions to start with.
+Adding a centroiding routine significantly improves the precision as seen in Figure \ref{fig:secTseries}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{second_t_series.pdf}
+\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
+This time aperture centroiding was done.
+No bias or flat field corrections were applied.}\label{fig:secTseries}
 \end{centering}

### 2017-04-06 ms.tex
I added some descriptions of how I did photometric reduction.
I added a figure to show example Gaussian 2d centering.

@@
 
-\section{Previous Observations}
+\subsection{Previous Observations}
 
@@
 
-\section{Time Series}
+\subsection{Photometric Pipeline}
+
+For the photometric reduction, I used the \texttt{ccdproc} package to generate master flat field and bias files.
+I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
 
@@
 I used \texttt{photutils.centroid\_2g} to do 2D Gaussian centroiding to choose the aperture positions to start with.
+The guess position and \texttt{centroid\_2g} position for the target \sha\ are shown in Figure \ref{fig:centroid2g}.
 Adding a centroiding routine significantly improves the precision as seen in Figure \ref{fig:secTseries}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{centering.pdf}
+\caption{The guess position of (750.7,682.4) is shown as a cyan circle. The \texttt{centroid\_2g} position of (749.7,681.1) is shown as a red circle.}\label{fig:centroid2g}
+\end{centering}
+\end{figure}
 
@@
 \end{figure}
+
+\clearpage
 

### 2017-04-16 ms.tex
I added a figure showing the time series with a wider src finding box that allows for pointing wander.

@@
 We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
+Table \ref{tab:obsList} shows a summary of our observations and the UT dates.
+We obtained photometry for 5 nights with good weather on the \sha\ system.
 
@@
 No bias or flat field corrections were applied.}\label{fig:secTseries}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{second_t_series_bias_flat.pdf}
+\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
+This time bias correction, flat field correction and aperture centroiding was done.
+Note that the target, reference stars 2 and 3 have smaller deviations at 0.81 days.}\label{fig:secTseriesBiasFlat}
+\end{centering}
+\end{figure}
+
+It turns out that the large flux excursions in Figure \ref{fig:secTseries} and \ref{fig:secTseriesBiasFlat} are due to some bumps pointing errors and so substantial fractions of flux fall outside the source apertures.
+I solved this problem by increasing the size of the subarray box (from 10 pix width to 18 px) so that the source would be found even if it wanders.
+This results in much smaller flux excursions, as seen in Figure \ref{fig:secTseriesWiderBox}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{second_t_series_wider_box.pdf}
+\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
+Bias correction, flat field correction and aperture centroiding was done.
+The aperture centering (2D Gaussian fits) was done with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
 \end{centering}

### 2017-04-17 ms.tex
I added some examples of different averaging methods for the reference stars.

@@
 The aperture centering (2D Gaussian fits) was done with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
+\end{centering}
+\end{figure}
+
+We considered several ways to do reference summation.
+Under consideration were two choices:
+\begin{itemize}
+	\item How to weight the stars (by flux, equally, variance)?
+	\item Which stars to include in the summation?
+\end{itemize}
+Figure \ref{fig:refSumMethods} shows these 4 combinations of these two choices.
+Clearly reference star 2 adds noise to the time series, but this does not affect the total summation method since it has lower flux.
+When normalizing each time series before summation, this appears to decrease the linear trend in the data.
+In all cases, there is an apparent transit-like feature near JD = 2457551.82.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/reference_method.pdf}
+\caption{Corrected time series for \shStar\ when using different combinations of averaging the reference stars: i) Summing all stars equally ii) Summing the best stars [1,3,4,5,6], iii) Summing the normalized time series of the best stars iv) summing the normalized time series of the best stars.}\label{fig:refSumMethods}
 \end{centering}

### 2017-04-20 ms.tex
I added a short description of which reference stars were selected.

@@
 Bias correction, flat field correction and aperture centroiding was done.
-The aperture centering (2D Gaussian fits) was done with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
+The aperture centering (2D Gaussian fits) was performed with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
 \end{centering}
@@
 \caption{Corrected time series for \shStar\ when using different combinations of averaging the reference stars: i) Summing all stars equally ii) Summing the best stars [1,3,4,5,6], iii) Summing the normalized time series of the best stars iv) summing the normalized time series of the best stars.}\label{fig:refSumMethods}
+\end{centering}
+\end{figure}
+
+Figure \ref{fig:starLabels} shows the reference stars used in the initial analysis.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/st_labels.pdf}
+\caption{\shStar\ at the center and the reference stars used for the photometry.}\label{fig:starLabels}
 \end{centering}

### 2017-04-22 ms.tex
I added postage stamps of zoom-ins where we have apertures and stars.
I added postage stamps to show the centroiding with centroid_2g.

@@
 \caption{\shStar\ at the center and the reference stars used for the photometry.}\label{fig:starLabels}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/postage_stamps.pdf}
+\caption{Postage stamps of apertures used for each source (before centroiding).}\label{fig:starPostageGuess}
+\end{centering}
+\end{figure}
+
+Source centroiding was performed with \texttt{centroid\_2g} within \texttt{photutils} to do 2-D Gaussian fitting. Figure \ref{fig:starPostageCen}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/postage_stamps_centered.pdf}
+\caption{Postage stamps of apertures used for each source, after centroiding with \texttt{centroid\_2g} with the initial guesses shown in Figure \ref{fig:starPostageGuess}.}\label{fig:starPostageCen}
 \end{centering}

### 2017-04-25 ms.tex
Added postage stamps and a reference-corrected time series for UT Aug 12.

@@
 \caption{Postage stamps of apertures used for each source, after centroiding with \texttt{centroid\_2g} with the initial guesses shown in Figure \ref{fig:starPostageGuess}.}\label{fig:starPostageCen}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/postage_stamps_r09px_cen.pdf}
+\caption{Postage stamps of apertures used for each source, after centroiding and using a wider 9 pixel source aperture.}\label{fig:starPostageCenAp9px}
+\end{centering}
+\end{figure}
+
+When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{}.
+The Kepler-based ephemeris indicates a transit at JD = 2457551.830.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
+\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830.}\label{fig:refCorrectedPhotAug12}
 \end{centering}

### 2017-04-26 ms.tex
I completed the table of all observations with some of the results in this paper.

@@
 2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
-2013-08-13 & 2013-09-03 & IRTF & $g'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
-2014-08-14 & 2013-09-04 & IRTF & $g'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
+2013-08-13 & 2013-09-03 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
+2014-08-14 & 2013-09-04 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
+2016-06-12 & 2016-06-12 & Kuiper & Harris R & This Work \\
+2016-07-12 & 2016-07-16 & Kuiper & Harris R & This Work \\
 \enddata
@@
 
-When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{}.
+When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotAug12}.
 The Kepler-based ephemeris indicates a transit at JD = 2457551.830.

### 2017-04-26 ms.tex
Added a time series for Aug 14, 2016 made quickly with the same paramers as Aug 12, 2016.

@@
 \includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
-\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830.}\label{fig:refCorrectedPhotAug12}
+\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830 (UT 2016-06-12).}\label{fig:refCorrectedPhotAug12}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/refcor_aug14.pdf}
+\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14.}\label{fig:refCorrectedPhotAug12}
 \end{centering}

### 2017-04-28 ms.tex
I added descriptions and plots for new times series on UT2016-06-14 and UT2016-07-14.

--- 2017-04-26 ms.tex
@@
 
-When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotAug12}.
+When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotJun12}.
 The Kepler-based ephemeris indicates a transit at JD = 2457551.830.
@@
 \includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
-\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830.}\label{fig:refCorrectedPhotAug12}
+\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830 (UT 2016-06-12).}\label{fig:refCorrectedPhotJun12}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/refcor_aug14.pdf}
+\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14.}\label{fig:refCorrectedPhotJun14}
+\end{centering}
+\end{figure}
+
+I experimented with a whole new set of reference stars (shown in Figure \ref{fig:newRefStars}) to see if they would work better for the time series on UT 2016-06-14.
+I ended up with a very similar time series, as see in Figure \ref{fig:refCorrectedPhotJun14newStars}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/st_labels}
+\caption{A new set of reference stars that matched the source better in terms of brightness.}\label{fig:newRefStars}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/refcor_01}
+\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14, using a new set of reference stars shown in Figure \ref{fig:newRefStars}.}\label{fig:refCorrectedPhotJun14newStars}
+\end{centering}
+\end{figure}
+
+The time series from UT2016-07-14 showed a sharp drop in flux for all stars as seen in Figure \ref{fig:ut2016-07-14clouds}.
+Turns out is clouds, as visible in Figure \ref{fig:ut2016-07-14cloudImg}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/ut2016_07_14_tser_allstars.pdf}
+\caption{All stars' photometry for \shStar\ on UT 2016-07-14.
+There is a sharp drop in flux at 32.88 due to clouds}\label{fig:ut2016-07-14clouds}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
+\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_162.pdf}
+\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_166.pdf}
+\caption{Three example images during a cloud passage.}\label{fig:ut2016-07-14cloudImg}
 \end{centering}

### 2017-04-29 ms.tex
I added summary plots showing photometry from all nights and all stars as well as reference-corrected photometry.

@@
 2016-07-12 & Good \\
-2016-07-14 & Good \\
+2016-07-14 & Mostly clear, some clouds \\
 2016-07-16 & Good \\
@@
 \end{figure}
+
+All nights light curves are shown in Figure \ref{fig:allNightallStar}.
+These are the same reference stars shown in Figure \ref{fig:ut2016-07-14cloudImg}.
+The nights two nights in June, 2016 show greater overall stability than the ones in July, 2016.
+I suspect that this can mostly be explained by moisture and clouds (such as the ones that caused huge drops in flux on UT2016-07-14.
+
+\begin{figure*}
+\begin{centering}
+\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
+\caption{Time series photometry for all stars and all nights nights.
+The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.
+All source radius, background start and background annulus end parameters were 9, 9 and 12 pixels respectively.}\label{fig:allNightallStar}
+\end{centering}
+\end{figure*}
+
+Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ showing transits.
+The expected transit epochs from the ephemeris in \citep{vanWerkhoven2014} are shown for reference.
+Typical uncertainties for the Kepler ephemeris are $\sim$ 1 minute at these dates (considering only the uncertainty in period since the transit center is ill-defined).
+The ``transit duration'' from Kepler light curves is around 0.05 days, which is consistent with these transit durations.
+
+\begin{figure*}
+\begin{centering}
+\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
+\caption{Reference-corrected time series photometry \shStar\ for all nights.
+The expected transit epochs from the Kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
+Transits are clearly visible for all five nights except for UT2016-06-14.}\label{fig:allNightrefCorrect}
+\end{centering}
+\end{figure*}
 

### 2017-05-11 ms.tex
I now show average SC Kepler light curves on top of the individual transits.
Added more background and references to the intro.

@@
 \section{Introduction}
-The disintegrating planet candidate KIC 12557548 b \citep{rappaport} was the first discovery of a planet candidate causes wildly varying dust obscuration of its host star.
-It is now one of many systems that are proposed to be disintegrating planets that are rapidly losing dust that is seen as obscurations toward the host star.
+The disintegrating planet candidate KIC 12557548 b (hereafter \sha) \citep{rappaport} was the first discovery of a planet candidate causes stochastically varying dust obscuration of its host star.
+It is now one of many systems that have stochastically varying transit depths.
+The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and can have wavelength-dependent transmission predicted for dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
+Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still multiple explanations: KIC 8462852 (ie.
+Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
+
+Observational evidence from the \shStar\ system puts constraints on the planet candidate on the system.
+Radial velocity velocity variations of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
+There is no detection of secondary eclipses of \sha\ $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km.
+The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
+are proposed to be disintegrating planets that are rapidly losing dust that is seen as obscurations toward the host star.
 
@@
 The expected transit epochs from the Kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
+We also show the average Short Cadence Kepler light curves for each of the transit events for comparison with the average.
 Transits are clearly visible for all five nights except for UT2016-06-14.}\label{fig:allNightrefCorrect}

### 2017-05-13 ms.tex
I adjusted the intro to describe some of the attributes of the KIC 1255 light curve.

@@
 \section{Introduction}
-The disintegrating planet candidate KIC 12557548 b (hereafter \sha) \citep{rappaport} was the first discovery of a planet candidate causes stochastically varying dust obscuration of its host star.
-It is now one of many systems that have stochastically varying transit depths.
-The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and can have wavelength-dependent transmission predicted for dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
+\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
+The KIC 12557548 (hereafter \shStar) light curve exhibited periodic flux dips with a period of 0.653 days.
+What was highly unusual about \shStar\ was that the flux dips were neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
+The variations in amplitude are highly stochastic and unpredictable from one event to the next 0.653 days later.
+This indicates the creation and destruction of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
+These variable dips are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
+The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.
+
+The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
+Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
+
 Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still multiple explanations: KIC 8462852 (ie.

### 2017-05-15 ms.tex
I added a few sentences on the Subaru analysis to parallel the IRAF reduction I'm doing.

@@
 
+\section{Subaru Analysis}
+
+The host star \shStar\ has been characterized by both photometry and spectroscopy.
+In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
+High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara}
+We decided to re-visit the high resolution spectrum from \citet{kawahara} by downloading the raw data from the Subaru SMOKA database.
+
 \section{Conclusions}\label{sec:conclusions}

### 2017-05-16 ms.tex
I added some more details on the IRAF reduction of the HDS spectrum.

--- 2017-05-13 ms.tex
@@
 
+\section{Subaru Analysis}
+
+The host star \shStar\ has been characterized by both photometry and spectroscopy.
+In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
+High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
+We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.
+
+We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
+Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
+We applied bad pixel masks and bias files to each CCD.
+
 \section{Conclusions}\label{sec:conclusions}

### 2017-05-18 ms.tex
I added some updates to the intro and observation summary tables.

@@
 \citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
-The KIC 12557548 (hereafter \shStar) light curve exhibited periodic flux dips with a period of 0.653 days.
+KIC 12557548's (hereafter \shStar's) light curve exhibited periodic flux dips with a period of 0.653 days.
 What was highly unusual about \shStar\ was that the flux dips were neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
 The variations in amplitude are highly stochastic and unpredictable from one event to the next 0.653 days later.
-This indicates the creation and destruction of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
+This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
 These variable dips are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
@@
 
-Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still multiple explanations: KIC 8462852 (ie.
+Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie.
 Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
+KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
+RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planets.
+RIK-210 may have accreting material that causes variable extinction.
+PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
 
@@
 Radial velocity velocity variations of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
-There is no detection of secondary eclipses of \sha\ $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km.
+There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km.
 The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
-are proposed to be disintegrating planets that are rapidly losing dust that is seen as obscurations toward the host star.
 
@@
 \citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
-This was evidence that the observations all fell during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
+This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
 We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.
 
-\section{Observations}
-We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
-Table \ref{tab:obsList} shows a summary of our observations and the UT dates.
-We obtained photometry for 5 nights with good weather on the \sha\ system.
-
-\begin{deluxetable*}{lr}
+\begin{deluxetable}{lr}
 \tablecaption{List of observations}\label{tab:obsList}
@@
 2016-06-10 & Clouds \\
-2016-06-12 & Good \\
-2016-06-14 & Good \\
-2016-07-12 & Good \\
-2016-07-14 & Mostly clear, some clouds \\
-2016-07-16 & Good \\
+2016-06-12 & Clear \\
+2016-06-14 & Clear \\
+2016-07-12 & Clear \\
+2016-07-14 & Mostly clear \\
+2016-07-16 & Clear \\
 \enddata
-\tablenotetext{}{Summary of observations in this work.}
-\end{deluxetable*}
+\tablenotetext{}{Summary of observations and conditions in this work.}
+\end{deluxetable}
+
+\section{Observations}
+We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
+Table \ref{tab:obsList} shows a summary of our observations and the UT dates.
+We obtained photometry for 5 nights with good weather on the \sha\ system.
 
@@
 \enddata
-\tablenotetext{}{Summary of published observations of \sha.}
+\tablenotetext{}{Summary of published photometric observations of \sha.}
 \end{deluxetable*}
@@
 Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
-We applied bad pixel masks and bias files to each CCD.
+We applied bad pixel masks and bias files to each CCD separately.
 

### 2017-05-26 ms.tex
added an explanation of how the spectral tracers were found.
I added some quick spectrum of an initial reduction of one KIC 1255 file.

@@
 We applied bad pixel masks and bias files to each CCD separately.
+Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.
+
+The 2013 HDS data for KIC 1255 display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
+The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
+For wavelength identification, a Thorium Argon reference is used.
+The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
+\caption{Example spectrum of \shStar\ near the Na D line.
+There are many bad pixels.}\label{fig:naDline}
+\end{centering}
+\end{figure}
 

### 2017-05-27 ms.tex
added plots of the Mg triplet analysis compared with some HIGHRES models.

@@
 \includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Na D line.
+\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
 There are many bad pixels.}\label{fig:naDline}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
+\caption{Example spectrum of \shStar\ near the Mg triplet.
+First, the points above 2.0 are flagged as bad pixels and interpolated over.
+Second, a convolution kernel is applied and the spectrum is compared to HIGHRES models.}\label{fig:mgTriplet}
 \end{centering}

### 2017-05-27 ms.tex
added more description of the high resolution spectra.

@@
 
-The 2013 HDS data for KIC 1255 display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
+The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
 The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
 For wavelength identification, a Thorium Argon reference is used.
-The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
+(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
+The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
+The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
+The final rms in this wavelength solution is 0.0021 $\AA$.
+
+After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the Mg Triplet (Figure \ref{fig:mgTriplet}).
+The Mg triplet is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
+\citet{kawahara2013starspots} find a log(g) = 3.9 $\pm$ 0.2, whereas \citet{rappaport} find a log(g)=4.63.
+To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
+Also, we interpolated over any pixels above a normalized flux of 2.0 in Figure \ref{fig:mgTriplet} (top).
+Then, we convolve with a Gaussian kernel with a standard deviation of 6 pixels.
 
@@
 
+\clearpage
 \section{Conclusions}\label{sec:conclusions}

### 2017-05-29 ms.tex
added more explanation of the high res spectrum analysis and added the summary table from Van Lieshout et al. 2016.

@@
 
-\section{Subaru Analysis}
+\section{Stellar Characterization}
 
+\subsection{Previous Observations}
 The host star \shStar\ has been characterized by both photometry and spectroscopy.
+Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
 In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
 High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
+\citet{vanlieshout2016kic1255} analyze the light curve with a dust model and find a constraint on the semi-major axis which, in term, constraints the density of the star.
+\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
+
+\begin{deluxetable*}{lrrrr}
+\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}\label{tab:stellObsParams}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Reference} &
+\colhead{$ T_{eff,*} $} &
+\colhead{$\log(g)$} &
+\colhead{Evolutionary Status} &
+\colhead{Method} \\
+ & (K) & $\log$(cm s$^{-2}$) & & \\
+ }
+\startdata
+  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
+  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
+  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
+  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
+\enddata
+\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}
+\end{deluxetable*}
+
+\subsection{Observation}
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
+\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
+There are many bad pixels.}\label{fig:naDlines}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
+\caption{Example spectrum of \shStar\ near the Mg triplet.
+{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
+The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
+{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
+The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
+\end{centering}
+\end{figure}
+
 We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.
-
 We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
@@
 The final rms in this wavelength solution is 0.0021 $\AA$.
+After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the
 
-After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the Mg Triplet (Figure \ref{fig:mgTriplet}).
-The Mg triplet is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
+\subsection{Comparison to Templates}
+
+The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
 \citet{kawahara2013starspots} find a log(g) = 3.9 $\pm$ 0.2, whereas \citet{rappaport} find a log(g)=4.63.
@@
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
-There are many bad pixels.}\label{fig:naDline}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Mg triplet.
-First, the points above 2.0 are flagged as bad pixels and interpolated over.
-Second, a convolution kernel is applied and the spectrum is compared to HIGHRES models.}\label{fig:mgTriplet}
-\end{centering}
-\end{figure}
+The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a much closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES.
+The only mismatch between the 4500 K and log(g)=4.5 model and the HDS spectrum for \shStar\ is the overall line strengths.
 

### 2017-05-29 ms.tex
discussed line ratios in figure caption.

@@
 {\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
-The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
+The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
 \end{centering}

### 2017-05-29 ms.tex
A few more notes on the high res spectrum of KIC 1255.

@@
 \citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
+They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
+If true, this would suggest that high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
 
-\begin{deluxetable*}{lrrrr}
+\begin{deluxetable*}{lcrrr}
 \tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}\label{tab:stellObsParams}

### 2017-05-29 ms.tex
started eliminating material that will go in the supplement. Also added postage stamps for the final reference star collection.

@@
 
-For the photometric reduction, I used the \texttt{ccdproc} package to generate master flat field and bias files.
+For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
 I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
-
-As an initial start, I created a time series for the night of UT 2016-06-12.
-I used aperture photometry with a source radius of 4 pixels, an inner aperture annulus of 5 pixels and an outer aperture radius of 8 pixels for the background.
-I choose 6 reference stars of similar brightness and which were nearby the source on the CCD.
-I use the \texttt{photutils} python package for the aperture photometry.
-The resulting raw time series can be seen in \ref{fig:initTseries}.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{initial_t_series.pdf}
-\caption{Quick raw time series for UT 2016-06-12. No aperture centering was done (there were fixed apertures with time).
-No bias or flat field corrections were applied.}\label{fig:initTseries}
-\end{centering}
-\end{figure}
-
-The initial time series has huge fluctuations (and even goes negative! due to poor aperture centering at the start).
-I used \texttt{photutils.centroid\_2g} to do 2D Gaussian centroiding to choose the aperture positions to start with.
-The guess position and \texttt{centroid\_2g} position for the target \sha\ are shown in Figure \ref{fig:centroid2g}.
-Adding a centroiding routine significantly improves the precision as seen in Figure \ref{fig:secTseries}.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{centering.pdf}
-\caption{The guess position of (750.7,682.4) is shown as a cyan circle. The \texttt{centroid\_2g} position of (749.7,681.1) is shown as a red circle.}\label{fig:centroid2g}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{second_t_series.pdf}
-\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
-This time aperture centroiding was done.
-No bias or flat field corrections were applied.}\label{fig:secTseries}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{second_t_series_bias_flat.pdf}
-\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
-This time bias correction, flat field correction and aperture centroiding was done.
-Note that the target, reference stars 2 and 3 have smaller deviations at 0.81 days.}\label{fig:secTseriesBiasFlat}
-\end{centering}
-\end{figure}
-
-It turns out that the large flux excursions in Figure \ref{fig:secTseries} and \ref{fig:secTseriesBiasFlat} are due to some bumps pointing errors and so substantial fractions of flux fall outside the source apertures.
-I solved this problem by increasing the size of the subarray box (from 10 pix width to 18 px) so that the source would be found even if it wanders.
-This results in much smaller flux excursions, as seen in Figure \ref{fig:secTseriesWiderBox}.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{second_t_series_wider_box.pdf}
-\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
-Bias correction, flat field correction and aperture centroiding was done.
-The aperture centering (2D Gaussian fits) was performed with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
-\end{centering}
-\end{figure}
-
-We considered several ways to do reference summation.
-Under consideration were two choices:
-\begin{itemize}
-	\item How to weight the stars (by flux, equally, variance)?
-	\item Which stars to include in the summation?
-\end{itemize}
-Figure \ref{fig:refSumMethods} shows these 4 combinations of these two choices.
-Clearly reference star 2 adds noise to the time series, but this does not affect the total summation method since it has lower flux.
-When normalizing each time series before summation, this appears to decrease the linear trend in the data.
-In all cases, there is an apparent transit-like feature near JD = 2457551.82.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/reference_method.pdf}
-\caption{Corrected time series for \shStar\ when using different combinations of averaging the reference stars: i) Summing all stars equally ii) Summing the best stars [1,3,4,5,6], iii) Summing the normalized time series of the best stars iv) summing the normalized time series of the best stars.}\label{fig:refSumMethods}
-\end{centering}
-\end{figure}
-
-Figure \ref{fig:starLabels} shows the reference stars used in the initial analysis.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/st_labels.pdf}
-\caption{\shStar\ at the center and the reference stars used for the photometry.}\label{fig:starLabels}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/postage_stamps.pdf}
-\caption{Postage stamps of apertures used for each source (before centroiding).}\label{fig:starPostageGuess}
-\end{centering}
-\end{figure}
-
-Source centroiding was performed with \texttt{centroid\_2g} within \texttt{photutils} to do 2-D Gaussian fitting. Figure \ref{fig:starPostageCen}.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/postage_stamps_centered.pdf}
-\caption{Postage stamps of apertures used for each source, after centroiding with \texttt{centroid\_2g} with the initial guesses shown in Figure \ref{fig:starPostageGuess}.}\label{fig:starPostageCen}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/postage_stamps_r09px_cen.pdf}
-\caption{Postage stamps of apertures used for each source, after centroiding and using a wider 9 pixel source aperture.}\label{fig:starPostageCenAp9px}
-\end{centering}
-\end{figure}
-
-When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotJun12}.
-The Kepler-based ephemeris indicates a transit at JD = 2457551.830.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
-\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830 (UT 2016-06-12).}\label{fig:refCorrectedPhotJun12}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/refcor_aug14.pdf}
-\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14.}\label{fig:refCorrectedPhotJun14}
-\end{centering}
-\end{figure}
-
-I experimented with a whole new set of reference stars (shown in Figure \ref{fig:newRefStars}) to see if they would work better for the time series on UT 2016-06-14.
-I ended up with a very similar time series, as see in Figure \ref{fig:refCorrectedPhotJun14newStars}.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/st_labels}
-\caption{A new set of reference stars that matched the source better in terms of brightness.}\label{fig:newRefStars}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/refcor_01}
-\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14, using a new set of reference stars shown in Figure \ref{fig:newRefStars}.}\label{fig:refCorrectedPhotJun14newStars}
-\end{centering}
-\end{figure}
-
-The time series from UT2016-07-14 showed a sharp drop in flux for all stars as seen in Figure \ref{fig:ut2016-07-14clouds}.
-Turns out is clouds, as visible in Figure \ref{fig:ut2016-07-14cloudImg}.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/ut2016_07_14_tser_allstars.pdf}
-\caption{All stars' photometry for \shStar\ on UT 2016-07-14.
-There is a sharp drop in flux at 32.88 due to clouds}\label{fig:ut2016-07-14clouds}
-\end{centering}
-\end{figure}
 
@@
 \includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
-\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_162.pdf}
-\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_166.pdf}
-\caption{Three example images during a cloud passage.}\label{fig:ut2016-07-14cloudImg}
+\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
+\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
+The reference stars were chosen to have similar count levels as the source. 
+}\label{fig:ut2016-07-14cloudImg}
 \end{centering}

### 2017-05-29 supplement.tex
started deleting material already present in the paper.

--- 2017-05-29 ms.tex
@@
 \section{Introduction}
-\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
-KIC 12557548's (hereafter \shStar's) light curve exhibited periodic flux dips with a period of 0.653 days.
-What was highly unusual about \shStar\ was that the flux dips were neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
-The variations in amplitude are highly stochastic and unpredictable from one event to the next 0.653 days later.
-This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
-These variable dips are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
-The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.
-
-The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
-Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
-
-Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie.
-Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
-KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
-RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planets.
-RIK-210 may have accreting material that causes variable extinction.
-PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
-
-Observational evidence from the \shStar\ system puts constraints on the planet candidate on the system.
-Radial velocity velocity variations of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
-There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km.
-The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
-
-The Kepler spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
-During this time, the transit depths averaged around $\sim$0.6\% but varied stochastically from just one 15.7 hour orbit to the next.
-\citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
-There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month.
-
-Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
-\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
-This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
-We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.
-
-\begin{deluxetable}{lr}
-\tablecaption{List of observations}\label{tab:obsList}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Date} &
-\colhead{Comment} \\
-\colhead{UT} & \\
- }
-\startdata
-2016-06-10 & Clouds \\
-2016-06-12 & Clear \\
-2016-06-14 & Clear \\
-2016-07-12 & Clear \\
-2016-07-14 & Mostly clear \\
-2016-07-16 & Clear \\
-\enddata
-\tablenotetext{}{Summary of observations and conditions in this work.}
-\end{deluxetable}
+Supplementary Material/Notes for the main paper
 
 \section{Observations}
-We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
-Table \ref{tab:obsList} shows a summary of our observations and the UT dates.
-We obtained photometry for 5 nights with good weather on the \sha\ system.
-
-\subsection{Previous Observations}
-
-\begin{deluxetable*}{lrrrr}
-\tablecaption{List of published observations}\label{tab:obsList}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Date Start} &
-\colhead{Date End} &
-\colhead{Observatory} &
-\colhead{Filter} &
-\colhead{Reference(s)} \\
-UT & UT & & & \\
- }
-\startdata
-2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
-2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
-2013-08-13 & 2013-09-03 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
-2014-08-14 & 2013-09-04 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
-2016-06-12 & 2016-06-12 & Kuiper & Harris R & This Work \\
-2016-07-12 & 2016-07-16 & Kuiper & Harris R & This Work \\
-\enddata
-\tablenotetext{}{Summary of published photometric observations of \sha.}
-\end{deluxetable*}
 

### 2017-05-30 ms.tex
added more analysis of spectral lines and a comparison between 2013 and 2015 after some suggestions from Johanna.

@@
 \clearpage
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec_interp.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec.pdf}
+\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
+There are many bad pixels, which are preliminarily discarded for fluxes above 1.25.
+These are not fully removed in the convolved spectrum.}\label{fig:naDlines}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
+\caption{Example spectrum of \shStar\ near the Mg triplet.
+{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
+The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
+{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
+The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
+\end{centering}
+\end{figure}
 
 \section{Stellar Characterization}
-
 \subsection{Previous Observations}
-The host star \shStar\ has been characterized by both photometry and spectroscopy.
-Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
-In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
-High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
-\citet{vanlieshout2016kic1255} analyze the light curve with a dust model and find a constraint on the semi-major axis which, in term, constraints the density of the star.
-\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
-They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
-If true, this would suggest that high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
 
@@
 
-\subsection{Observation}
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
-There are many bad pixels.}\label{fig:naDlines}
-\end{centering}
-\end{figure}
+The host star \shStar\ has been characterized by both photometry and spectroscopy.
+Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
+In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
+High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
+\citet{vanlieshout2016kic1255} analyze the light curve with a dust model and find a constraint on the semi-major axis which, in term, constraints the density of the star.
+\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
+They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
+If true, this would suggest that high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Mg triplet.
-{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
-The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
-{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
-The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
-\end{centering}
-\end{figure}
+\subsection{Observations}
 
@@
 
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/out_HDSA00094087.pdf}
+\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/HDSA00111345.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
+\caption{Spectra images from 2013 versus 2015. The PSF profile (bottom panel) is much larger in 2013 is more difficult to fit with a tracing function.}\label{fig:mgTriplet}
+\end{centering}
+\end{figure}
+
 The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
+Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
+The wider longer slit (2 $\times$ 30 mm) used in 2013 versus the narrower one in 2015 produce very different PSFs.
 The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
@@
 The only mismatch between the 4500 K and log(g)=4.5 model and the HDS spectrum for \shStar\ is the overall line strengths.
+
+\begin{figure}{!hbtp}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/CaI6162_spec.pdf}
+\caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:mgTriplet}
+\end{centering}
+\end{figure}
 

### 2017-05-31 ms.tex
added a few fixes details and clarifications about HDS spectra.

@@
 {\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
-The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
+The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios but not the strength of the features.}\label{fig:mgTriplet}
 \end{centering}
@@
 We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.
-We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
+We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
 Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
@@
 \includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
-\caption{Spectra images from 2013 versus 2015. The PSF profile (bottom panel) is much larger in 2013 is more difficult to fit with a tracing function.}\label{fig:mgTriplet}
+\caption{Spectra images from 2013 versus 2015. The PSF profile (bottom panel) is much larger in 2013 is more difficult to fit with a tracing function.}\label{fig:prof2013vs2015}
 \end{centering}
@@
 Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
-The wider longer slit (2 $\times$ 30 mm) used in 2013 versus the narrower one in 2015 produce very different PSFs.
+The wider longer slit (2 $\times$ 30 mm) used in 2013 versus the narrower one in 2015 (0.3 $\times$ 3.5 mm) produce very different PSFs.
 The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
@@
 
-The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a much closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES.
-The only mismatch between the 4500 K and log(g)=4.5 model and the HDS spectrum for \shStar\ is the overall line strengths.
+The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES, but not the line strengths.
 
-\begin{figure}{!hbtp}
+\begin{figure}[!hbtp]
 \begin{centering}

### 2017-06-01 ms.tex
updated several changes now that Hajime Kawahara explained that an image slicer was used.

@@
 \includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
-\caption{Spectra images from 2013 versus 2015. The PSF profile (bottom panel) is much larger in 2013 is more difficult to fit with a tracing function.}\label{fig:prof2013vs2015}
+\caption{Spectra images from 2013 versus 2015.
+The PSF profile (bottom panel) is much wider in 2013 because an image slicer creates 3 traces for the one star.
+In 2015, a narrow slit is used instead.}\label{fig:prof2013vs2015}
 \end{centering}
@@
 
-The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
+The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
 Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
-The wider longer slit (2 $\times$ 30 mm) used in 2013 versus the narrower one in 2015 (0.3 $\times$ 3.5 mm) produce very different PSFs.
-The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
+The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm) has a sharper PSF and and is easier to trace.
+The 2013 data was taken with an image slicer and a wider ((2 $\times$ 30 mm)) slit, which create 3 parallel traces for \shStar.
+A flat field with a narrower (0.3 mm) slit is needed to create a trace for use with the image slicer.
 For wavelength identification, a Thorium Argon reference is used.
-(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
+(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
 The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.

### 2017-06-03 ms.tex
made a comparison with BOSZ models and Kento's spectrum.
added a little about the BOSZ models and references to Seager 2003 for the stellar density measurement.

@@
 In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
-High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
-\citet{vanlieshout2016kic1255} analyze the light curve with a dust model and find a constraint on the semi-major axis which, in term, constraints the density of the star.
+High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
+\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis, which in turn constrains the density of the star when combined with Kepler's third law \citep{seager2003uniqueSolution}.
 \citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
@@
 The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm) has a sharper PSF and and is easier to trace.
-The 2013 data was taken with an image slicer and a wider ((2 $\times$ 30 mm)) slit, which create 3 parallel traces for \shStar.
+The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
 A flat field with a narrower (0.3 mm) slit is needed to create a trace for use with the image slicer.
@@
 \caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:mgTriplet}
+\end{centering}
+\end{figure}
+
+\subsection{Comparison to BOSZ}
+
+The BOSZ models \citep{bohlin2017bosz} are calculated up to a resolution of 300,000, so we use these to compare to the measured spectra.
+We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTriplet}.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
+\caption{Example spectrum of \shStar\ (reduced by Kento Mashuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTriplet}
 \end{centering}

### 2017-07-20 ms.tex
Smoothed out the wording in the intro and added some phrases about the high resolution spectroscopy.

@@
 Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
+We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
 \end{abstract}
@@
 \citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
-KIC 12557548's (hereafter \shStar's) light curve exhibited periodic flux dips with a period of 0.653 days.
-What was highly unusual about \shStar\ was that the flux dips were neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
-The variations in amplitude are highly stochastic and unpredictable from one event to the next 0.653 days later.
+KIC 12557548's (hereafter \shStar's) light curve exhibits periodic flux dips with a period of 0.653 days.
+Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
+The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next 0.653 days later.
 This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
-These variable dips are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
+These unusual light curve behaviors are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
 The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.
@@
 KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
-RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planets.
-RIK-210 may have accreting material that causes variable extinction.
-PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
+RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may are proto-planet candidates.
+RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
 
-Observational evidence from the \shStar\ system puts constraints on the planet candidate on the system.
-Radial velocity velocity variations of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
-There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km.
+The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
+High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
+There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
 The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
@@
 We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.
+We also analyze high resolution spectroscopy of the system to help resolve some of the different stellar parameters reported in the literature.
 
@@
 \includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Mashuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTriplet}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTriplet}
 \end{centering}

### 2017-07-20 ms.tex
Updated the observations and previous observations sections.

@@
 \begin{deluxetable}{lr}
-\tablecaption{List of observations}\label{tab:obsList}
+\tablecaption{List of observations}\label{tab:photSummary}
 \tablewidth{0pt}
@@
 We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
-Table \ref{tab:obsList} shows a summary of our observations and the UT dates.
+Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
 We obtained photometry for 5 nights with good weather on the \sha\ system.
@@
 
+In order to understand the long term behavior of the \sha\ system, we summarize the available published photometry in Table \ref{tab:prevObs}
+The Kepler mission provided the longest time baseline with near continuous photometry for about 4 years in long cadence ($\sim$30 min) mode.
+Following the failure of the reaction wheel, there were a few follow-up ground based observations.
+\citet{bochinsky2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
+The ratio of the $g'$ to $z'$ transit depths indeed deviated from unity, which could be fit with an interstellar dust extinction law.
+Overall, \citet{bochinisky2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.
+
+For one of the flux dip events, the $g$ band photometry exhibited a deeper transit depth than the $z'$ band.
+The ratio
+
 \begin{deluxetable*}{lrrrr}
-\tablecaption{List of published observations}\label{tab:obsList}
+\tablecaption{List of published observations}\label{tab:prevObs}
 \tablewidth{0pt}

### 2017-07-21 ms.tex
more description of the Subara spectra.

@@
 The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
-A flat field with a narrower (0.3 mm) slit is needed to create a trace for use with the image slicer.
+The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
 For wavelength identification, a Thorium Argon reference is used.
-(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
+(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
 The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
@@
 The final rms in this wavelength solution is 0.0021 $\AA$.
-After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the
+After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).
 
@@
 \includegraphics[width=0.45\textwidth]{images/subaru/CaI6162_spec.pdf}
-\caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:mgTriplet}
+\caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:CaILine}
 \end{centering}
@@
 \subsection{Comparison to BOSZ}
-
+K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
+The K Masuda reduction masks all telluric emission features and any outliers, producing cleaner spectra.
+These high resolution spectra can be compared to the BOSZ models which are calculated up to $R = 300,000$.
 The BOSZ models \citep{bohlin2017bosz} are calculated up to a resolution of 300,000, so we use these to compare to the measured spectra.
-We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTriplet}.
+We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
 
@@
 \includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTriplet}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
 \end{centering}

### 2017-07-21 ms.tex
corrected spelling of bochinski.

@@
 Following the failure of the reaction wheel, there were a few follow-up ground based observations.
-\citet{bochinsky2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
+\citet{bochinski2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
 The ratio of the $g'$ to $z'$ transit depths indeed deviated from unity, which could be fit with an interstellar dust extinction law.
-Overall, \citet{bochinisky2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.
+Overall, \citet{bochinski2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.
 

### 2017-07-23 ms.tex
added some more material about K Masuda's reduction.

@@
 
-\subsection{Comparison to BOSZ}
+\subsection{Independent Reduction}
 K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
 The K Masuda reduction masks all telluric emission features and any outliers, producing cleaner spectra.
-These high resolution spectra can be compared to the BOSZ models which are calculated up to $R = 300,000$.
-The BOSZ models \citep{bohlin2017bosz} are calculated up to a resolution of 300,000, so we use these to compare to the measured spectra.
+Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
+The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
+All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
+
+\subsection{Comparison to BOSZ}
+The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it can be compared to the measurements without convolving the Subaru spectra.
 We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.

### 2017-07-24 ms.tex
further details on the Subaru spectra.

@@
 They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
-If true, this would suggest that high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
+If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
 
@@
 
-We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.
-We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
+We decided to re-visit the stellar parameters by examining the high spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
+There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
+Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system.
+Both of these observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
+
+\subsection{Independent Iraf Reduction}
+
+In one independent analysis (E Schlawin), we we follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
 Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
@@
 Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
-The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm) has a sharper PSF and and is easier to trace.
+The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/ume/node16.html}) has a sharper PSF and and is easier to trace.
 The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.

### 2017-07-26 ms.tex
further typo corrections in the description of the HDS spectra.

@@
 \clearpage
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/out_HDSA00094087.pdf}
+\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/HDSA00111345.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
+\caption{Spectra images from 2013 versus 2015.
+The PSF profile (bottom panel) is much wider in 2013 because an image slicer creates 3 traces for the one star.
+In 2015, a narrow slit is used instead.}\label{fig:prof2013vs2015}
+\end{centering}
+\end{figure}
+
 \begin{figure}
@@
 \includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
+\caption{{\it Top:} Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
 There are many bad pixels, which are preliminarily discarded for fluxes above 1.25.
-These are not fully removed in the convolved spectrum.}\label{fig:naDlines}
+{\it Bottom:} The measured spectrum is convolved with a Gaussian kernel to match the resolution of the HIGHRES models which are calculated for log(g)=4.5 and 4.0.
+The measured Na D$_1$ and D$_2$ lines are deeper than either model, but have similar line ratios to the 4500 K log(g)=4.5 model.}\label{fig:naDlines}
 \end{centering}
@@
 \begin{deluxetable*}{lcrrr}
-\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}\label{tab:stellObsParams}
+\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
 \tablewidth{0pt}
@@
 \enddata
-\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}
+\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
 \end{deluxetable*}
@@
 
-\subsection{Observations}
+\subsection{Subaru HDS Spectra}
 
@@
 Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
-We applied bad pixel masks and bias files to each CCD separately.
+We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
 Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/out_HDSA00094087.pdf}
-\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/HDSA00111345.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
-\caption{Spectra images from 2013 versus 2015.
-The PSF profile (bottom panel) is much wider in 2013 because an image slicer creates 3 traces for the one star.
-In 2015, a narrow slit is used instead.}\label{fig:prof2013vs2015}
-\end{centering}
-\end{figure}
 
@@
 The final rms in this wavelength solution is 0.0021 $\AA$.
-After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).
+After the reference spectrum is used to find a wavelength solution, the spectrum is examined near some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).
 

### 2017-07-28 ms.tex
updated the BOSZ comparison to use a convolved stellar spectrum.
Added a better spectrum which is the median combination of all frames. Also tweaked the convolution kernel slightly to better match the data.

@@
 We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
+The models are convolved with a Gaussian that has a standard deviation $\sigma_G = 1/57700$  to obtain a resolution of 50,000.
 
@@
 \caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
+\end{centering}
+\end{figure}
+
+We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
+Also, we average ll available spectra from the Masuda reduction to increate the signal to noise.
+The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
+Interestingly, the median spectrum has weaker features than the individual spectrum, perhaps because it is variable but also it could be part of the median process.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
 \end{centering}

### 2017-07-30 ms.tex
added an image comparing to a higher temp model.

@@
 The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
-Interestingly, the median spectrum has weaker features than the individual spectrum, perhaps because it is variable but also it could be part of the median process.
+The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.
 
@@
 \end{figure}
+
+As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
+The line ratios appear to match the BOSZ model with T=4500 K much better.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
+\end{centering}
+\end{figure}
+
+This motivates a check on the temperatures, so we compare 3 models all with log(g)=4.5 and
 

### 2017-08-18 ms.tex
corrected the resolving power.
added break in the line for the link since it was running into other text.

@@
 
-We decided to re-visit the stellar parameters by examining the high spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
+We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
 There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
@@
 The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
-Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
-The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/ume/node16.html}) has a sharper PSF and and is easier to trace.
+Figure \ref{fig:prof2013vs2015} shows an example blue-chip images from 2013 and 2015.
+The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000)\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/ume/node16.html} has a sharper PSF and and is easier to trace.
 The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
@@
 The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
-The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
+The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
 The final rms in this wavelength solution is 0.0021 $\AA$.
@@
 We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
-The models are convolved with a Gaussian that has a standard deviation $\sigma_G = 1/57700$  to obtain a resolution of 50,000.
+The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.
 

### 2017-08-24 ms.tex
added a figure for my bosz model exploration.

@@
 \clearpage
+
+\subsection{BOSZ Model Exploration}
+
+We also convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
+Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M].
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/T_EFF_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/LOGG_exploration}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/MH_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/ALPHA_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/CM_exploration.pdf}
+\caption{BOSZ parameter exploration.}\label{fig:boszModelParamsMedianSpec}
+\end{centering}
+\end{figure*}
+
 \section{Conclusions}\label{sec:conclusions}

### 2017-08-26 ms.tex
added more description of the BOSZ model exploration.

@@
 We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
-Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.
 
@@
 The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES, but not the line strengths.
+In figure \ref{fig:CaILine} we zoom in on the Ca I 6162 $\AA$ feature.
+Again, there is no clear match to either BOSZ model.
 
@@
 K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
-The K Masuda reduction masks all telluric emission features and any outliers, producing cleaner spectra.
+This more sophisticated reduction masks all telluric emission features and any outliers, producing cleaner spectra.
 Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
@@
 All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
+Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
+The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
 
 \subsection{Comparison to BOSZ}
-The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it can be compared to the measurements without convolving the Subaru spectra.
+The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it should be comparable to measurements without smoothing the Subaru spectra as was necessary for the HIGHRES models above.
 We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
@@
 
-We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
-Also, we average ll available spectra from the Masuda reduction to increate the signal to noise.
-The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
-The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.
+The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
+\textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
+In order for us to compare the BOSZ models and our data, we have to convolve the Subaru spectrum.
+They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
+Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
+For each parameter, we change the models by about 2 steps in the BOSZ grid.
+For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
+The errors are estimated from the standard deviation of the spectra over the night.
 
-\begin{figure}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
-\end{centering}
-\end{figure}
-
-As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
-The line ratios appear to match the BOSZ model with T=4500 K much better.
-
-\begin{figure}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
-\end{centering}
-\end{figure}
-
-This motivates a check on the temperatures, so we compare 3 models all with log(g)=4.5 and
-
-\clearpage
-
-\subsection{BOSZ Model Exploration}
-
-We also convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
-Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M].
+The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
+A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.
 
@@
 \end{figure*}
+
+\clearpage
 

### 2017-08-29 ms.tex
started describing the chi-squared minimization search of the BOSZ models.

@@
 The errors are estimated from the standard deviation of the spectra over the night.
+For now, we ignore the smoothing of the data that creates non-zero off-diagonal terms in the covariance matrix.
 
@@
 \end{figure*}
+
+\subsubsection{$\chi^2$ Minimization}
+We downloaded a grid of BOSZ models with temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
+As discussed above, we use an approximate $\chi^2$ statistic over the wavelength range covering the Mg triplet (5160 $\AA$ to 5190 $\AA$).
 

### 2018-03-28 ms.tex
reporting result of grid search>
updated the model comparison plots to make them clearer and highlight the minimum chi-squared solution.

@@
 \includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/CM_exploration.pdf}
-\caption{BOSZ parameter exploration.}\label{fig:boszModelParamsMedianSpec}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/FINAL_exploration.pdf}
+\caption{The BOSZ models are explored over the parameter space to search for a best fit as well as visualize how much each parameter affects the spectrum.
+The final plot shows the best-fit BOSZ model, but it still under-predicts and over-predicts some line strengths.}\label{fig:boszModelParamsMedianSpec}
 \end{centering}
@@
 As discussed above, we use an approximate $\chi^2$ statistic over the wavelength range covering the Mg triplet (5160 $\AA$ to 5190 $\AA$).
+The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec}: T=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
 

### 2018-03-31 ms.tex
updated plot with binned photometry for the 5 nights.

@@
 This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
-We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.
+We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity was decreasing as a function of time.
 We also analyze high resolution spectroscopy of the system to help resolve some of the different stellar parameters reported in the literature.
@@
 Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ showing transits.
+We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
+\begin{equation}
+T = T_0 + n P
+\end{equation}
+where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.
+
 The expected transit epochs from the ephemeris in \citep{vanWerkhoven2014} are shown for reference.
@@
 \includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
-\caption{Reference-corrected time series photometry \shStar\ for all nights.
+\caption{Reference-corrected time series photometry \shStar\ for all nights (blue circles).
+Orange squares mark 20 minute flux bins.
 The expected transit epochs from the Kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.

### 2018-04-03 supplement.tex
started morphing the paper into a supplement and will separtely make a research note.

--- 2017-05-29 ms.tex
@@
 
-\title{Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}
+\title{Supplement: Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}
 
@@
 This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
-We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.
+We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity was decreasing as a function of time.
+We also analyze high resolution spectroscopy of the system to help resolve some of the different stellar parameters reported in the literature.
 
 \begin{deluxetable}{lr}
-\tablecaption{List of observations}\label{tab:obsList}
+\tablecaption{List of observations}\label{tab:photSummary}
 \tablewidth{0pt}
@@
 
+In order to understand the long term behavior of the \sha\ system, we summarize the available published photometry in Table \ref{tab:prevObs}
+The Kepler mission provided the longest time baseline with near continuous photometry for about 4 years in long cadence ($\sim$30 min) mode.
+Following the failure of the reaction wheel, there were a few follow-up ground based observations.
+\citet{bochinski2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
+The ratio of the $g'$ to $z'$ transit depths indeed deviated from unity, which could be fit with an interstellar dust extinction law.
+Overall, \citet{bochinski2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.
+
+For one of the flux dip events, the $g$ band photometry exhibited a deeper transit depth than the $z'$ band.
+The ratio
+
 \begin{deluxetable*}{lrrrr}
-\tablecaption{List of published observations}\label{tab:obsList}
+\tablecaption{List of published observations}\label{tab:prevObs}
 \tablewidth{0pt}
@@
 
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/out_HDSA00094087.pdf}
+\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/HDSA00111345.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
+\caption{Spectra images from 2013 versus 2015.
+The PSF profile (bottom panel) is much wider in 2013 because an image slicer creates 3 traces for the one star.
+In 2015, a narrow slit is used instead.}\label{fig:prof2013vs2015}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec_interp.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec.pdf}
+\caption{{\it Top:} Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
+There are many bad pixels, which are preliminarily discarded for fluxes above 1.25.
+{\it Bottom:} The measured spectrum is convolved with a Gaussian kernel to match the resolution of the HIGHRES models which are calculated for log(g)=4.5 and 4.0.
+The measured Na D$_1$ and D$_2$ lines are deeper than either model, but have similar line ratios to the 4500 K log(g)=4.5 model.}\label{fig:naDlines}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
+\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
+\caption{Example spectrum of \shStar\ near the Mg triplet.
+{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
+The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
+{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
+The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios but not the strength of the features.}\label{fig:mgTriplet}
+\end{centering}
+\end{figure}
+
 \section{Stellar Characterization}
-
 \subsection{Previous Observations}
-The host star \shStar\ has been characterized by both photometry and spectroscopy.
-Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
-In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
-High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
-\citet{vanlieshout2016kic1255} analyze the light curve with a dust model and find a constraint on the semi-major axis which, in term, constraints the density of the star.
-\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
-They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
-If true, this would suggest that high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
 
 \begin{deluxetable*}{lcrrr}
-\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}\label{tab:stellObsParams}
+\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
 \tablewidth{0pt}
@@
 \enddata
-\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}
+\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
 \end{deluxetable*}
 
-\subsection{Observation}
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
-There are many bad pixels.}\label{fig:naDlines}
-\end{centering}
-\end{figure}
+The host star \shStar\ has been characterized by both photometry and spectroscopy.
+Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
+In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
+High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
+\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis, which in turn constrains the density of the star when combined with Kepler's third law \citep{seager2003uniqueSolution}.
+\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
+They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
+If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Mg triplet.
-{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
-The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
-{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
-The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
-\end{centering}
-\end{figure}
+\subsection{Subaru HDS Spectra}
 
-We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.
-We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
+We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
+There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
+Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system.
+Both of these observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
+
+\subsection{Independent Iraf Reduction}
+
+In one independent analysis (E Schlawin), we we follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
 Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
-We applied bad pixel masks and bias files to each CCD separately.
-Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.
+We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
 
-The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
-The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
+The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
+Figure \ref{fig:prof2013vs2015} shows an example blue-chip images from 2013 and 2015.
+The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000)\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/ume/node16.html} has a sharper PSF and and is easier to trace.
+The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
+The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
 For wavelength identification, a Thorium Argon reference is used.
-(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
+(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
 The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
-The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
+The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
 The final rms in this wavelength solution is 0.0021 $\AA$.
-After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the
+After the reference spectrum is used to find a wavelength solution, the spectrum is examined near some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).
 
@@
 
-The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a much closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES.
-The only mismatch between the 4500 K and log(g)=4.5 model and the HDS spectrum for \shStar\ is the overall line strengths.
+The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES, but not the line strengths.
+In figure \ref{fig:CaILine} we zoom in on the Ca I 6162 $\AA$ feature.
+Again, there is no clear match to either BOSZ model.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/CaI6162_spec.pdf}
+\caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:CaILine}
+\end{centering}
+\end{figure}
+
+\subsection{Independent Reduction}
+K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
+This more sophisticated reduction masks all telluric emission features and any outliers, producing cleaner spectra.
+Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
+The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
+All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
+Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
+The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
+
+\subsection{Comparison to BOSZ}
+The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it should be comparable to measurements without smoothing the Subaru spectra as was necessary for the HIGHRES models above.
+We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
+The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
+\end{centering}
+\end{figure}
+
+The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
+\textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
+In order for us to compare the BOSZ models and our data, we have to convolve the Subaru spectrum.
+They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
+Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
+For each parameter, we change the models by about 2 steps in the BOSZ grid.
+For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
+The errors are estimated from the standard deviation of the spectra over the night.
+For now, we ignore the smoothing of the data that creates non-zero off-diagonal terms in the covariance matrix.
+
+The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
+A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/T_EFF_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/LOGG_exploration}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/MH_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/ALPHA_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/CM_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/FINAL_exploration.pdf}
+\caption{The BOSZ models are explored over the parameter space to search for a best fit as well as visualize how much each parameter affects the spectrum.
+The final plot shows the best-fit BOSZ model, but it still under-predicts and over-predicts some line strengths.}\label{fig:boszModelParamsMedianSpec}
+\end{centering}
+\end{figure*}
+
+\subsubsection{$\chi^2$ Minimization}
+We downloaded a grid of BOSZ models with temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
+As discussed above, we use an approximate $\chi^2$ statistic over the wavelength range covering the Mg triplet (5160 $\AA$ to 5190 $\AA$).
+The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec}: T=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
 
 \clearpage
+
 \section{Conclusions}\label{sec:conclusions}

### 2018-04-04 ms.tex
changed out the aastex style file with one that doesn't skip first page.

@@
 %\documentclass[12pt,preprint]{aastex}
-\documentclass[twocolumn]{aastex61}
+\documentclass[preprint]{aastex61_mod}
 %\documentclass[iop]{emulateapj}
@@
 
-\shorttitle{KIC 12557548 b Long Term Followup}
+\shorttitle{KIC 12557548 b back to normal}
 \shortauthors{Schlawin et al.}
@@
 
-\title{Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}
+\title{Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b}
 
@@
 
-\author{J. Teske?}
-\affiliation{Carnegie Observatories, 813 Santa Barbara Street, Pasadena, CA 91101, USA}
+\author{Jonathan Fraine?}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
 
-\author{S. Rappaport?}
-\affiliation{MIT}
+\author{Rafia Bushra?}
+\affiliation{Steward Observatory, Tucson AZ 85721}
 
-\author{R. van Lieshout?}
-\affiliation{Institute of Astronomy - University of Cambridge}
+%\begin{abstract}
+%KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
+Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014.
+Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
+%We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
+%\end{abstract}
 
-\begin{abstract}
+%\keywords{stars: atmospheres -- stars: individual (\objectname{KIC 12557548}) -- stars: variables: general}
+
+\section{Abstract}
 KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
@@
 We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
-\end{abstract}
-
-\keywords{stars: atmospheres -- stars: individual (\objectname{KIC 12557548}) -- stars: variables: general}
 
@@
 
-\begin{deluxetable}{lr}
-\tablecaption{List of observations}\label{tab:photSummary}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Date} &
-\colhead{Comment} \\
-\colhead{UT} & \\
- }
-\startdata
-2016-06-10 & Clouds \\
-2016-06-12 & Clear \\
-2016-06-14 & Clear \\
-2016-07-12 & Clear \\
-2016-07-14 & Mostly clear \\
-2016-07-16 & Clear \\
-\enddata
-\tablenotetext{}{Summary of observations and conditions in this work.}
-\end{deluxetable}
-
 \section{Observations}
-We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
-Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
+We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
+The nights were clear with the exception of a few passing cloud son 2016-07-14.
+We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
 We obtained photometry for 5 nights with good weather on the \sha\ system.

### 2018-04-04 ms.tex
condensed down paper into research note.

@@
 
-%\slugcomment{To be submitted to MNRAS}
+%\submitjournal{RNAAS}
 
@@
 
-The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
-Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
+%The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
+%Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
 
-Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie.
+%Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie.
 Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
-KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
-RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may are proto-planet candidates.
-RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
+%KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
+%RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may are proto-planet candidates.
+%RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
 
-The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
-High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
-There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
-The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
+%The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
+%High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
+%There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
+%The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
 
@@
 \citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
-This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
+This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
 We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity was decreasing as a function of time.
@@
 We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
-The nights were clear with the exception of a few passing cloud son 2016-07-14.
+The nights were clear with the exception of a few passing clouds on 2016-07-14.
 We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
-We obtained photometry for 5 nights with good weather on the \sha\ system.
-
-\subsection{Previous Observations}
-
-In order to understand the long term behavior of the \sha\ system, we summarize the available published photometry in Table \ref{tab:prevObs}
-The Kepler mission provided the longest time baseline with near continuous photometry for about 4 years in long cadence ($\sim$30 min) mode.
-Following the failure of the reaction wheel, there were a few follow-up ground based observations.
-\citet{bochinski2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
-The ratio of the $g'$ to $z'$ transit depths indeed deviated from unity, which could be fit with an interstellar dust extinction law.
-Overall, \citet{bochinski2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.
-
-For one of the flux dip events, the $g$ band photometry exhibited a deeper transit depth than the $z'$ band.
-The ratio
-
-\begin{deluxetable*}{lrrrr}
-\tablecaption{List of published observations}\label{tab:prevObs}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Date Start} &
-\colhead{Date End} &
-\colhead{Observatory} &
-\colhead{Filter} &
-\colhead{Reference(s)} \\
-UT & UT & & & \\
- }
-\startdata
-2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
-2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
-2013-08-13 & 2013-09-03 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
-2014-08-14 & 2013-09-04 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
-2016-06-12 & 2016-06-12 & Kuiper & Harris R & This Work \\
-2016-07-12 & 2016-07-16 & Kuiper & Harris R & This Work \\
-\enddata
-\tablenotetext{}{Summary of published photometric observations of \sha.}
-\end{deluxetable*}
 
@@
 For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
-I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
-\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
-\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
-The reference stars were chosen to have similar count levels as the source. 
-}\label{fig:ut2016-07-14cloudImg}
-\end{centering}
-\end{figure}
-
-All nights light curves are shown in Figure \ref{fig:allNightallStar}.
-These are the same reference stars shown in Figure \ref{fig:ut2016-07-14cloudImg}.
-The nights two nights in June, 2016 show greater overall stability than the ones in July, 2016.
-I suspect that this can mostly be explained by moisture and clouds (such as the ones that caused huge drops in flux on UT2016-07-14.
-
-\begin{figure*}
-\begin{centering}
-\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
-\caption{Time series photometry for all stars and all nights nights.
-The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.
-All source radius, background start and background annulus end parameters were 9, 9 and 12 pixels respectively.}\label{fig:allNightallStar}
-\end{centering}
-\end{figure*}
+They were combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
+12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
+These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \sha.
 
@@
 
-\clearpage
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/out_HDSA00094087.pdf}
-\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/HDSA00111345.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
-\caption{Spectra images from 2013 versus 2015.
-The PSF profile (bottom panel) is much wider in 2013 because an image slicer creates 3 traces for the one star.
-In 2015, a narrow slit is used instead.}\label{fig:prof2013vs2015}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec_interp.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec.pdf}
-\caption{{\it Top:} Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
-There are many bad pixels, which are preliminarily discarded for fluxes above 1.25.
-{\it Bottom:} The measured spectrum is convolved with a Gaussian kernel to match the resolution of the HIGHRES models which are calculated for log(g)=4.5 and 4.0.
-The measured Na D$_1$ and D$_2$ lines are deeper than either model, but have similar line ratios to the 4500 K log(g)=4.5 model.}\label{fig:naDlines}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Mg triplet.
-{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
-The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
-{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
-The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios but not the strength of the features.}\label{fig:mgTriplet}
-\end{centering}
-\end{figure}
-
-\section{Stellar Characterization}
-\subsection{Previous Observations}
-
-\begin{deluxetable*}{lcrrr}
-\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Reference} &
-\colhead{$ T_{eff,*} $} &
-\colhead{$\log(g)$} &
-\colhead{Evolutionary Status} &
-\colhead{Method} \\
- & (K) & $\log$(cm s$^{-2}$) & & \\
- }
-\startdata
-  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
-  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
-  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
-  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
-\enddata
-\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
-\end{deluxetable*}
-
-The host star \shStar\ has been characterized by both photometry and spectroscopy.
-Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
-In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
-High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
-\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis, which in turn constrains the density of the star when combined with Kepler's third law \citep{seager2003uniqueSolution}.
-\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
-They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
-If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
-
-\subsection{Subaru HDS Spectra}
-
-We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
-There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
-Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system.
-Both of these observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
-
-\subsection{Independent Iraf Reduction}
-
-In one independent analysis (E Schlawin), we we follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
-Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
-We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
-
-The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
-Figure \ref{fig:prof2013vs2015} shows an example blue-chip images from 2013 and 2015.
-The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000)\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/ume/node16.html} has a sharper PSF and and is easier to trace.
-The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
-The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
-For wavelength identification, a Thorium Argon reference is used.
-(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
-The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
-The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
-The final rms in this wavelength solution is 0.0021 $\AA$.
-After the reference spectrum is used to find a wavelength solution, the spectrum is examined near some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).
-
-\subsection{Comparison to Templates}
-
-The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
-\citet{kawahara2013starspots} find a log(g) = 3.9 $\pm$ 0.2, whereas \citet{rappaport} find a log(g)=4.63.
-To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
-Also, we interpolated over any pixels above a normalized flux of 2.0 in Figure \ref{fig:mgTriplet} (top).
-Then, we convolve with a Gaussian kernel with a standard deviation of 6 pixels.
-
-The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES, but not the line strengths.
-In figure \ref{fig:CaILine} we zoom in on the Ca I 6162 $\AA$ feature.
-Again, there is no clear match to either BOSZ model.
-
-\begin{figure}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/CaI6162_spec.pdf}
-\caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:CaILine}
-\end{centering}
-\end{figure}
-
-\subsection{Independent Reduction}
-K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
-This more sophisticated reduction masks all telluric emission features and any outliers, producing cleaner spectra.
-Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
-The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
-All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
-Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
-The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
-
-\subsection{Comparison to BOSZ}
-The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it should be comparable to measurements without smoothing the Subaru spectra as was necessary for the HIGHRES models above.
-We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
-The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.
-
-\begin{figure}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
-\end{centering}
-\end{figure}
-
-The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
-\textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
-In order for us to compare the BOSZ models and our data, we have to convolve the Subaru spectrum.
-They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
-Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
-For each parameter, we change the models by about 2 steps in the BOSZ grid.
-For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
-The errors are estimated from the standard deviation of the spectra over the night.
-For now, we ignore the smoothing of the data that creates non-zero off-diagonal terms in the covariance matrix.
-
-The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
-A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/T_EFF_exploration.pdf}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/LOGG_exploration}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/MH_exploration.pdf}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/ALPHA_exploration.pdf}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/CM_exploration.pdf}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/FINAL_exploration.pdf}
-\caption{The BOSZ models are explored over the parameter space to search for a best fit as well as visualize how much each parameter affects the spectrum.
-The final plot shows the best-fit BOSZ model, but it still under-predicts and over-predicts some line strengths.}\label{fig:boszModelParamsMedianSpec}
-\end{centering}
-\end{figure*}
-
-\subsubsection{$\chi^2$ Minimization}
-We downloaded a grid of BOSZ models with temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
-As discussed above, we use an approximate $\chi^2$ statistic over the wavelength range covering the Mg triplet (5160 $\AA$ to 5190 $\AA$).
-The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec}: T=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
-
-\clearpage
-
 \section{Conclusions}\label{sec:conclusions}
@@
 Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
-Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the 61-inch Kuiper telescope on Mt Bigelow.
+%Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the 61-inch Kuiper telescope on Mt Bigelow.
 MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
@@
 \appendix
-
-\section{Original Light Curves}
 

### 2018-04-06 ms.tex
a few more text updates for the note.

@@
 Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
-We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
 
@@
 This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
-We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity was decreasing as a function of time.
-We also analyze high resolution spectroscopy of the system to help resolve some of the different stellar parameters reported in the literature.
+We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.
 
@@
 
-Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ showing transits.
+Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all 5 nights which were timed with transits.
 We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.

### 2018-04-08 supplement.tex
added some info on tweaking the resolutions as well as comparison of BOSZ models and median spec.

--- 2017-05-29 supplement.tex
@@
 \clearpage
+
+\subsection{Tweaking resolutions}
+
+We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
+Also, we averaged all available spectra from the Masuda reduction to increase the signal to noise.
+The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
+The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
+\end{centering}
+\end{figure}
+
+As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
+The line ratios appear to match the BOSZ model with T=4500 K much better.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
+\end{centering}
+\end{figure}
+
 \section{Conclusions}\label{sec:conclusions}

### 2018-04-09 supplement.tex

--- 2018-04-03 supplement.tex
@@
 
-\title{Supplement: Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}
+\title{Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}
 
@@
 \section{Introduction}
+
+Supplementary Material/Notes for the main paper
+
+\section{Observations}
+
 \citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
@@
 
+\subsection{Tweaking resolutions}
+
+We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
+Also, we averaged all available spectra from the Masuda reduction to increase the signal to noise.
+The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
+The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
+\end{centering}
+\end{figure}
+
+As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
+The line ratios appear to match the BOSZ model with T=4500 K much better.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
+\end{centering}
+\end{figure}
+
 The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.

### 2018-04-09 supplement.tex
a few notes on specmatch results.

@@
   \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
+  This Work - BOSZ match & 4500 		& 4.5				& main-sequence star & high-resolution spectroscopy \\
+  This Work - Specmatch 	&  4500 $\pm 110$ & 4.6 $\pm 0.1$ & main-sequence star & high-resolution spectroscopy \\ 
 \enddata
@@
 The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec}: T=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
+
+\subsection{Specmatch}\label{sec:SpecMatch}
+
+We also use the \texttt{specmatch} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
+\texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
+Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
+
+\begin{figure}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/subaru/spec_chi_min.pdf}
+\caption{$\chi^2$ as a function of stellar parameters found by \texttt{specmatch}.}\label{fig:specMatch}
+\end{centering}
+\end{figure}
 

### 2018-04-10 supplement.tex
added explanation of specmatch results and cleaned up spectral matching section.

@@
 \enddata
-\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
+\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.
+We find that the Subaru high resolution spectrum best-fits the higher gravity main-sequence star case.}\label{tab:stellObsParams}
 \end{deluxetable*}
@@
 There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
-Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system.
+Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}.
 Both of these observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
@@
 The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
-Figure \ref{fig:prof2013vs2015} shows an example blue-chip images from 2013 and 2015.
+Figure \ref{fig:prof2013vs2015} shows example blue-chip images from 2013 and 2015.
 The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000)\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/ume/node16.html} has a sharper PSF and and is easier to trace.
@@
 The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
-\citet{kawahara2013starspots} find a log(g) = 3.9 $\pm$ 0.2, whereas \citet{rappaport} find a log(g)=4.63.
+\citet{kawahara2013starspots} find T$_{eff}$=4950 $\pm$ 70 K, whereas \citet{rappaport} find a T$_{eff}$=4400 $\pm$200.
 To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
@@
 The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it should be comparable to measurements without smoothing the Subaru spectra as was necessary for the HIGHRES models above.
-We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
+We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
 The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.
@@
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\caption{Median spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
 \end{centering}
@@
 
-The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
+The BOSZ models appear much smoother than the measured spectrum, even if we use the BOSZ models at the full R=100,000.
 \textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
@@
 They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
-Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
+
+We then explored the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
 For each parameter, we change the models by about 2 steps in the BOSZ grid.
@@
 For now, we ignore the smoothing of the data that creates non-zero off-diagonal terms in the covariance matrix.
-
-\subsection{Tweaking resolutions}
-
-We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
-Also, we averaged all available spectra from the Masuda reduction to increase the signal to noise.
-The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
-The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.
-
-\begin{figure}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
-\end{centering}
-\end{figure}
-
-As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
-The line ratios appear to match the BOSZ model with T=4500 K much better.
-
-\begin{figure}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
-\end{centering}
-\end{figure}
 
@@
 \texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
+As with the comparisons to the BOSZ models, we first convolve the median spectrum from \citet{masuda2018rvKIC1255} with a R=40,000 kernel.
+We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.
+
 Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
+The effective temperature radius show clear global $\chi^2$ minima for the HIRES spectral libraries.
+The resulting best-fit parameters are T$_{eff}$=4500 K, [Fe/H]=-0.1$\pm$0.1,  and log(g)=4.5$\pm$0.1.
+We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}.
 
-\begin{figure}[!hbtp]
+\begin{figure*}[!hbtp]
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/spec_chi_min.pdf}
-\caption{$\chi^2$ as a function of stellar parameters found by \texttt{specmatch}.}\label{fig:specMatch}
+\includegraphics[width=0.8\textwidth]{images/subaru/spec_chi_min.pdf}
+\caption{$\chi^2$ as a function of stellar parameters found by \texttt{specmatch}.
+The effective temperature and radii show clear global minima.}\label{fig:specMatch}
 \end{centering}
-\end{figure}
+\end{figure*}
 

### 2018-04-10 supplement.tex
added results with specmatch and BOSZ not realizing I had another copy of the paper supplement.

--- 2018-04-09 supplement.tex
@@
 \section{Introduction}
-
-Supplementary Material/Notes for the main paper
-
-\section{Observations}
-
 \citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
@@
   \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
+  This work - Specmatch	& 4500 	& 4.63	& main-sequence star & high-resolution spectroscopy\\
+  This work - BOSZ		& 4500	& 4.5		& main-sequence star & high-resolution spectroscopy\\
 \enddata
@@
 
+\clearpage
 \subsection{Comparison to BOSZ}

### 2018-04-11 supplement.tex
added the van Lieshout transit duration constraint.

--- 2018-04-10 supplement.tex
@@
   \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
+  \citet{vanlieshout2016kic1255} & 			& $\gtrsim 4.4 $		& main-sequence star & transit duration + Kepler's 3rd law \\
   This Work - BOSZ match & 4500 		& 4.5				& main-sequence star & high-resolution spectroscopy \\
-  This Work - Specmatch 	&  4500 $\pm 110$ & 4.6 $\pm 0.1$ & main-sequence star & high-resolution spectroscopy \\ 
+  This Work - \texttt{specmatch} 	&  4500 $\pm 110$ & 4.6 $\pm 0.1$ & main-sequence star & high-resolution spectroscopy \\ 
 \enddata

### 2018-04-12 supplement.tex
added a secondary eclipse figure.

@@
 
+\section{Kepler Re-analysis}
+We examine the 17 total quarters of Kepler data.
+There is not detectable secondary eclipse at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
+The constraint is even tighter assuming a circular orbit.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.8\textwidth]{images/kepler/secondary_eclipse.pdf}
+\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
+\end{centering}
+\end{figure*}
+
 \section{Conclusions}\label{sec:conclusions}

### 2018-04-13 ms.tex

--- 2018-04-04 ms.tex
@@
 %\documentclass[12pt,preprint]{aastex}
-\documentclass[preprint]{aastex61_mod}
+\documentclass[preprint]{aastex61}
 %\documentclass[iop]{emulateapj}
@@
 
+\author{Kento Masuda?}
+\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
+
+\author{Teruyuki Hirano?}
+\affiliation{Department of Earth and Planetary Sciences, Tokyo Institute of Technology, Tokyo 152-8550, Japan}
+
+\author{Hajima Kawahara?}
+\affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan;}
+
 \author{Betsy Green?}
@@
 
-%\begin{abstract}
-%KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
+\begin{abstract}
+KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
 Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014.
 Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
-%We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
-%\end{abstract}
+We also evaluate high resolution spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 K, main-sequence star.
+\end{abstract}
 
@@
 
-\section{Abstract}
-KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
-Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014.
-Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
-We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
+%\section{Abstract}
 
@@
 \citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
-This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
-We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity was decreasing as a function of time.
-We also analyze high resolution spectroscopy of the system to help resolve some of the different stellar parameters reported in the literature.
+This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
+We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.
 
@@
 For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
-I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
+They were combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
+12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
+These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \sha.
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
-\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
-\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
-The reference stars were chosen to have similar count levels as the source. 
-}\label{fig:ut2016-07-14cloudImg}
-\end{centering}
-\end{figure}
-
-All nights light curves are shown in Figure \ref{fig:allNightallStar}.
-These are the same reference stars shown in Figure \ref{fig:ut2016-07-14cloudImg}.
-The nights two nights in June, 2016 show greater overall stability than the ones in July, 2016.
-I suspect that this can mostly be explained by moisture and clouds (such as the ones that caused huge drops in flux on UT2016-07-14.
-
-\begin{figure*}
-\begin{centering}
-\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
-\caption{Time series photometry for all stars and all nights nights.
-The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.
-All source radius, background start and background annulus end parameters were 9, 9 and 12 pixels respectively.}\label{fig:allNightallStar}
-\end{centering}
-\end{figure*}
-
-Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ showing transits.
+Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all 5 nights which were timed with transits.
 We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.

### 2018-04-13 ms.tex
added back in info on the reference stars.

@@
 
-%The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
-%Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
+The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
+Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
 
-%Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie.
+Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie.
 Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
-%KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
-%RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may are proto-planet candidates.
-%RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
+KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
+RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planet candidates.
+RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
 
-%The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
-%High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
-%There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
-%The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
+The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
+High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
+There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
+The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
 
@@
 Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
-\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
+\citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
 This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
 We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.
+
+\begin{deluxetable}{lr}
+\tablecaption{List of observations}\label{tab:photSummary}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Date} &
+\colhead{Comment} \\
+\colhead{UT} & \\
+ }
+\startdata
+2016-06-10 & Clouds \\
+2016-06-12 & Clear \\
+2016-06-14 & Clear \\
+2016-07-12 & Clear \\
+2016-07-14 & Mostly clear \\
+2016-07-16 & Clear \\
+\enddata
+\tablenotetext{}{Summary of observations and conditions in this work.}
+\end{deluxetable}
 
@@
 We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
+Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
 
@@
 
+For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
+I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
+\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
+\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
+The reference stars were chosen to have similar count levels as the source. 
+}\label{fig:ut2016-07-14cloudImg}
+\end{centering}
+\end{figure}
+
+All nights light curves are shown in Figure \ref{fig:allNightallStar}.
+These are the same reference stars shown in Figure \ref{fig:ut2016-07-14cloudImg}.
+The nights two nights in June, 2016 show greater overall stability than the ones in July, 2016.
+I suspect that this can mostly be explained by moisture and clouds (such as the ones that caused huge drops in flux on UT2016-07-14.
+
+\begin{figure*}
+\begin{centering}
+\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
+\caption{Time series photometry for all stars and all nights nights.
+The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.
+All source radius, background start and background annulus end parameters were 9, 9 and 12 pixels respectively.}\label{fig:allNightallStar}
+\end{centering}
+\end{figure*}
+
 Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all 5 nights which were timed with transits.
-We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
+We use the following planet transit ephemeris, using the flux minimum ``transit center'' from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
 \begin{equation}

### 2018-04-14 ms.tex
added kepler stuff, pca and river plot

@@
 
+\section{Kepler Re-analysis}
+We examine the 17 total quarters of Kepler data.
+There is not detectable secondary eclipse at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
+The constraint is even tighter assuming a circular orbit.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.8\textwidth]{images/kepler/secondary_eclipse.pdf}
+\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
+\caption{Cleaned Kepler Long-cadence data and PCA analysis.}\label{fig:kepPCA}
+\end{centering}
+\end{figure*}
+
 \section{Conclusions}\label{sec:conclusions}

### 2018-04-15 ms.tex
specmatch stuff including radius.

@@
 
+\subsection{Specmatch}\label{sec:SpecMatch}
+
+We also use the \texttt{specmatch} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
+\texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
+As with the comparisons to the BOSZ models, we first convolve the median spectrum from \citet{masuda2018rvKIC1255} with a R=40,000 kernel.
+We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.
+
+Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
+The effective temperature radius show clear global $\chi^2$ minima for the HIRES spectral libraries.
+The resulting best-fit parameters are T$_{eff}$=4500 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$.
+We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.8\textwidth]{images/subaru/spec_chi_min.pdf}
+\caption{$\chi^2$ as a function of stellar parameters found by \texttt{specmatch}.
+The effective temperature and radii show clear global minima.}\label{fig:specMatch}
+\end{centering}
+\end{figure*}
+
 \section{Conclusions}\label{sec:conclusions}

### 2018-04-15 ms.tex
added the model fits.

@@
 
-\title{Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b}
+\title{Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b}
 
@@
 
-\clearpage
-
-\section{Kepler Re-analysis}
-We examine the 17 total quarters of Kepler data.
-There is not detectable secondary eclipse at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
-The constraint is even tighter assuming a circular orbit.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.8\textwidth]{images/kepler/secondary_eclipse.pdf}
-\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
-\end{centering}
-\end{figure*}
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
-\caption{Cleaned Kepler Long-cadence data and PCA analysis.}\label{fig:kepPCA}
-\end{centering}
-\end{figure*}
-
 \subsection{Specmatch}\label{sec:SpecMatch}
@@
 The effective temperature and radii show clear global minima.}\label{fig:specMatch}
+\end{centering}
+\end{figure*}
+
+\clearpage
+
+\section{Kepler Re-analysis}
+We examine the 17 total quarters of Kepler data.
+There is not detectable secondary eclipse at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
+The constraint is even tighter assuming a circular orbit.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
+\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
+\end{centering}
+\end{figure*}
+
+We create a cleaned Kepler long-cadence data set by interpolating all time series data onto a fixed phase grid with a spacing of 30 minutes.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
+\caption{Cleaned Kepler Long-cadence data (Left) and model fit (Right).}\label{fig:kepPCA}
+\end{centering}
+\end{figure*}
+
+We take the dot product ($\bullet$) with the first principal component to create an amplitude time series.
+\begin{equation}
+A = \frac{(f - 1) \bullet c_1}{c_1 \bullet c_1},
+\end{equation}
+where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $c_1$ is the vector of the first principal component .
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
+\includegraphics[width=0.45\textwidth]{images/kepler/amplitude_series.pdf}
+\caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:secEclipse}
 \end{centering}

### 2018-04-17 ms.tex
added a histo plot for K1255 amplitudes.

@@
 
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
+\caption{Histogram of transit amplitudes.
+An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
+A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.}\label{fig:secEclipse}
+\end{centering}
+\end{figure*}
+
 \section{Conclusions}\label{sec:conclusions}

### 2018-04-18 ms.tex
added updated histograms and periodogram.

@@
 \includegraphics[width=0.45\textwidth]{images/kepler/amplitude_series.pdf}
-\caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:secEclipse}
+\caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:PCAamp}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
+\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:PCAamp}
+Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
+The peak at 0.65 days is the orbital period.
+The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.}\label{fig:periodogram}
 \end{centering}
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
-\caption{Histogram of transit amplitudes.
+\includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
+\caption{(Lef) Histogram of transit amplitudes.
 An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
-A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.}\label{fig:secEclipse}
+A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.
+(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histoGrams}
 \end{centering}

### 2018-04-19 ms.tex
more description of Kepler analysis.

@@
 \section{Kepler Re-analysis}
-We examine the 17 total quarters of Kepler data.
-There is not detectable secondary eclipse at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
+We examine the 17 total quarters of Kepler data for three purposes:
+\begin{enumerate}
+	\item To understand the statistics of the transits and put our 2013-2016 observations in context. Mainly, how likely/unlikely were the weak transits observed in 2013-2014?
+	\item To measure the radius of the planet or put an upper limit on its radius by examining any possible transit beneath the dust signal
+	\item Identify any new patterns or observations from the Kepler data that might occur along the way
+\end{enumerate}
+
+We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009-05-13 and ending on 2013-04-08 for a total of 1425 days or 2181.5 orbits.
+The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
+A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 with thin the $\pm$ 0.28 window.
+All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
+The secondary eclipses are used to quantify the noise in the transit depths.
+
+We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
 The constraint is even tighter assuming a circular orbit.
@@
 \includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
-\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
+\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
+Here the data are binned to orbital phases of 0.1 or 1.5 minutes and errors calculated from the standard error in the mean of the data.
+}\label{fig:secEclipse}
 \end{centering}
@@
 
-We create a cleaned Kepler long-cadence data set by interpolating all time series data onto a fixed phase grid with a spacing of 30 minutes.
+In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
+We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 30 minutes and put together all the time series that have no gaps into this two dimensional grid.
+This cleaned Kepler long-cadence array is shown in Figure \ref{fig:kepPCA}.
 

### 2018-04-21 ms.tex
additional intro material and description of photometry.

@@
 These unusual light curve behaviors are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
-The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.
+The KIC 12557548 system (hereafter \shStar) has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.
 
@@
 KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
-RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planet candidates.
-RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
+RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planet candidates or structures within a protoplanetary disk.
+RIK-210 could be accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
 
 The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
-High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
+High precision radial velocity measurements of the host star with Keck/HIRES put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
+\citet{masuda2018rvKIC1255} find that the upper limit on the radial velocity semi-amplitude is 86 km/s corresponding to a planet mass $\lesssim 0.28 M_{\mathrm Jup}$ using the Subaru High Dispersion Spectrometer (HDS).
 There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
-The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
+The timescale of the variability of the transits gives a mass lot rate of $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
 
@@
 12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
+The reference stars are identified in Figure \ref{fig:refStars}.
 These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \sha.
@@
 For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
-I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
+We combined the flat fields and bias files with a a sigma-clipped average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
 
@@
 \begin{centering}
-\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
-\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
+\includegraphics[width=0.49\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
+\includegraphics[width=0.49\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
 \caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
 The reference stars were chosen to have similar count levels as the source. 
-}\label{fig:ut2016-07-14cloudImg}
+}\label{fig:refStars}
 \end{centering}
@@
 
-All nights light curves are shown in Figure \ref{fig:allNightallStar}.
-These are the same reference stars shown in Figure \ref{fig:ut2016-07-14cloudImg}.
-The nights two nights in June, 2016 show greater overall stability than the ones in July, 2016.
-I suspect that this can mostly be explained by moisture and clouds (such as the ones that caused huge drops in flux on UT2016-07-14.
+All light curves are shown in Figure \ref{fig:allNightallStar}.
+These are the same reference stars shown in Figure \ref{fig:refStars}.
+The nights two nights 2016-06-12 and 2016-06-14 show greater overall stability than the ones in July, 2016.
+We suspect that the higher moisture levels and occasional cloud passages (such as the ones that caused huge drops in flux on UT2016-07-14) affected the later observations.
 
@@
 
-Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all 5 nights which were timed with transits.
+Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all nights.
 We use the following planet transit ephemeris, using the flux minimum ``transit center'' from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
@@
 where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.
+The expected transit epochs from the ephemeris in \citep{vanWerkhoven2014} are shown for reference as vertical red bars.
+Typical uncertainties for the Kepler ephemeris are $\sim$ 1 minute at these dates due to the large number of transits measured by the Kepler observatory over nearly 4 years.
+The ``transit duration'' from Kepler light curves is around 0.05 days, which is consistent with these transit durations.
 
-The expected transit epochs from the ephemeris in \citep{vanWerkhoven2014} are shown for reference.
-Typical uncertainties for the Kepler ephemeris are $\sim$ 1 minute at these dates (considering only the uncertainty in period since the transit center is ill-defined).
-The ``transit duration'' from Kepler light curves is around 0.05 days, which is consistent with these transit durations.
+We also overlay the average Kepler short cadence light curves on the measured light curves.
+To ease the comparison of the average Kepler light curve and measured data, we bin the 61-inch Mont4K data into 20 minute long bins.
+Obvious cosmic ray outliers were discarded by removing points with fluxes below 0.98 and above 1.02 times the median flux.
+The error bars for the binned data are calculated from the standard error in the mean for each bin.
+When comparing the average Kepler Short Cadence light curve and the measured light curves that the measured light curves represent typical KIC 12557548 b transits.
+Only 2016-06-14 appears to have a non-detection.
 

### 2018-04-22 ms.tex
more details on 61-inch observing.

@@
 \section{Observations}
-We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
+We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory located on Mt Bigelow, Arizona on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
+On all nights we used 90 second exposures using a Harris-R filter to best approximate the $r'$ filter used in \citet{schlawin2016kic1255}.
 The nights were clear with the exception of a few passing clouds on 2016-07-14.
@@
 Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
+The data was taken in a 3x3 binning mode resulting in an effective 0.43"/pixel plate scale.
+We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.
 
@@
 
-All light curves are shown in Figure \ref{fig:allNightallStar}.
+All light curves for \shStar\ and the 12 reference stars are shown in Figure \ref{fig:allNightallStar}.
 These are the same reference stars shown in Figure \ref{fig:refStars}.
-The nights two nights 2016-06-12 and 2016-06-14 show greater overall stability than the ones in July, 2016.
+The two nights 2016-06-12 and 2016-06-14 show greater overall stability than the ones in July, 2016.
 We suspect that the higher moisture levels and occasional cloud passages (such as the ones that caused huge drops in flux on UT2016-07-14) affected the later observations.

### 2018-04-25 ms.tex
added an example fit for 2016-06-12.
added additional fits.

@@
 
-\begin{deluxetable}{lr}
+\begin{deluxetable}{lrr}
 \tablecaption{List of observations}\label{tab:photSummary}
@@
 \colhead{UT} & \\
+\colhead{Amplitude} & \\
  }
 \startdata
-2016-06-10 & Clouds \\
-2016-06-12 & Clear \\
-2016-06-14 & Clear \\
-2016-07-12 & Clear \\
-2016-07-14 & Mostly clear \\
-2016-07-16 & Clear \\
+2016-06-10 & Clouds	& \\
+2016-06-12 & Clear 		& \\
+2016-06-14 & Clear 		&\\
+2016-07-12 & Clear 		&\\
+2016-07-14 & Mostly clear	& \\
+2016-07-16 & Clear 		& \\
 \enddata
@@
 Transits are clearly visible for all five nights except for UT2016-06-14.}\label{fig:allNightrefCorrect}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}
+\begin{centering}
+\includegraphics[width=0.9\textwidth]{images/tser_fits/best_fit_all.pdf}
+\caption{Best-fit for all nights.}\label{fig:fitAll}
 \end{centering}

### 2018-04-26 ms.tex
added table of fit results.

@@
 \colhead{Date} &
-\colhead{Comment} \\
-\colhead{UT} & \\
-\colhead{Amplitude} & \\
+\colhead{Weather} &
+\colhead{Amplitude} \\
+\colhead{UT} & & \\
  }
 \startdata
-2016-06-10 & Clouds	& \\
-2016-06-12 & Clear 		& \\
-2016-06-14 & Clear 		&\\
-2016-07-12 & Clear 		&\\
-2016-07-14 & Mostly clear	& \\
-2016-07-16 & Clear 		& \\
+2016-06-10 & Clouds	& \nodata \\
+2016-06-12 & Clear 		& 0.94 $\pm$ 0.16 \\
+2016-06-14 & Clear 		&0.70 $\pm$ 0.18\\
+2016-07-12 & Clear 		& 0.78 $\pm$ 0.14 \\
+2016-07-14 & Mostly clear	& 1.33 $\pm$ 0.14 \\
+2016-07-16 & Clear 		& 2.14 $\pm$ 0.19 \\
 \enddata

### 2018-04-27 ms.tex
now I show a comparison of the 3 distributions.

@@
 \includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
-\caption{(Lef) Histogram of transit amplitudes.
+\caption{(Left) Histogram of transit amplitudes.
 An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
 A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.
-(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histoGrams}
+(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histograms}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
+\caption{Distributions from 2 photometric campaigns and the Kepler data.}\label{fig:histoPhot}
 \end{centering}

### 2018-04-28 ms.tex
KS tests and better comparison histogram.

@@
 \includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
-\caption{Distributions from 2 photometric campaigns and the Kepler data.}\label{fig:histoPhot}
+\caption{Normalized frequency of 3 different distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 3) the 5 night Kuiper observatory campaign in the summer of 2016.
+The \citet{schlawin2016kic1255} (S16) evens give a Kolmogorov Smirnov p value of 0.001 of the null hypothesis that the S16 results are drawn from the same distribution as the Kepler Long Cadence.
+In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.}\label{fig:histoPhot}
 \end{centering}

### 2018-04-28 ms.tex
added a plot w/ residuals revealing that the timing might be changing.

@@
 The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
-A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 with thin the $\pm$ 0.28 window.
+A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 window.
 All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
@@
 We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
-The constraint is even tighter assuming a circular orbit.
+We then use the secondary eclipses as a way to characterize the noise of the primary eclipses.
+Both have the same quadratic baseline removal process over the same time intervals.
 
@@
 \caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
-Here the data are binned to orbital phases of 0.1 or 1.5 minutes and errors calculated from the standard error in the mean of the data.
+Here, the data are binned to orbital phases of 0.1 or 1.5 minutes and errors calculated from the standard error in the mean of the data within a bin.
 }\label{fig:secEclipse}
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
-\caption{Cleaned Kepler Long-cadence data (Left) and model fit (Right).}\label{fig:kepPCA}
+\includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
+\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
+The residual is shown with a different scaling below.
+In this fitting process, no adjustments were made for timing, which is apparent in the residuals.}\label{fig:kepPCA}
 \end{centering}

### 2018-04-28 ms.tex
added some more on specmatch results.

@@
   \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
-  This work - Specmatch	& 4500 	& 4.63	& main-sequence star & high-resolution spectroscopy\\
+  This work - Specmatch	& 4500 $\pm$110 	& 4.63 $\pm$ 0.1 & main-sequence star & high-resolution spectroscopy\\
   This work - BOSZ		& 4500	& 4.5		& main-sequence star & high-resolution spectroscopy\\
@@
 The effective temperature radius show clear global $\chi^2$ minima for the HIRES spectral libraries.
-The resulting best-fit parameters are T$_{eff}$=4500 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$.
+The resulting best-fit parameters are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$.
 We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}.
@@
 The effective temperature and radii show clear global minima.}\label{fig:specMatch}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.8\textwidth]{images/subaru/lincomb_kic1255.pdf}
+\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:specMatch}
 \end{centering}

### 2018-04-29 ms.tex
phase shift analysis.

@@
 
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.99\textwidth]{images/kepler/phase_shifts.pdf}
+\caption{Time Series of phase shifts.}\label{fig:phaseShift}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/phase_shift_vs_amplitude.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/phase_shifts_periodogram.pdf}
+\caption{Phase shifts versus amplitude (left) and phase shift periodogram (right).}\label{fig:phaseShift}
+\end{centering}
+\end{figure*}
+
 \section{Conclusions}\label{sec:conclusions}

### 2018-05-01 ms.tex
somme analysis of residuals after model subtraction.

@@
 \includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/residual_after_shifted_model.pdf}
 \caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
-The residual is shown with a different scaling below.
-In this fitting process, no adjustments were made for timing, which is apparent in the residuals.}\label{fig:kepPCA}
+(Bottom Left) The residual is shows some periodic behavior.
+(Bottom Right) If we allow for shifting in the model with cross-correlation, the periodic behavior is even stronger.
+This is likely an erroneous alias caused by a an early typo in the phase grid of 30 seconds instead of 30 minutes.}\label{fig:riverPlots}
 \end{centering}

### 2018-05-02 ms.tex
More PCA and periodogram descrip. Also corrected sampling

@@
 \caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
-Here, the data are binned to orbital phases of 0.1 or 1.5 minutes and errors calculated from the standard error in the mean of the data within a bin.
+Here, the data are binned to orbital phases of 0.1 (1.5 minutes) and errors calculated from the standard error in the mean of the data within a bin.
 }\label{fig:secEclipse}
@@
 In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
-We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 30 minutes and put together all the time series that have no gaps into this two dimensional grid.
-This cleaned Kepler long-cadence array is shown in Figure \ref{fig:kepPCA}.
+We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 15 minutes (to Nyquist sample the 30 minute observation cadence) and put together all the time series that have no gaps into this two dimensional grid.
+This cleaned Kepler long-cadence array is shown in Figure \ref{fig:riverPlots}.
 
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/residual_after_shifted_model.pdf}
 \caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
-(Bottom Left) The residual is shows some periodic behavior.
+(Bottom) The residual is shows some periodic behavior.
 (Bottom Right) If we allow for shifting in the model with cross-correlation, the periodic behavior is even stronger.
@@
 
+We also perform PCA along the time axis.
+This gives the principal components shown in Figure \ref{fig:PCAtime}.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_time_direction.pdf}
+\caption{Principal components for orbital phase when working along the time axis.}\label{fig:PCAtime}
+\end{centering}
+\end{figure*}
+
+In Figure \ref{fig:ampPeriodogram} we show the periodogram of amplitudes that have peaks at 0.654, 22.9, 153 and 750 days.
+The 22.9 day peak is consistent with the \citet{kawahara2013starspots} that shows amplitudes are anti-correlated with
+
 \begin{figure*}[!hbtp]
@@
 Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
-The peak at 0.65 days is the orbital period.
-The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.}\label{fig:periodogram}
+The peak at 0.654 days is the orbital period.
+The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
+The 22.9 day peak is consistent with the \citet{kawahara2013starspots} peak that is co-incident with the stellar rotation period.}\label{fig:PCAamp}
 \end{centering}

### 2018-05-03 ms.tex
some more details on spectroscopy and added a row to the parameters table.

@@
   \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
+  \citet{morton2016falsePos} & 4677 		& 4.61		& main-sequence star	& photometry \\
   This work - Specmatch	& 4500 $\pm$110 	& 4.63 $\pm$ 0.1 & main-sequence star & high-resolution spectroscopy\\
@@
 The host star \shStar\ has been characterized by both photometry and spectroscopy.
-Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
+Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from .
 In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
@@
 We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
-There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
-Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system.
-Both of these observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
+There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 4 exposures each 2700 seconds in duration.
+Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
+The second set of observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
 
@@
 The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
-The 22.9 day peak is consistent with the \citet{kawahara2013starspots} peak that is co-incident with the stellar rotation period.}\label{fig:PCAamp}
+The 22.9 day peak is consistent with the \citet{kawahara2013starspots} peak that is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
 \end{centering}

### 2018-05-04 ms.tex
added a few notes on resolution and added a better match between resolution of models and data.

@@
 There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 4 exposures each 2700 seconds in duration.
+For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
 Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
+The instrument 
 The second set of observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
@@
 \subsection{Independent Reduction}
-K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
+K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations \citep{masuda2018rvKIC1255}.
 This more sophisticated reduction masks all telluric emission features and any outliers, producing cleaner spectra.
@@
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
-\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
+\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\caption{Median spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
 \end{centering}

### 2018-05-04 ms.tex
more background added to the intro.

@@
 \author{Hajima Kawahara?}
-\affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan;}
+\affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan}
+
+\author{Johanna Teske?}
+\affiliation{Department of Terrestrial Magnetism, Carnegie Institution for Science, 5241 Broad Branch Road, NW, Washington, DC 20015}
 
@@
 Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
-We also evaluate high resolution spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 K, main-sequence star.	
+We also evaluate high resolution spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K, main-sequence star.	
 \end{abstract}
@@
 
-The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
+The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding planet evolution and composition.
 Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
@@
 There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
-The timescale of the variability of the transits gives a mass lot rate of $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
+A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$, the modeled mass is 0.014 $M_\oplus$.
+
+One possible explanation of for the planet disintegration is that it is tied to stellar activity.
+\citet{kawahara2013starspots} found an anti-correlation between stellar flux and the depth of transit events, which suggested that the alignment of the planet's position (true anomaly) causes disintegration.
+The alignment of spots and disintegration activity could be due to XUV photoevaporation or magnetic reconnection events.
+The anti-correlation between stellar flux and transit depth was confirmed by \citet{croll2015starspots} though they find that occultations of star spots can also modulate the transit depth at the 22.9 day rotation period of the star.
 
@@
 \citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
-There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month.
+There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month in duration.
 
-Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
+The Kepler data was used to put constraints on the particle size distribution and composition of the dust particles.
+\citet{budaj12} and \citet{brogi2012} modeled the light curve, which includes a slight increase in flux prior before the transit begins.
+This pre-ingress flux increase is caused by forward scattering dust particles and the scattering function is sensitive to particle size modulo composition.
+\citet{budaj12} and \citet{brogi2012} find particle sizes $\sim$0.1 to $\sim$1.0$\mu$m in size based on this method.
+Subsequently, \citet{croll2014} obtained a $K'$-band light curve simultaneously with the Kepler spacecraft to put a constraint on the dust extinction as a function of wavelength.
+\citet{croll2014} find a particle size distribution of $\gtrsim 0.5\mu$m.
+
+\citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
 \citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
@@
 We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.
+We also examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to improve the stellar parameters from the data.
 
@@
 The host star \shStar\ has been characterized by both photometry and spectroscopy.
-Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from .
+Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from \citet{morton2016falsePos} and this work.
 In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
@@
 \begin{enumerate}
-	\item To understand the statistics of the transits and put our 2013-2016 observations in context. Mainly, how likely/unlikely were the weak transits observed in 2013-2014?
+	\item To understand the statistics of the transits and put the 2013-2016 observations in context. Mainly, how likely/unlikely were the weak transits observed in 2013-2014?
 	\item To measure the radius of the planet or put an upper limit on its radius by examining any possible transit beneath the dust signal
@@
 The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
-A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 window.
+A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 phase window.
 All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
@@
 \section{Acknowledgements}
-Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
+%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
 %Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the 61-inch Kuiper telescope on Mt Bigelow.
-MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
+%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
 Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.

### 2018-05-06 ms.tex
more description of PCA

@@
 
+We start by taking the average transit light curve of all the long cadence data (the mean of the 2D grid along the transit number axis).
+We then take the dot product ($\bullet$) with this average light curve to create an amplitude time series.
+\begin{equation}
+A = \frac{(f - 1) \bullet a}{a \bullet a},
+\end{equation}
+where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
+This dot product is then multiplied by the average transit light curve to create a 2D model grid.
+The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve.
+
 \begin{figure*}[!hbtp]
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
-\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
-(Bottom) The residual is shows some periodic behavior.
-(Bottom Right) If we allow for shifting in the model with cross-correlation, the periodic behavior is even stronger.
-This is likely an erroneous alias caused by a an early typo in the phase grid of 30 seconds instead of 30 minutes.}\label{fig:riverPlots}
+\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using the average light curve (Top Right).
+(Bottom) The residuals show significant deviations at phases of -0.5 and 0.05.
+}\label{fig:riverPlots}
 \end{centering}
@@
 
-We take the dot product ($\bullet$) with the first principal component to create an amplitude time series.
-\begin{equation}
-A = \frac{(f - 1) \bullet c_1}{c_1 \bullet c_1},
-\end{equation}
-where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $c_1$ is the vector of the first principal component .
+As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
+We start by rescaling the two dimensional grid to have zero mean and a variance of 1.0 along the Transit Number axis.
+Next, we perform PCA on the two dimensional grid to identify eigenvectors as a function of orbital phase and then the principal components as a function of transit number.
 

### 2018-05-07 ms.tex
plots showing PCA model and residuals.

@@
 
+\subsection{Kepler Secondary Eclipse}
+
 We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
@@
 
+\subsection{PCA Analysis}
+
 In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
@@
 This dot product is then multiplied by the average transit light curve to create a 2D model grid.
-The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve.
+The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve below.
 
@@
 As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
-We start by rescaling the two dimensional grid to have zero mean and a variance of 1.0 along the Transit Number axis.
+We start by rescaling the two dimensional grid to have zero mean and a variance of 1.0 along the Transit Number axis, while saving the transformation to return to the original flux units.
+This first rescaling step will remove the constants from the transit light curve (such as the planet candidate's transit curve).
 Next, we perform PCA on the two dimensional grid to identify eigenvectors as a function of orbital phase and then the principal components as a function of transit number.
@@
 \caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:PCAamp}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_model_2D.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_resid_2D.pdf}
+\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
+(Bottom) The residuals show smaller residuals than the average model.
+}\label{fig:riverPlotsPCA}
 \end{centering}

### 2018-05-08 ms.tex
more on HDS spectra.

@@
   \citet{morton2016falsePos} & 4677 		& 4.61		& main-sequence star	& photometry \\
+  \citet{vanlieshout2016kic1255} & 		& $\gtrsim 4.4$	& main-sequence star	& transit light curve \\
   This work - Specmatch	& 4500 $\pm$110 	& 4.63 $\pm$ 0.1 & main-sequence star & high-resolution spectroscopy\\
@@
 
-We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
-There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 4 exposures each 2700 seconds in duration.
+We evaluate the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
+There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
 For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
 Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
-The instrument 
+The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
 The second set of observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
+None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).
 
@@
 Figure \ref{fig:prof2013vs2015} shows an example blue-chip images from 2013 and 2015.
-The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000)\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/ume/node16.html} has a sharper PSF and and is easier to trace.
-The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
+The 2015 data, with a narrow slit (0.3 $\times$ 30 mm, has a sharper PSF and and is easier to trace.
+The 2013 data was taken with  an image slicer, which create 3 parallel traces for \shStar.
 The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
@@
 
-The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
-\citet{kawahara2013starspots} find a log(g) = 3.9 $\pm$ 0.2, whereas \citet{rappaport} find a log(g)=4.63.
+The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts (or variability in interpretation due to planet disintegration) in the literature about the gravity of the host star as listed in Table \ref{tab:stellObsParams}.
 To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
@@
 In figure \ref{fig:CaILine} we zoom in on the Ca I 6162 $\AA$ feature.
-Again, there is no clear match to either BOSZ model.
+Again, there is no clear match to either HIGHRES model.
 

### 2018-05-09 ms.tex
cleaning up the description of the Subaru data.

@@
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/out_HDSA00094087.pdf}
-\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/HDSA00111345.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
-\caption{Spectra images from 2013 versus 2015.
-The PSF profile (bottom panel) is much wider in 2013 because an image slicer creates 3 traces for the one star.
-In 2015, a narrow slit is used instead.}\label{fig:prof2013vs2015}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec_interp.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec.pdf}
-\caption{{\it Top:} Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
-There are many bad pixels, which are preliminarily discarded for fluxes above 1.25.
-{\it Bottom:} The measured spectrum is convolved with a Gaussian kernel to match the resolution of the HIGHRES models which are calculated for log(g)=4.5 and 4.0.
-The measured Na D$_1$ and D$_2$ lines are deeper than either model, but have similar line ratios to the 4500 K log(g)=4.5 model.}\label{fig:naDlines}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
-\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
-\caption{Example spectrum of \shStar\ near the Mg triplet.
-{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
-The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
-{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
-The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios but not the strength of the features.}\label{fig:mgTriplet}
-\end{centering}
-\end{figure}
-
 \section{Stellar Characterization}
@@
 \begin{deluxetable*}{lcrrr}
-\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
+\tablecaption{Observational estimates of the stellar parameters of \shStar, adapted from \citet{vanlieshout2016kic1255}}
 \tablewidth{0pt}
@@
 The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
-The second set of observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
+The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
 None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).
 
-\subsection{Independent Iraf Reduction}
-
-In one independent analysis (E Schlawin), we we follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
-Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
-We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
-
-The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
-Figure \ref{fig:prof2013vs2015} shows an example blue-chip images from 2013 and 2015.
-The 2015 data, with a narrow slit (0.3 $\times$ 30 mm, has a sharper PSF and and is easier to trace.
-The 2013 data was taken with  an image slicer, which create 3 parallel traces for \shStar.
-The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
-For wavelength identification, a Thorium Argon reference is used.
-(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
-The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
-The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
-The final rms in this wavelength solution is 0.0021 $\AA$.
-After the reference spectrum is used to find a wavelength solution, the spectrum is examined near some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).
-
-\subsection{Comparison to Templates}
-
-The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts (or variability in interpretation due to planet disintegration) in the literature about the gravity of the host star as listed in Table \ref{tab:stellObsParams}.
-To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
-Also, we interpolated over any pixels above a normalized flux of 2.0 in Figure \ref{fig:mgTriplet} (top).
-Then, we convolve with a Gaussian kernel with a standard deviation of 6 pixels.
-
-The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES, but not the line strengths.
-In figure \ref{fig:CaILine} we zoom in on the Ca I 6162 $\AA$ feature.
-Again, there is no clear match to either HIGHRES model.
-
-\begin{figure}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/CaI6162_spec.pdf}
-\caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:CaILine}
-\end{centering}
-\end{figure}
-
-\subsection{Independent Reduction}
-K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations \citep{masuda2018rvKIC1255}.
-This more sophisticated reduction masks all telluric emission features and any outliers, producing cleaner spectra.
+\subsection{Data Reduction}
+The Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations \citep{masuda2018rvKIC1255}.
+All telluric emission features and outliers are masked in this analysis to remove these components.
 Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
@@
 
-\clearpage
 \subsection{Comparison to BOSZ}
@@
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\includegraphics[width=0.7\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
 \caption{Median spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}

### 2018-05-09 ms.tex
updated PCA with non-standardized version.

@@
 
-\subsection{PCA Analysis}
+\subsection{Average Light Curve Analysis}
 
@@
 \begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
-\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using the average light curve (Top Right).
-(Bottom) The residuals show significant deviations at phases of -0.5 and 0.05.
+\includegraphics[width=0.3\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.3\textwidth]{images/kepler/model_riverplot.pdf}
+\includegraphics[width=0.3\textwidth]{images/kepler/residual_riverplot.pdf}
+\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
+(Right) The residuals show significant deviations at phases of -0.5 and 0.05.
 }\label{fig:riverPlots}
@@
 
+\subsection{Principal Component Analysis}
+
 As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
-We start by rescaling the two dimensional grid to have zero mean and a variance of 1.0 along the Transit Number axis, while saving the transformation to return to the original flux units.
-This first rescaling step will remove the constants from the transit light curve (such as the planet candidate's transit curve).
+Here, we are assuming that the grid of orbital phases (spaced by 15 minutes) contains random correlated variables with different realizations along the transit number axis.
+The first principal component eigenvector is the linear combination of these random variables that maximizes the variance in the data.
+The second principal component eigenvector is the linear combination of these random variables with the next-highest variance while being orthogonal to the first principal component.
+This continues up to some finite number of principal components, with the hope that we can use just a few orthogonal light curves to adequately describe the data \citep[e.g.][]{jolliffe2002pca}.
+We use the Python package \texttt{scikit-learn} \citep{pedregosa2011scikit-learn} to calculate the principal components and eigenvectors.
+
+It is customary with PCA to scale the variables to have zero mean and a variance of 1.0 (ie. along the Transit Number axis) before performing PCA.
+However, we elect to keep the original variables without scaling each column in this 2D grid by its standard deviation, since that would magnify the contribution of photon noise in out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.1 to $\sim$ 0.1).
 Next, we perform PCA on the two dimensional grid to identify eigenvectors as a function of orbital phase and then the principal components as a function of transit number.
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
-\includegraphics[width=0.45\textwidth]{images/kepler/amplitude_series.pdf}
-\caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:PCAamp}
+\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
+\caption{Principal component eigenvectors (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scatterg.
+The first two principal components (Right) do not isolate any separate populations of transits.
+As expected, the quiescent periods show up as low principal component contributions from both of the two eigenvectors (ie. a flatter light curve)}.
 \end{centering}
@@
 
+\facility{Subaru}
+
+\software{astropy \citep{astropy2013}, 
+	\texttt{scikit-learn} \citep{pedregosa2011scikit-learn},
+	\texttt{iraf},
+	\texttt{specmatch} tool \citep{yee2017specMatch} 
+          %\texttt{emcee} \citep{foreman-mackey2013emcee}, 
+          }
+
 %% Appendix material should be preceded with a single \appendix command.

### 2018-05-10 ms.tex
updated PCA model plots and added software citations.

@@
 \begin{centering}
-\includegraphics[width=0.3\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.3\textwidth]{images/kepler/model_riverplot.pdf}
-\includegraphics[width=0.3\textwidth]{images/kepler/residual_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
 \caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
@@
 \begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_model_2D.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_resid_2D.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
 \caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
-(Bottom) The residuals show smaller residuals than the average model.
+(Right) The residuals show smaller residuals than the average model.
 }\label{fig:riverPlotsPCA}
-\end{centering}
-\end{figure*}
-
-We also perform PCA along the time axis.
-This gives the principal components shown in Figure \ref{fig:PCAtime}.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_time_direction.pdf}
-\caption{Principal components for orbital phase when working along the time axis.}\label{fig:PCAtime}
 \end{centering}
@@
 
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.99\textwidth]{images/kepler/phase_shifts.pdf}
-\caption{Time Series of phase shifts.}\label{fig:phaseShift}
-\end{centering}
-\end{figure*}
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/phase_shift_vs_amplitude.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/phase_shifts_periodogram.pdf}
-\caption{Phase shifts versus amplitude (left) and phase shift periodogram (right).}\label{fig:phaseShift}
-\end{centering}
-\end{figure*}
+%\begin{figure*}[!hbtp]
+%\begin{centering}
+%\includegraphics[width=0.99\textwidth]{images/kepler/phase_shifts.pdf}
+%\caption{Time Series of phase shifts.}\label{fig:phaseShift}
+%\end{centering}
+%\end{figure*}
+%
+%
+%\begin{figure*}[!hbtp]
+%\begin{centering}
+%\includegraphics[width=0.49\textwidth]{images/kepler/phase_shift_vs_amplitude.pdf}
+%\includegraphics[width=0.49\textwidth]{images/kepler/phase_shifts_periodogram.pdf}
+%\caption{Phase shifts versus amplitude (left) and phase shift periodogram (right).}\label{fig:phaseShift}
+%\end{centering}
+%\end{figure*}
 

### 2018-05-17 ms.tex
added some observing details in a table.

@@
 High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
-\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis, which in turn constrains the density of the star when combined with Kepler's third law \citep{seager2003uniqueSolution}.
+\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis in terms of stellar radii, which can be combined with Kepler's third law to calculate the stellar density \citep{seager2003uniqueSolution}.
 \citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
@@
 If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
+In this section, we analyze available high resolution spectra to put new constraints on the stellar temperature and surface gravity.
 
@@
 For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
-Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
+Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
 The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
 The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
+The orbital phases during the observations were in the range f
 None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).
+
+\begin{deluxetable}{cccccccc}
+\tablefontsize{\scriptsize}
+\tablehead{\colhead{Exposure Number} & \colhead{ExpTime} & \colhead{UT Date} & \colhead{UT Start} & \colhead{Image Slicer} & \colhead{Slit Width} & \colhead{Orbital Phase} & \colhead{Resolving Power}\\
+	& (s)	& & & & (mm) & & R}
+\startdata
+94085 & 2700 &  2013 Jun 22 & 00:32 & 2 & 2.0 & 0.621 & 80,000 \\
+94087 & 2700 &  2013 Jun 22 & 00:18 & 2 & 2.0 & 0.670 & 80,000 \\
+111345 & 2400 & 2015 Aug 28 & 00:37 & N & 0.3 & 0.667 & 60,000 \\
+111349 & 2303 & 2015 Aug 28 & 00:20 & N & 0.3 & 0.712 & 60,000 \\
+111355 & 2400 & 2015 Aug 28 & 00:33 & N & 0.3 & 0.790 & 60,000 \\
+111359 & 2400 & 2015 Aug 28 & 00:16 & N & 0.3 & 0.835 & 60,000 \\
+111373 & 2400 & 2015 Aug 28 & 00:18 & N & 0.3 & 0.901 & 60,000 \\
+111525 & 2400 & 2015 Aug 29 & 00:35 & N & 0.3 & 0.194 & 60,000 \\
+111529 & 2400 & 2015 Aug 29 & 00:18 & N & 0.3 & 0.240 & 60,000 \\
+111533 & 2400 & 2015 Aug 29 & 00:00 & N & 0.3 & 0.285 & 60,000 \\
+111549 & 2400 & 2015 Aug 29 & 00:32 & N & 0.3 & 0.382 & 60,000 \\
+111553 & 2400 & 2015 Aug 29 & 00:15 & N & 0.3 & 0.428 & 60,000 \\
+\enddata
+\end{deluxetable}
 

### 2018-05-18 ms.tex
updated PCA based on some of the info from Jolliffe book.

@@
 
-It is customary with PCA to scale the variables to have zero mean and a variance of 1.0 (ie. along the Transit Number axis) before performing PCA.
-However, we elect to keep the original variables without scaling each column in this 2D grid by its standard deviation, since that would magnify the contribution of photon noise in out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.1 to $\sim$ 0.1).
-Next, we perform PCA on the two dimensional grid to identify eigenvectors as a function of orbital phase and then the principal components as a function of transit number.
+We use a covariance matrix as opposed to correlation matrix to calculate the principal component eigenvectors.
+In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
+However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
+If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.12 to $\sim$0.15).
+
+Figure \ref{fig:pcaVectorsComp} shows the calculated 4 eigenvectors as a function of orbital phase and the corresponding 4 principal components as a function of transit number.
+We weight each eigenvectors by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
+The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
 
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
-\caption{Principal component eigenvectors (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scatterg.
+\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scatterg.
 The first two principal components (Right) do not isolate any separate populations of transits.
-As expected, the quiescent periods show up as low principal component contributions from both of the two eigenvectors (ie. a flatter light curve)}.
+As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
 \end{centering}
@@
 The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
-The 22.9 day peak is consistent with the \citet{kawahara2013starspots} peak that is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
+The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
 \end{centering}

### 2018-05-22 ms.tex
few clarifications of the spec observing log.

@@
 The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
-The orbital phases during the observations were in the range f
+We list the observing log in Table \ref{}
 None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).
@@
 \begin{deluxetable}{cccccccc}
+\tablecaption{List of Spectroscopic Observations}
 \tablefontsize{\scriptsize}
@@
 \enddata
+\tablenotetext{}{Observing log of the Subaru HDS spectroscopic observations.}\label{tab:specObs}
 \end{deluxetable}
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
-\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scatterg.
+\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
 The first two principal components (Right) do not isolate any separate populations of transits.

### 2018-05-24 supplement.tex
added comparison plots between TH and ES reductions.

@@
 The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
-Figure \ref{fig:prof2013vs2015} shows example blue-chip images from 2013 and 2015.
-The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000)\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/ume/node16.html} has a sharper PSF and and is easier to trace.
-The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
+Figure \ref{fig:prof2013vs2015} shows an example blue-chip images from 2013 and 2015.
+The 2015 data, with a narrow slit (0.3 $\times$ 30 mm, has a sharper PSF and and is easier to trace.
+The 2013 data was taken with  an image slicer, which create 3 parallel traces for \shStar.
 The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
 For wavelength identification, a Thorium Argon reference is used.
-(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
+(Note to self: The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
+For the blue arm, I find IRAF aperture 1 for the data is Aperture 16, Order 95 in the Subaru HDS Th-Ar atlas.)
+
 The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
@@
 
-The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
-\citet{kawahara2013starspots} find T$_{eff}$=4950 $\pm$ 70 K, whereas \citet{rappaport} find a T$_{eff}$=4400 $\pm$200.
+The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts (or variability in interpretation due to planet disintegration) in the literature about the gravity of the host star as listed in Table \ref{tab:stellObsParams}.
 To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
@@
 Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
-The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
+The median spectrum is visible in Figure \ref{fig:mgTripletBOSZMedianW5000}.
+
+\subsection{Another Reduction}
+T Hirano reduced the 2013 and 2015 data and made these available.
+A comparison of the E Schlawin (ES) and T Hirano (TH) spectra can be seen.
+The
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.9\textwidth]{images/subaru/es_and_th_comparison.pdf}
+\includegraphics[width=0.9\textwidth]{images/subaru/es_and_th_comparison_aperture_22.pdf}
+\caption{(Top Panel): Comparison between the T Hirano spectrum (Aperture 24) and E Schlawin one (Aperture 23).
+There is likely a mistake in the wavelength calibration.
+(Bottom Panel:) Comparing the extracted pixels for Aperture 23 and 24 shows that both recover the Mg Triplet.
+The two are shifted likely because they use different traces and apertures.}\label{fig:CaILine}
+\end{centering}
+\end{figure*}
 

### 2018-05-25 ms.tex
plot comparing 2013 and 2015 data.

@@
 \caption{Linear combination of templates that best matches KIC 1255.}\label{fig:specMatch}
+\end{centering}
+\end{figure*}
+
+We compare the 2013 and 2015 data to search for any variability in the absorption lines.
+Absorption line variability could be caused by variable disintegration activity of the planet and dusty material that sublimates into gas and absorbs against the stellar spectrum.
+We compare the 2013 and 2015 data in Figure \ref{fig:spec2013vs2015}.
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=1.0\textwidth]{images/subaru/2013_vs_2015/2013_vs_2015_spec.pdf}
+\caption{Comparison between the 2013 spectrum and 2015 spectrum of \shStar\ near the Mg I triplet. The two are consistent within the larger noise of the 2013 data.}\label{fig:spec2013vs2015}
 \end{centering}

### 2018-05-26 ms.tex
updates to Subaru description.

@@
 Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
-We also evaluate high resolution spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K, main-sequence star.	
+We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K star.
 \end{abstract}
@@
 
-The host star \shStar\ has been characterized by both photometry and spectroscopy.
+The host star \shStar\ has been characterized by both photometry and spectroscopy to better understand the system and parameters of the disintegrating planet and debris.
 Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from \citet{morton2016falsePos} and this work.
@@
 
-We evaluate the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
+We evaluate the stellar parameters by examining the archival spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
+An observing log of the 3 nights is summarized in Table \ref{tab:specObs}.
 There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
@@
 The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
-The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
-We list the observing log in Table \ref{}
-None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).
+The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\url{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy to assess disintegration activity preceding or following the spectra.
+None of the observations was timed during a primary transit (phase = 0.0) or secondary eclipse (phase = 0.5 for a circular orbit).
 
@@
 \subsection{Data Reduction}
-The Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations \citep{masuda2018rvKIC1255}.
+For the 2015 data, we use the same spectra as in \citep{masuda2018rvKIC1255}.
 All telluric emission features and outliers are masked in this analysis to remove these components.
@@
 All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
-Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
-The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
+To combine the observations, we found the median spectrum for UT dates 2015 Aug 28 and 2015 Aug 29 to robustly combine the data.
+This median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
+
+For the 2013 data, we follow the \texttt{iraf} reduction techniques from the instrument manual V2.0.0  \footnote{\url{https://www.subarutelescope.org/Observing/Instruments/HDS/}}.
+Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
+We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
+
+We performed wavelength calibration with a Thorium Argon reference spectrum.
+The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
 
 \subsection{Comparison to BOSZ}
-The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it should be comparable to measurements without smoothing the Subaru spectra as was necessary for the HIGHRES models above.
-We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
-The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.
+We first evaluate stellar parameters by comparing to the high resolving power ($R=100,000$) BOSZ grids of ATLAS-APOGEE ATLAS9 models \citep{bohlin2017bosz}.
+Since the discrepancies in the literature are mostly differences in the surface gravity (see Table \ref{tab:stellObsParams}), we study the gravity-sensitive Mg triplet near 517 nm.
+The $R=100,000$ models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
+This was a smaller than one might expect from combining inverse resolving powers in quadrature, which would use an $R=75,000 $ kernel.
 
@@
 
-The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
-\textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
-In order for us to compare the BOSZ models and our data, we have to convolve the Subaru spectrum.
-They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
-Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
+We explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
 For each parameter, we change the models by about 2 steps in the BOSZ grid.
@@
 The errors are estimated from the standard deviation of the spectra over the night.
-For now, we ignore the smoothing of the data that creates non-zero off-diagonal terms in the covariance matrix.
 

### 2018-05-27 ms.tex
more tweaks to the spectrum writeup.

@@
 
+We compare the 2013 and 2015 data to search for any variability in the absorption lines, as seen in Figure \ref{fig:spec2013vs2015}.
+Absorption line variability could be caused by disintegration activity of the planet that escapes as dusty material and then sublimates into gas.
+This gas absorption could potentially provide kinematic information on escaping material provided that the sublimated gas has sufficient optical depth.
+We find no statistically significant differences between the 2013 and 2015 spectra, as shown in Figure \ref{fig:spec2013vs2015}.
+We then proceed with the 2015 data to constrain stellar models since it has 6.7 hours of total exposure time compared (compared to 1.5 hours in 2013).
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=1.0\textwidth]{images/subaru/2013_vs_2015/2013_vs_2015_spec.pdf}
+\caption{Comparison between the 2013 spectrum and 2015 spectrum of \shStar\ near the Mg I triplet. The two are consistent within the larger noise of the 2013 data.}\label{fig:spec2013vs2015}
+\end{centering}
+\end{figure*}
+
 \subsection{Comparison to BOSZ}
-We first evaluate stellar parameters by comparing to the high resolving power ($R=100,000$) BOSZ grids of ATLAS-APOGEE ATLAS9 models \citep{bohlin2017bosz}.
+We first evaluate stellar parameters by comparing to the high resolving power ($R=100,000$) BOSZ grids of ATLAS-APOGEE ATLAS9 models \citep{bohlin2017bosz} to the median spectrum from 2015.
 Since the discrepancies in the literature are mostly differences in the surface gravity (see Table \ref{tab:stellObsParams}), we study the gravity-sensitive Mg triplet near 517 nm.
 The $R=100,000$ models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
-This was a smaller than one might expect from combining inverse resolving powers in quadrature, which would use an $R=75,000 $ kernel.
+This was a smaller we expected from combining inverse resolving powers in quadrature, which would imply that an $R=75,000 $ kernel convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
 
@@
 We explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
+The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
 For each parameter, we change the models by about 2 steps in the BOSZ grid.
@@
 
-The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
-A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.
+%A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.
 
@@
 \caption{The BOSZ models are explored over the parameter space to search for a best fit as well as visualize how much each parameter affects the spectrum.
-The final plot shows the best-fit BOSZ model, but it still under-predicts and over-predicts some line strengths.}\label{fig:boszModelParamsMedianSpec}
+The bottom right plot shows the best-fit BOSZ model, but it still under-predicts and over-predicts some line strengths.}\label{fig:boszModelParamsMedianSpec}
 \end{centering}
@@
 
-\subsubsection{$\chi^2$ Minimization}
-We downloaded a grid of BOSZ models with temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
+After initial constraints on the models from the sensitivity to parameters search, we downloaded a grid of BOSZ models with temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
+We found the model with the  $\chi^2$ statistic over the Mg triple lines from 5160 to 51690 $\AA$
 As discussed above, we use an approximate $\chi^2$ statistic over the wavelength range covering the Mg triplet (5160 $\AA$ to 5190 $\AA$).
-The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec}: T=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
+The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
 
@@
 \texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
-As with the comparisons to the BOSZ models, we first convolve the median spectrum from \citet{masuda2018rvKIC1255} with a R=40,000 kernel.
+The median spectrum from 2015 has a resolution of $R=60,000$, which is close to the \texttt{specmatch} grid of $R=55,000$, so we do not convolve the input data for \texttt{specmatch}.
+%We first convolve the median spectrum from \citet{masuda2018rvKIC1255} with a R=40,000 kernel to better match .
 We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.
@@
 \caption{Linear combination of templates that best matches KIC 1255.}\label{fig:specMatch}
-\end{centering}
-\end{figure*}
-
-We compare the 2013 and 2015 data to search for any variability in the absorption lines.
-Absorption line variability could be caused by variable disintegration activity of the planet and dusty material that sublimates into gas and absorbs against the stellar spectrum.
-We compare the 2013 and 2015 data in Figure \ref{fig:spec2013vs2015}.
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=1.0\textwidth]{images/subaru/2013_vs_2015/2013_vs_2015_spec.pdf}
-\caption{Comparison between the 2013 spectrum and 2015 spectrum of \shStar\ near the Mg I triplet. The two are consistent within the larger noise of the 2013 data.}\label{fig:spec2013vs2015}
 \end{centering}

### 2018-05-28 ms.tex
finished editing this run-through of the Subaru spectrum section.

@@
 In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
-High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
+High resolution spectra, however, indicated a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
 \citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis in terms of stellar radii, which can be combined with Kepler's third law to calculate the stellar density \citep{seager2003uniqueSolution}.
@@
 If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
-In this section, we analyze available high resolution spectra to put new constraints on the stellar temperature and surface gravity.
+In this section, we analyze archival high resolution spectra to put new constraints on the stellar temperature and surface gravity.
 
@@
 An observing log of the 3 nights is summarized in Table \ref{tab:specObs}.
-There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
+There is one set of data taken on 2013 June 22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
 For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
-Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
+Additionally, there are two sets of observations from 2015 Aug 28 (UT) and 2015 Aug 29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
 The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
-The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\url{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy to assess disintegration activity preceding or following the spectra.
+The second set of observations happened after the reaction wheel failure on 2013 May 11\footnote{\url{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy to assess disintegration activity preceding or following the spectra.
 None of the observations was timed during a primary transit (phase = 0.0) or secondary eclipse (phase = 0.5 for a circular orbit).
@@
 The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
+This polynomial fit has a RMS error of 0.02$\AA$.
 
@@
 Absorption line variability could be caused by disintegration activity of the planet that escapes as dusty material and then sublimates into gas.
-This gas absorption could potentially provide kinematic information on escaping material provided that the sublimated gas has sufficient optical depth.
+This gas absorption could provide kinematic information on escaping material provided that the sublimated gas has sufficient optical depth.
 We find no statistically significant differences between the 2013 and 2015 spectra, as shown in Figure \ref{fig:spec2013vs2015}.
@@
 \includegraphics[width=1.0\textwidth]{images/subaru/2013_vs_2015/2013_vs_2015_spec.pdf}
-\caption{Comparison between the 2013 spectrum and 2015 spectrum of \shStar\ near the Mg I triplet. The two are consistent within the larger noise of the 2013 data.}\label{fig:spec2013vs2015}
+\caption{Comparison between the 2013 spectrum and 2015 median spectrum of \shStar\ near the Mg I triplet. The two are consistent within the larger noise of the 2013 data.}\label{fig:spec2013vs2015}
 \end{centering}
@@
 Since the discrepancies in the literature are mostly differences in the surface gravity (see Table \ref{tab:stellObsParams}), we study the gravity-sensitive Mg triplet near 517 nm.
-The $R=100,000$ models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
+The $R=100,000$ models are convolved with a Gaussian kernel that has a standard deviation $\sigma_K = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
 This was a smaller we expected from combining inverse resolving powers in quadrature, which would imply that an $R=75,000 $ kernel convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
+We start by comparing the measured spectrum with two BOSZ models in Figure \ref{fig:mgTripletBOSZ}.
+Here, the two BOSZ models are broadly representative of the two types of results in Table \ref{tab:stellObsParams} (log(g)=4.5 and log(g)=4.0).
+The higher gravity log(g)=4.5 model appears to match the data better in terms of line ratios but does not explain all of the line depths in the spectrum.
 
@@
 The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
+This is similar to the log(g)$\approx$4.6, T=4500 stellar parameters derived from photometry and low resolution spectroscopy listed in Table \ref{tab:stellObsParams}.
 
@@
 
-We also use the \texttt{specmatch} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
+We also use the open-source \texttt{specmatch} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
 \texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
-The median spectrum from 2015 has a resolution of $R=60,000$, which is close to the \texttt{specmatch} grid of $R=55,000$, so we do not convolve the input data for \texttt{specmatch}.
-%We first convolve the median spectrum from \citet{masuda2018rvKIC1255} with a R=40,000 kernel to better match .
+%The median spectrum from 2015 has a resolution of $R=60,000$, which is close to the \texttt{specmatch} grid of $R=55,000$, so we do not convolve the input data for \texttt{specmatch}.
 We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.
@@
 Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
-The effective temperature radius show clear global $\chi^2$ minima for the HIRES spectral libraries.
-The resulting best-fit parameters are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$.
-We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}.
+The effective temperature and radius parameters show clear global $\chi^2$ minima for the HIRES spectral libraries.
+However, the metallicity is less well constrained.
+The resulting best-fit parameters from \texttt{specmatch} are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$ and Mass=0.7 $\pm 0.1 $M$_\odot$.
+The output \texttt{specmatch} age constraint of 9.6 $\pm$ 0.2 Gyr is likely an underestimated error in the age.
+Figure \ref{fig:specMatchComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{specmatch}.
 
@@
 
+We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}, which both favor a main-sequence log(g) $\approx$ 4.6 star.
+Our analysis of the median 2015 spectrum therefore indicates that the stellar spectrum shows no strong contamination from planet disintegration activity.
+Unfortunately, this makes diagnosing the gaseous material evaporating from sublimated dust grains challenging to detect.
+A brighter transiting disintegrating system may reveal itself more strongly, if discovered in the TESS field.
+
 \begin{figure*}[!hbtp]
@@
 \includegraphics[width=0.8\textwidth]{images/subaru/lincomb_kic1255.pdf}
-\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:specMatch}
+\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:specMatchComb}
 \end{centering}
@@
 \caption{Normalized frequency of 3 different distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 3) the 5 night Kuiper observatory campaign in the summer of 2016.
-The \citet{schlawin2016kic1255} (S16) evens give a Kolmogorov Smirnov p value of 0.001 of the null hypothesis that the S16 results are drawn from the same distribution as the Kepler Long Cadence.
+The \citet{schlawin2016kic1255} (S16) events give a Kolmogorov Smirnov p value of 0.001 of the null hypothesis that the S16 results are drawn from the same distribution as the Kepler Long Cadence.
 In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.}\label{fig:histoPhot}

### 2018-05-30 ms.tex
incorporated the corrections and suggestions from Kento.

@@
 
-\author{Kento Masuda?}
-\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
+%\author{Kento Masuda?}
+%\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
 
@@
 KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
-Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014.
+Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of disintegration activity in 2013 and 2014.
 Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
@@
 High precision radial velocity measurements of the host star with Keck/HIRES put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
-\citet{masuda2018rvKIC1255} find that the upper limit on the radial velocity semi-amplitude is 86 km/s corresponding to a planet mass $\lesssim 0.28 M_{\mathrm Jup}$ using the Subaru High Dispersion Spectrometer (HDS).
+\citet{masuda2018rvKIC1255} find that the upper limit on the radial velocity semi-amplitude is 86 m/s corresponding to a planet mass $\lesssim 0.28 M_{\mathrm Jup}$ using the Subaru High Dispersion Spectrometer (HDS).
 There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
@@
 \includegraphics[width=0.7\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
-\caption{Median spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
+\caption{Median spectrum of \shStar\ \citep{} near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
 \end{centering}
@@
 %MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
+Thanks to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
 Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
-This research made use of the \texttt{astropy} package \citep{astropy2013}.
 

### 2018-06-01 ms.tex
added a plot with the time series.

@@
 
+Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.99\textwidth]{images/kepler/pc1_tser_w_quiescent.pdf}
+\caption{The first principal component's time series.}\label{fig:tserPC1}
+\end{centering}
+\end{figure*}
+
 In Figure \ref{fig:ampPeriodogram} we show the periodogram of amplitudes that have peaks at 0.654, 22.9, 153 and 750 days.
-The 22.9 day peak is consistent with the \citet{kawahara2013starspots} that shows amplitudes are anti-correlated with
+The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
+As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
 

### 2018-06-02 ms.tex
fixed the UT times in the table, SpecMatch-Emp fix and rearranged figures.

@@
 \startdata
-94085 & 2700 &  2013 Jun 22 & 00:32 & 2 & 2.0 & 0.621 & 80,000 \\
-94087 & 2700 &  2013 Jun 22 & 00:18 & 2 & 2.0 & 0.670 & 80,000 \\
-111345 & 2400 & 2015 Aug 28 & 00:37 & N & 0.3 & 0.667 & 60,000 \\
-111349 & 2303 & 2015 Aug 28 & 00:20 & N & 0.3 & 0.712 & 60,000 \\
-111355 & 2400 & 2015 Aug 28 & 00:33 & N & 0.3 & 0.790 & 60,000 \\
-111359 & 2400 & 2015 Aug 28 & 00:16 & N & 0.3 & 0.835 & 60,000 \\
-111373 & 2400 & 2015 Aug 28 & 00:18 & N & 0.3 & 0.901 & 60,000 \\
-111525 & 2400 & 2015 Aug 29 & 00:35 & N & 0.3 & 0.194 & 60,000 \\
-111529 & 2400 & 2015 Aug 29 & 00:18 & N & 0.3 & 0.240 & 60,000 \\
-111533 & 2400 & 2015 Aug 29 & 00:00 & N & 0.3 & 0.285 & 60,000 \\
-111549 & 2400 & 2015 Aug 29 & 00:32 & N & 0.3 & 0.382 & 60,000 \\
-111553 & 2400 & 2015 Aug 29 & 00:15 & N & 0.3 & 0.428 & 60,000 \\
+94085 & 2700 & 2013 Jun 22 & 12:32 & 2 & 2.0 & 0.621 & 80,000 \\
+94087 & 2700 & 2013 Jun 22 & 13:18 & 2 & 2.0 & 0.670 & 80,000 \\
+111345 & 2400 & 2015 Aug 28 & 05:37 & N & 0.3 & 0.667 & 60,000 \\
+111349 & 2303 & 2015 Aug 28 & 06:19 & N & 0.3 & 0.712 & 60,000 \\
+111355 & 2400 & 2015 Aug 28 & 07:33 & N & 0.3 & 0.790 & 60,000 \\
+111359 & 2400 & 2015 Aug 28 & 08:15 & N & 0.3 & 0.835 & 60,000 \\
+111373 & 2400 & 2015 Aug 28 & 09:17 & N & 0.3 & 0.901 & 60,000 \\
+111525 & 2400 & 2015 Aug 29 & 05:34 & N & 0.3 & 0.194 & 60,000 \\
+111529 & 2400 & 2015 Aug 29 & 06:17 & N & 0.3 & 0.240 & 60,000 \\
+111533 & 2400 & 2015 Aug 29 & 07:00 & N & 0.3 & 0.285 & 60,000 \\
+111549 & 2400 & 2015 Aug 29 & 08:31 & N & 0.3 & 0.382 & 60,000 \\
+111553 & 2400 & 2015 Aug 29 & 09:14 & N & 0.3 & 0.428 & 60,000 \\
 \enddata
@@
 \includegraphics[width=0.7\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
-\caption{Median spectrum of \shStar\ \citep{} near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
+\caption{Median spectrum of \shStar\ \citep{masuda2018rvKIC1255} near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
 \end{centering}
@@
 
-\subsection{Specmatch}\label{sec:SpecMatch}
+\subsection{SpecMatch-Emp}\label{sec:SpecMatch-Emp}
 
-We also use the open-source \texttt{specmatch} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
-\texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
-%The median spectrum from 2015 has a resolution of $R=60,000$, which is close to the \texttt{specmatch} grid of $R=55,000$, so we do not convolve the input data for \texttt{specmatch}.
+We also use the open-source \texttt{SpecMatch-Emp} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
+\texttt{SpecMatch-Emp} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
+%The median spectrum from 2015 has a resolution of $R=60,000$, which is close to the \texttt{SpecMatch-Emp} grid of $R=55,000$, so we do not convolve the input data for \texttt{SpecMatch-Emp}.
 We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.
 
-Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
+Figure \ref{fig:SpecMatch-Emp} shows the chi-squared differences between the median Subaru spectrum and the models.
 The effective temperature and radius parameters show clear global $\chi^2$ minima for the HIRES spectral libraries.
 However, the metallicity is less well constrained.
-The resulting best-fit parameters from \texttt{specmatch} are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$ and Mass=0.7 $\pm 0.1 $M$_\odot$.
-The output \texttt{specmatch} age constraint of 9.6 $\pm$ 0.2 Gyr is likely an underestimated error in the age.
-Figure \ref{fig:specMatchComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{specmatch}.
+The resulting best-fit parameters from \texttt{SpecMatch-Emp} are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$ and Mass=0.7 $\pm 0.1 $M$_\odot$.
+The output \texttt{SpecMatch-Emp} age constraint of 9.6 $\pm$ 0.2 Gyr is likely an underestimated error in the age.
+Figure \ref{fig:SpecMatch-EmpComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{SpecMatch-Emp}.
 
@@
 \includegraphics[width=0.8\textwidth]{images/subaru/spec_chi_min.pdf}
-\caption{$\chi^2$ as a function of stellar parameters found by \texttt{specmatch}.
-The effective temperature and radii show clear global minima.}\label{fig:specMatch}
+\caption{$\chi^2$ as a function of stellar parameters found by \texttt{SpecMatch-Emp}.
+The effective temperature and radii show clear global minima.}\label{fig:SpecMatch-Emp}
 \end{centering}
@@
 
-We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}, which both favor a main-sequence log(g) $\approx$ 4.6 star.
+We summarize these \texttt{SpecMatch-Emp} and BOSZ results in Table \ref{tab:stellObsParams}, which both favor a main-sequence log(g) $\approx$ 4.6 star.
 Our analysis of the median 2015 spectrum therefore indicates that the stellar spectrum shows no strong contamination from planet disintegration activity.
@@
 \includegraphics[width=0.8\textwidth]{images/subaru/lincomb_kic1255.pdf}
-\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:specMatchComb}
+\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:SpecMatch-EmpComb}
 \end{centering}
@@
 \caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
-(Right) The residuals show significant deviations at phases of -0.5 and 0.05.
+(Right) The residuals show significant deviations near phases of -0.5 and 0.05.
 }\label{fig:riverPlots}
@@
 If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.12 to $\sim$0.15).
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
+\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
+(Right) The residuals show smaller residuals than the average model.
+}\label{fig:riverPlotsPCA}
+\end{centering}
+\end{figure*}
 
@@
 \end{figure*}
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
-\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
-(Right) The residuals show smaller residuals than the average model.
-}\label{fig:riverPlotsPCA}
-\end{centering}
-\end{figure*}
-
 Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
-\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:PCAamp}
+\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1}
 Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
@@
 An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
-A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.
+A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical noise.
 (Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histograms}
@@
 	\texttt{iraf},
-	\texttt{specmatch} tool \citep{yee2017specMatch} 
+	\texttt{SpecMatch-Emp} \citep{yee2017specMatch} 
           %\texttt{emcee} \citep{foreman-mackey2013emcee}, 

### 2018-06-03 ms.tex
added some notes about the 2013 lower SNR.

@@
 
-\subsection{Subaru HDS Spectra}
+\subsection{Subaru HDS Spectra}\label{sec:SubaruDescrip}
 
@@
 \end{figure*}
+
+We posit that the initial analysis of the 2013 Subaru spectrum \citep{kawahara2013starspots} that found a temperature and log(g) of 4950 K and 3.9 log(cm/s$^{-2}$) was affected by insufficient signal to noise in the spectrum.
+The 2013 data has a 30\% smaller count rate (in e$^-$/s) than the 2015 data likely because the 2013 weather and guiding were sub-optimal.
+On top of that, the total exposure time for the 2013 observations was only 1.5 hours.
+The consequence of the increased noise in the 2013 spectra affected the interpretation of this high resolution spectrum.
+For example, the SNR of the Na D lines was $\sim$ 30, which is near the threshold needed for the \citet{takeda2005specFGKdwarfs} equivalent width method employed in the initial analysis.
+We therefore conclude that the noise in the spectrum affected the stellar parameters rather than gas absorption from sublimating dust grains.
 

### 2018-06-04 ms.tex
a little more description of spectra in Intro.

@@
 
-\author{Teruyuki Hirano?}
+\author{Teruyuki Hirano}
 \affiliation{Department of Earth and Planetary Sciences, Tokyo Institute of Technology, Tokyo 152-8550, Japan}
 
-\author{Hajima Kawahara?}
+\author{Hajima Kawahara}
 \affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan}
@@
 This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
-We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.
-We also examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to improve the stellar parameters from the data.
+We performed follow-up $R$ band photometry of the \shStar\ system to explore these two hypotheses and see if the the disintegration has returned to the levels found in the Kepler mission.
+
+The high resolution spectrum of \shStar\ \citep{kawahara2013starspots} showed a different temperature and gravity than photometric methods \cite[e.g.][]{brown2011kic}.
+\citet{vanlieshout2016kic1255} suggest that one exciting possibility is that gases from the disintegrating planet contaminate the high resolution spectrum.
+This would enable compositional and kinematic studies of the disintegrating planet.
+Here, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
 

### 2018-06-06 ms.tex
updated description of photometry.

@@
 \begin{deluxetable}{lrr}
-\tablecaption{List of observations}\label{tab:photSummary}
+\tablecaption{List of photometric observations}\label{tab:photSummary}
 \tablewidth{0pt}
@@
 \startdata
-2016-06-10 & Clouds	& \nodata \\
-2016-06-12 & Clear 		& 0.94 $\pm$ 0.16 \\
-2016-06-14 & Clear 		&0.70 $\pm$ 0.18\\
-2016-07-12 & Clear 		& 0.78 $\pm$ 0.14 \\
-2016-07-14 & Mostly clear	& 1.33 $\pm$ 0.14 \\
-2016-07-16 & Clear 		& 2.14 $\pm$ 0.19 \\
+2016 Jun 10 & Clouds	& \nodata \\
+2016 Jun 12 & Clear 		& 0.94 $\pm$ 0.16 \\
+2016 Jun 14 & Clear 		&0.70 $\pm$ 0.18\\
+2016 Jul 12 & Clear 		& 0.78 $\pm$ 0.14 \\
+2016 Jul 14 & Mostly clear	& 1.33 $\pm$ 0.14 \\
+2016 Jul 16 & Clear 		& 2.14 $\pm$ 0.19 \\
 \enddata
-\tablenotetext{}{Summary of observations and conditions in this work.}
+\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper observatory.}
 \end{deluxetable}
@@
 \section{Observations}
-We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory located on Mt Bigelow, Arizona on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
+We attempted to observe 6 transit events of \sha\ with the Mont4k imager on the 61-inch Kuiper observatory located on Mt Bigelow, Arizona on UT using the f/13.5 Cassegrain focus.
 On all nights we used 90 second exposures using a Harris-R filter to best approximate the $r'$ filter used in \citet{schlawin2016kic1255}.
-The nights were clear with the exception of a few passing clouds on 2016-07-14.
-We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
+5 of the 6 nights were clear with the exception of a few passing clouds on UT 2016 Jul 14.
+Cloudy skies on UT 2016 Jun 10 that prevented high precision time series.
 Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
 The data was taken in a 3x3 binning mode resulting in an effective 0.43"/pixel plate scale.
-We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.
 
@@
 
-For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
+For the photometric reduction, we used the Python \texttt{ccdproc} package \citep{craig2015ccdproc} to generate master flat field and bias files.
 They were combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
+
+We used the \texttt{photutils v0.3} \citep{bradley2016photutilsv0p3} package to centroid and extract fluxes of the \shStar\ and the reference stars.
+We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.
 12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
 The reference stars are identified in Figure \ref{fig:refStars}.
-These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \sha.
-
-For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
-We combined the flat fields and bias files with a a sigma-clipped average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
+These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \shStar.
 
@@
 \includegraphics[width=0.49\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
-\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
-The reference stars were chosen to have similar count levels as the source. 
+\caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of Mont4K.
+{\it Right:} Postage stamp zoom-ins for the source and reference stars show the point spread functions for each star.
+The reference stars were chosen to have similar count levels as \shStar.
 }\label{fig:refStars}
@@
 
-\software{astropy \citep{astropy2013}, 
+\software{
+	\texttt{ccdproc} \citep{craig2015ccdproc},
+	\texttt{astropy} \citep{astropy2013}, 
 	\texttt{scikit-learn} \citep{pedregosa2011scikit-learn},
+	\texttt{photutils v0.3} \citep{bradley2016photutilsv0p3},
 	\texttt{iraf},

### 2018-06-07 ms.tex
added time series and periodogram for PC2.

@@
 \begin{centering}
-\includegraphics[width=0.99\textwidth]{images/kepler/pc1_tser_w_quiescent.pdf}
-\caption{The first principal component's time series.}\label{fig:tserPC1}
+\includegraphics[width=0.99\textwidth]{images/kepler/pc_tser_w_quiescent.pdf}
+\caption{The first two principal component's time series.}\label{fig:tserPC1}
 \end{centering}
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
 \caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1}

### 2018-06-09 ms.tex
updated ephemeris to latest Croll one.

@@
 
-We used the \texttt{photutils v0.3} \citep{bradley2016photutilsv0p3} package to centroid and extract fluxes of the \shStar\ and the reference stars.
+We used the Python \texttt{photutils v0.3} \citep{bradley2016photutilsv0p3} package to centroid and extract fluxes of the \shStar\ and the reference stars.
 We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.
 12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
-The reference stars are identified in Figure \ref{fig:refStars}.
+The reference stars are identified Figure \ref{fig:refStars} across the 9.8\arcmin $\times$ 9.8 \arcmin\ Mont4K field of view.
 These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \shStar.
@@
 These are the same reference stars shown in Figure \ref{fig:refStars}.
-The two nights 2016-06-12 and 2016-06-14 show greater overall stability than the ones in July, 2016.
-We suspect that the higher moisture levels and occasional cloud passages (such as the ones that caused huge drops in flux on UT2016-07-14) affected the later observations.
+The two nights 2016 Jun 12 and 2016 Jun 14 show greater overall stability than the 3 nights in July, 2016.
+We suspect that the higher moisture levels and occasional cloud passages (such as the ones that caused huge drops in flux on UT 2016 Jul 14) affected the later observations.
 
@@
 Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all nights.
-We use the following planet transit ephemeris, using the flux minimum ``transit center'' from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
+We use the planet transit ephemeris from \citet{croll2015starspots} where the Kepler flux minimum is the ``transit center'':
 \begin{equation}
@@
 \end{equation}
-where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.
+where $T_0 = 2 454 968.982 0 \pm 0.000 7$ BJD$_{TDB}$ and $P = 0.653 553 4 \pm 0.000 000 2$ days.
 The expected transit epochs from the ephemeris in \citep{vanWerkhoven2014} are shown for reference as vertical red bars.

### 2018-06-11 ms.tex
removed extraneous best fit plot.
described fits to photometry.

@@
 \colhead{Weather} &
-\colhead{Amplitude} \\
+\colhead{Amplitude, $A$} \\
 \colhead{UT} & & \\
@@
 
-\section{Observations}
+\section{Photometric Observations}
 We attempted to observe 6 transit events of \sha\ with the Mont4k imager on the 61-inch Kuiper observatory located on Mt Bigelow, Arizona on UT using the f/13.5 Cassegrain focus.
@@
 \begin{centering}
-\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
+\includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
 \caption{Time series photometry for all stars and all nights nights.
@@
 \end{figure*}
+
+\subsection{Transit Depth Fitting}
 
@@
 
-We also overlay the average Kepler short cadence light curves on the measured light curves.
-To ease the comparison of the average Kepler light curve and measured data, we bin the 61-inch Mont4K data into 20 minute long bins.
-Obvious cosmic ray outliers were discarded by removing points with fluxes below 0.98 and above 1.02 times the median flux.
-The error bars for the binned data are calculated from the standard error in the mean for each bin.
-When comparing the average Kepler Short Cadence light curve and the measured light curves that the measured light curves represent typical KIC 12557548 b transits.
-Only 2016-06-14 appears to have a non-detection.
+We find the best fit to each light curve using the average Kepler short cadence light curve as a model.
+We include a linear baseline so that the model is
+\begin{equation}
+F(t) = \left(A \cdot f_{SC}(t) + 1 \right)  (1 + B + C \cdot t),
+\end{equation}
+where $F(t)$ is the normalized flux at orbital phase $t$, $A$ is the amplitude parameter, $f_{SC}(t)$ is average Kepler short cadence light curve linearly interpolated at an orbital phase $t$, $B$ is the baseline offset and $C$ is the baseline slope.
+We use the Markov Chain Monte Carlo (MCMC) package \texttt{emcee} \citep{foreman-mackey2013emcee} to find the transit depth amplitude and uncertainty.
+We use 50 MCMC chains with 500 burn-in points and 1500 points to sample the posterior distribution.
+The best-fit light curves are shown in Figure \ref{fig:allNightrefCorrect}.
 
@@
 \begin{centering}
-\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
+\includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
 \caption{Reference-corrected time series photometry \shStar\ for all nights (blue circles).
@@
 
-\begin{figure*}
-\begin{centering}
-\includegraphics[width=0.9\textwidth]{images/tser_fits/best_fit_all.pdf}
-\caption{Best-fit for all nights.}\label{fig:fitAll}
-\end{centering}
-\end{figure*}
+To ease the visual comparison of the models and measured data, we bin the 61-inch Mont4K data into 20 minute long bins.
+Obvious cosmic ray outliers were discarded by removing points with fluxes below 0.98 and above 1.02 times the median flux.
+The error bars for the binned data are calculated from the standard error in the mean for each bin.
+When calculating the best fit model and posterior distribution of parameter, however, the un-binned data is used.
+
+In contrast to \citet{schlawin2016kic1255}, the transit depths in 2016 June and 2016 July are similar to the distribution measured by the Kepler spacecraft from 2009 to 2013.
+\citet{schlawin2016kic1255} found significantly weaker transit depths that the Kepler spacecraft in 2013 Aug-Sep and 2014 Aug-Sep, which indicated that either disintegration activity was slowing down or that there were quiescent periods during those observations.
+The transit depths listed in Table \ref{tab:photSummary} are ``back to normal'' in that they are consistent with the Kepler results.
+We will revisit the statistics of these events in Section \ref{sec:Kepler}.
 
@@
 
-\section{Kepler Re-analysis}
+\section{Kepler Re-analysis}\label{sec:Kepler}
+
 We examine the 17 total quarters of Kepler data for three purposes:
@@
 
-We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009-05-13 and ending on 2013-04-08 for a total of 1425 days or 2181.5 orbits.
+We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.
 The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
@@
 	\texttt{SpecMatch-Emp} \citep{yee2017specMatch} 
-          %\texttt{emcee} \citep{foreman-mackey2013emcee}, 
+         \texttt{emcee} \citep{foreman-mackey2013emcee}, 
           }

### 2018-06-15 ms.tex
reorganized sections and added a quick note about transit duration.

@@
 Typical uncertainties for the Kepler ephemeris are $\sim$ 1 minute at these dates due to the large number of transits measured by the Kepler observatory over nearly 4 years.
-The ``transit duration'' from Kepler light curves is around 0.05 days, which is consistent with these transit durations.
+The ``transit duration'' from Kepler light curves is about 0.06 days\footnote{We define the transit duration as the point at which the average light curve measured by the Kepler spacecraft drops below 99.95\% of the normalized flux as in \citet{schlawin2016kic1255}}, which is consistent with these transit durations.
 
@@
 We use 50 MCMC chains with 500 burn-in points and 1500 points to sample the posterior distribution.
-The best-fit light curves are shown in Figure \ref{fig:allNightrefCorrect}.
+The best-fit light curves are shown in Figure \ref{fig:allNightrefCorrect} and the best-fit amplitudes are listed in Table \ref{tab:photSummary}.
 
@@
 \clearpage
+
+\section{Kepler Re-analysis}\label{sec:Kepler}
+
+We examine the 17 total quarters of Kepler data for three purposes:
+\begin{enumerate}
+	\item To understand the statistics of the transits and put the 2013-2016 observations in context. Mainly, how likely/unlikely were the weak transits observed in 2013-2014?
+	\item To measure the radius of the planet or put an upper limit on its radius by examining any possible transit beneath the dust signal
+	\item Identify any new patterns or observations from the Kepler data that might occur along the way
+\end{enumerate}
+
+We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.
+The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
+A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 phase window.
+All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
+The secondary eclipses are used to quantify the noise in the transit depths.
+
+\subsection{Kepler Secondary Eclipse}
+
+We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
+We then use the secondary eclipses as a way to characterize the noise of the primary eclipses.
+Both have the same quadratic baseline removal process over the same time intervals.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
+\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
+Here, the data are binned to orbital phases of 0.1 (1.5 minutes) and errors calculated from the standard error in the mean of the data within a bin.
+}\label{fig:secEclipse}
+\end{centering}
+\end{figure*}
+
+\subsection{Average Light Curve Analysis}
+
+In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
+We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 15 minutes (to Nyquist sample the 30 minute observation cadence) and put together all the time series that have no gaps into this two dimensional grid.
+This cleaned Kepler long-cadence array is shown in Figure \ref{fig:riverPlots}.
+
+We start by taking the average transit light curve of all the long cadence data (the mean of the 2D grid along the transit number axis).
+We then take the dot product ($\bullet$) with this average light curve to create an amplitude time series.
+\begin{equation}
+A = \frac{(f - 1) \bullet a}{a \bullet a},
+\end{equation}
+where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
+This dot product is then multiplied by the average transit light curve to create a 2D model grid.
+The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve below.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
+\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
+(Right) The residuals show significant deviations near phases of -0.5 and 0.05.
+}\label{fig:riverPlots}
+\end{centering}
+\end{figure*}
+
+\subsection{Principal Component Analysis}
+
+As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
+Here, we are assuming that the grid of orbital phases (spaced by 15 minutes) contains random correlated variables with different realizations along the transit number axis.
+The first principal component eigenvector is the linear combination of these random variables that maximizes the variance in the data.
+The second principal component eigenvector is the linear combination of these random variables with the next-highest variance while being orthogonal to the first principal component.
+This continues up to some finite number of principal components, with the hope that we can use just a few orthogonal light curves to adequately describe the data \citep[e.g.][]{jolliffe2002pca}.
+We use the Python package \texttt{scikit-learn} \citep{pedregosa2011scikit-learn} to calculate the principal components and eigenvectors.
+
+We use a covariance matrix as opposed to correlation matrix to calculate the principal component eigenvectors.
+In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
+However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
+If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.12 to $\sim$0.15).
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
+\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
+(Right) The residuals show smaller residuals than the average model.
+}\label{fig:riverPlotsPCA}
+\end{centering}
+\end{figure*}
+
+Figure \ref{fig:pcaVectorsComp} shows the calculated 4 eigenvectors as a function of orbital phase and the corresponding 4 principal components as a function of transit number.
+We weight each eigenvectors by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
+The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
+\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
+The first two principal components (Right) do not isolate any separate populations of transits.
+As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
+\end{centering}
+\end{figure*}
+Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.99\textwidth]{images/kepler/pc_tser_w_quiescent.pdf}
+\caption{The first two principal component's time series.}\label{fig:tserPC1}
+\end{centering}
+\end{figure*}
+
+In Figure \ref{fig:ampPeriodogram} we show the periodogram of amplitudes that have peaks at 0.654, 22.9, 153 and 750 days.
+The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
+As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
+\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1}
+Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
+The peak at 0.654 days is the orbital period.
+The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
+The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
+\caption{(Left) Histogram of transit amplitudes.
+An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
+A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical noise.
+(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histograms}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
+\caption{Normalized frequency of 3 different distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 3) the 5 night Kuiper observatory campaign in the summer of 2016.
+The \citet{schlawin2016kic1255} (S16) events give a Kolmogorov Smirnov p value of 0.001 of the null hypothesis that the S16 results are drawn from the same distribution as the Kepler Long Cadence.
+In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.}\label{fig:histoPhot}
+\end{centering}
+\end{figure*}
 
@@
 We therefore conclude that the noise in the spectrum affected the stellar parameters rather than gas absorption from sublimating dust grains.
-
-\clearpage
-
-\section{Kepler Re-analysis}\label{sec:Kepler}
-
-We examine the 17 total quarters of Kepler data for three purposes:
-\begin{enumerate}
-	\item To understand the statistics of the transits and put the 2013-2016 observations in context. Mainly, how likely/unlikely were the weak transits observed in 2013-2014?
-	\item To measure the radius of the planet or put an upper limit on its radius by examining any possible transit beneath the dust signal
-	\item Identify any new patterns or observations from the Kepler data that might occur along the way
-\end{enumerate}
-
-We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.
-The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
-A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 phase window.
-All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
-The secondary eclipses are used to quantify the noise in the transit depths.
-
-\subsection{Kepler Secondary Eclipse}
-
-We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
-We then use the secondary eclipses as a way to characterize the noise of the primary eclipses.
-Both have the same quadratic baseline removal process over the same time intervals.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
-\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
-Here, the data are binned to orbital phases of 0.1 (1.5 minutes) and errors calculated from the standard error in the mean of the data within a bin.
-}\label{fig:secEclipse}
-\end{centering}
-\end{figure*}
-
-\subsection{Average Light Curve Analysis}
-
-In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
-We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 15 minutes (to Nyquist sample the 30 minute observation cadence) and put together all the time series that have no gaps into this two dimensional grid.
-This cleaned Kepler long-cadence array is shown in Figure \ref{fig:riverPlots}.
-
-We start by taking the average transit light curve of all the long cadence data (the mean of the 2D grid along the transit number axis).
-We then take the dot product ($\bullet$) with this average light curve to create an amplitude time series.
-\begin{equation}
-A = \frac{(f - 1) \bullet a}{a \bullet a},
-\end{equation}
-where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
-This dot product is then multiplied by the average transit light curve to create a 2D model grid.
-The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve below.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
-\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
-(Right) The residuals show significant deviations near phases of -0.5 and 0.05.
-}\label{fig:riverPlots}
-\end{centering}
-\end{figure*}
-
-\subsection{Principal Component Analysis}
-
-As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
-Here, we are assuming that the grid of orbital phases (spaced by 15 minutes) contains random correlated variables with different realizations along the transit number axis.
-The first principal component eigenvector is the linear combination of these random variables that maximizes the variance in the data.
-The second principal component eigenvector is the linear combination of these random variables with the next-highest variance while being orthogonal to the first principal component.
-This continues up to some finite number of principal components, with the hope that we can use just a few orthogonal light curves to adequately describe the data \citep[e.g.][]{jolliffe2002pca}.
-We use the Python package \texttt{scikit-learn} \citep{pedregosa2011scikit-learn} to calculate the principal components and eigenvectors.
-
-We use a covariance matrix as opposed to correlation matrix to calculate the principal component eigenvectors.
-In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
-However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
-If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.12 to $\sim$0.15).
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
-\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
-(Right) The residuals show smaller residuals than the average model.
-}\label{fig:riverPlotsPCA}
-\end{centering}
-\end{figure*}
-
-Figure \ref{fig:pcaVectorsComp} shows the calculated 4 eigenvectors as a function of orbital phase and the corresponding 4 principal components as a function of transit number.
-We weight each eigenvectors by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
-The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
-\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
-The first two principal components (Right) do not isolate any separate populations of transits.
-As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
-\end{centering}
-\end{figure*}
-Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.99\textwidth]{images/kepler/pc_tser_w_quiescent.pdf}
-\caption{The first two principal component's time series.}\label{fig:tserPC1}
-\end{centering}
-\end{figure*}
-
-In Figure \ref{fig:ampPeriodogram} we show the periodogram of amplitudes that have peaks at 0.654, 22.9, 153 and 750 days.
-The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
-As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
-\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1}
-Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
-The peak at 0.654 days is the orbital period.
-The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
-The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
-\end{centering}
-\end{figure*}
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
-\caption{(Left) Histogram of transit amplitudes.
-An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
-A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical noise.
-(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histograms}
-\end{centering}
-\end{figure*}
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
-\caption{Normalized frequency of 3 different distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 3) the 5 night Kuiper observatory campaign in the summer of 2016.
-The \citet{schlawin2016kic1255} (S16) events give a Kolmogorov Smirnov p value of 0.001 of the null hypothesis that the S16 results are drawn from the same distribution as the Kepler Long Cadence.
-In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.}\label{fig:histoPhot}
-\end{centering}
-\end{figure*}
 

### 2018-06-16 ms.tex
added some more details to Kepler analysis

@@
 where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
+
 This dot product is then multiplied by the average transit light curve to create a 2D model grid.
-The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve below.
+The residual of this model (Figure \ref{fig:riverPlots}) shows significant $\pm$0.2\% deviations from white noise, indicating that the dusty tail surrounding \sha\ shanges in shape with time.
+We explore more sophisticated models than the average light curve below that are based on principal component analysis.
+However, this average model serves as a useful comparison to fitting lower-precision photometry, such as the ground-based light curves typical photometric scatter is $\sim$ 0.1 to 0.2\% for 20 minute timescales.
 
@@
 However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
-If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.12 to $\sim$0.15).
+If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$ -0.12 to $\sim$0.15).
 \begin{figure*}[!hbtp]
@@
 \includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
-\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
-(Right) The residuals show smaller residuals than the average model.
+\caption{Cleaned Kepler Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
+The residuals (Right) have $\lesssim 0.1\%$ residuals in contrast to the average-light curve method used in Figure \ref{fig:riverPlots}.
 }\label{fig:riverPlotsPCA}
@@
 \begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pc1_periodogram.pdf}
 \includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
 \caption{(Left) Histogram of transit amplitudes.
 An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
-A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical noise.
-(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histograms}
+A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical photon noise that explains shy some transit depths appear less than 0.
+}\label{fig:histograms}
 \end{centering}

### 2018-06-18 ms.tex
quick note on particle size from Schlawin et al. 2016
added airmass info

@@
 \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
+The SpeX/IRTF spectrum, though affected by systematic noise, confirmed the \citet{croll2014} result that particle sizes are $\gtrsim 0.5\%$ for a pyroxene composition.
 \citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
@@
 
-\begin{deluxetable}{lrr}
+\begin{deluxetable}{lrrr}
 \tablecaption{List of photometric observations}\label{tab:photSummary}
@@
 \colhead{Weather} &
+\colhead{Airmass} &
 \colhead{Amplitude, $A$} \\
-\colhead{UT} & & \\
+\colhead{UT} & & & \\
  }
 \startdata
-2016 Jun 10 & Clouds	& \nodata \\
-2016 Jun 12 & Clear 		& 0.94 $\pm$ 0.16 \\
-2016 Jun 14 & Clear 		&0.70 $\pm$ 0.18\\
-2016 Jul 12 & Clear 		& 0.78 $\pm$ 0.14 \\
-2016 Jul 14 & Mostly clear	& 1.33 $\pm$ 0.14 \\
-2016 Jul 16 & Clear 		& 2.14 $\pm$ 0.19 \\
+2016 Jun 10 & Clouds	& \nodata &  \nodata \\
+2016 Jun 12 & Clear 	& 1.29 $\rightarrow$ 1.06 $\rightarrow$ 1.10	& 0.94 $\pm$ 0.16 \\
+2016 Jun 14 & Clear 	& 1.47 $\rightarrow$ 1.06 $\rightarrow$ 1.12	&0.70 $\pm$ 0.18\\
+2016 Jul 12 & Clear 		& 1.19 $\rightarrow$ 1.06 $\rightarrow$ 1..63	& 0.78 $\pm$ 0.14 \\
+2016 Jul 14 & Mostly clear	& 1.24 $\rightarrow$ 1.06 $\rightarrow$ 1.55 & 1.33 $\pm$ 0.14 \\
+2016 Jul 16 & Clear 		& 1.36 $\rightarrow$ 1.06 $\rightarrow$ 1.26	& 2.14 $\pm$ 0.19 \\
 \enddata

### 2018-06-23 ms.tex
editing tser fitting and PCA sections.

--- 2018-06-16 ms.tex
@@
 
-\begin{deluxetable}{lrr}
+\begin{deluxetable}{lrrrr}
 \tablecaption{List of photometric observations}\label{tab:photSummary}
@@
 \colhead{Weather} &
+\colhead{Airmass} &
+\colhead{Seeing} &
 \colhead{Amplitude, $A$} \\
-\colhead{UT} & & \\
+\colhead{UT} & & & (\arcsec) & \\
  }
 \startdata
-2016 Jun 10 & Clouds	& \nodata \\
-2016 Jun 12 & Clear 		& 0.94 $\pm$ 0.16 \\
-2016 Jun 14 & Clear 		&0.70 $\pm$ 0.18\\
-2016 Jul 12 & Clear 		& 0.78 $\pm$ 0.14 \\
-2016 Jul 14 & Mostly clear	& 1.33 $\pm$ 0.14 \\
-2016 Jul 16 & Clear 		& 2.14 $\pm$ 0.19 \\
+2016 Jun 10 & Clouds	& \nodata & \nodata &  \nodata \\
+2016 Jun 12 & Clear 	& 1.29 $\rightarrow$ 1.06 $\rightarrow$ 1.10	& 1.3 &	0.94 $\pm$ 0.16 \\
+2016 Jun 14 & Clear 	& 1.47 $\rightarrow$ 1.06 $\rightarrow$ 1.12	& 1.4 &	0.70 $\pm$ 0.18\\
+2016 Jul 12 & Clear 		& 1.19 $\rightarrow$ 1.06 $\rightarrow$ 1.63	& 1.2 &	0.78 $\pm$ 0.14 \\
+2016 Jul 14 & Mostly clear	& 1.24 $\rightarrow$ 1.06 $\rightarrow$ 1.55 & 1.2 & 	1.33 $\pm$ 0.14 \\
+2016 Jul 16 & Clear 		& 1.36 $\rightarrow$ 1.06 $\rightarrow$ 1.26	& 1.4 & 	2.14 $\pm$ 0.19 \\
 \enddata
-\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper observatory.}
+\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper observatory.
+The seeing is expressed as the median FWHM for the night in arcseconds.}
 \end{deluxetable}
@@
 We use the planet transit ephemeris from \citet{croll2015starspots} where the Kepler flux minimum is the ``transit center'':
-\begin{equation}
+\begin{equation}\label{eq:ephem}
 T = T_0 + n P
@@
 We include a linear baseline so that the model is
-\begin{equation}
+\begin{equation}\label{eq:transFitting}
 F(t) = \left(A \cdot f_{SC}(t) + 1 \right)  (1 + B + C \cdot t),
@@
 where $F(t)$ is the normalized flux at orbital phase $t$, $A$ is the amplitude parameter, $f_{SC}(t)$ is average Kepler short cadence light curve linearly interpolated at an orbital phase $t$, $B$ is the baseline offset and $C$ is the baseline slope.
+We construct $f_{SC}(t)$ by phasing the Kepler time series with Equation \ref{eq:ephem}, normalizing by the median, removing a quadratic baseline from each transit, averaging the results and subtracting 1.0 to get the differential flux.
 We use the Markov Chain Monte Carlo (MCMC) package \texttt{emcee} \citep{foreman-mackey2013emcee} to find the transit depth amplitude and uncertainty.
@@
 
-To ease the visual comparison of the models and measured data, we bin the 61-inch Mont4K data into 20 minute long bins.
+To ease the visual comparison of the models and measured data, we bin the 61-inch Mont4K data into 20 minute long bins, shown in Figure \ref{fig:allNightrefCorrect}.
 Obvious cosmic ray outliers were discarded by removing points with fluxes below 0.98 and above 1.02 times the median flux.
@@
 
-We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
+We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected at $\lesssim 50$~ppm, seen in Figure \ref{fig:secEclipse}. 
 We then use the secondary eclipses as a way to characterize the noise of the primary eclipses.
@@
 In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
-We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 15 minutes (to Nyquist sample the 30 minute observation cadence) and put together all the time series that have no gaps into this two dimensional grid.
+We linearly interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 15 minutes (to Nyquist sample the 30 minute observation cadence) and put together all the time series that have no gaps into this two dimensional grid.
 This cleaned Kepler long-cadence array is shown in Figure \ref{fig:riverPlots}.
@@
 \begin{equation}
-A = \frac{(f - 1) \bullet a}{a \bullet a},
+A' \equiv \frac{(f - 1) \bullet \vec{a}}{\vec{a} \bullet \vec{a}},
 \end{equation}
-where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
+where $\vec{a}$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
+This dot product, $A'$ is comparable to the transit amplitude $A$ in Equation \ref{eq:transFitting}.
 
@@
 The second principal component eigenvector is the linear combination of these random variables with the next-highest variance while being orthogonal to the first principal component.
-This continues up to some finite number of principal components, with the hope that we can use just a few orthogonal light curves to adequately describe the data \citep[e.g.][]{jolliffe2002pca}.
+This continues up to some finite number of principal components, with the hope that we can use a few orthogonal light curves to adequately describe the data \citep[e.g.][]{jolliffe2002pca}.
 We use the Python package \texttt{scikit-learn} \citep{pedregosa2011scikit-learn} to calculate the principal components and eigenvectors.
@@
 If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$ -0.12 to $\sim$0.15).
+The resulting model and residuals shown in Figure \ref{fig:riverPlotsPCA} are much closer to white noise than the model that uses the dot product with the average light curve.
+
 \begin{figure*}[!hbtp]
@@
 
-Figure \ref{fig:pcaVectorsComp} shows the calculated 4 eigenvectors as a function of orbital phase and the corresponding 4 principal components as a function of transit number.
+Figure \ref{fig:pcaVectorsComp} shows the first 4 eigenvectors as a function of orbital phase.
 We weight each eigenvectors by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
 The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
+We also show the first two principal components as a scatter plot in Figure \ref{fig:pcaVectorsComp}.
+The quiescent periods discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots} appear as low values for the first two principal components.
 

### 2018-06-23 ms.tex
more editing of Kepler section.

@@
 
-\subsection{Transit Depth Fitting}
+\subsection{Transit Depth Fitting}\label{sec:transFitting}
 
@@
 
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
+\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
+(Right) The residuals show significant deviations near phases of -0.5 and 0.05.
+}\label{fig:riverPlots}
+\end{centering}
+\end{figure*}
+
 \subsection{Average Light Curve Analysis}
@@
 This dot product is then multiplied by the average transit light curve to create a 2D model grid.
-The residual of this model (Figure \ref{fig:riverPlots}) shows significant $\pm$0.2\% deviations from white noise, indicating that the dusty tail surrounding \sha\ shanges in shape with time.
+The residual of this model (Figure \ref{fig:riverPlots}) shows significant $\pm$0.2\% deviations from white noise, indicating that the dusty tail surrounding \sha\ changes in shape with time.
 We explore more sophisticated models than the average light curve below that are based on principal component analysis.
-However, this average model serves as a useful comparison to fitting lower-precision photometry, such as the ground-based light curves typical photometric scatter is $\sim$ 0.1 to 0.2\% for 20 minute timescales.
+However, this average model serves as a useful comparison to fitting the transit depth for ground-based photometry, as performed in Section \ref{sec:transFitting}.
+The 0.2\% residuals with this average model are comparable with the typical photometric scatter of $\sim$ 0.1 to 0.2\% for 20 minute timescales in this work and \citet{schlawin2016kic1255}.
+We statistically compare the transit depths from the Kepler mission from 2009 to 2013 to the ground-based measurements from 2013 through 2016 in Section \ref{sec:statistics}.
 
+\subsection{Principal Component Analysis}
 \begin{figure*}[!hbtp]
@@
 \includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
-\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
-(Right) The residuals show significant deviations near phases of -0.5 and 0.05.
-}\label{fig:riverPlots}
+\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
+\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
+\caption{Cleaned Kepler Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
+The residuals (Right) have $\lesssim 0.1\%$ residuals in contrast to the average-light curve method used in Figure \ref{fig:riverPlots}.
+}\label{fig:riverPlotsPCA}
 \end{centering}
 \end{figure*}
-
-\subsection{Principal Component Analysis}
 
@@
 \begin{centering}
-\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
-\caption{Cleaned Kepler Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
-The residuals (Right) have $\lesssim 0.1\%$ residuals in contrast to the average-light curve method used in Figure \ref{fig:riverPlots}.
-}\label{fig:riverPlotsPCA}
-\end{centering}
-\end{figure*}
-
-Figure \ref{fig:pcaVectorsComp} shows the first 4 eigenvectors as a function of orbital phase.
-We weight each eigenvectors by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
-The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
-We also show the first two principal components as a scatter plot in Figure \ref{fig:pcaVectorsComp}.
-The quiescent periods discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots} appear as low values for the first two principal components.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
 \includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
@@
 \end{figure*}
+
+Figure \ref{fig:pcaVectorsComp} shows the first 4 eigenvectors as a function of orbital phase.
+We weight each eigenvectors by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
+The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
+The first eigenvector largely describes extinction from the core of the comet-like tail (modeled in \citet{rappaport}, \citet{brogi2012}, \citet{budaj12} and \citet{vanlieshout2016kic1255}, while the second one corresponds more the forward scattering component.
+We also show the first two principal components as a scatter plot in Figure \ref{fig:pcaVectorsComp}.
+In some applications of PCA, separate populations of behaviors can appear in these scatter plots (such as different modes of planet disintegration) but here there is a continuous distribution points.
+We also color the quiescent periods of very little \sha\ disintegration activity (discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots}) and these quiescent periods appear as low values for the first two principal components.
+This indicates that
+
 Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.
@@
 \end{figure*}
+
+\subsection{Statistical Analysis of Ground-based Photometry}\label{sec:statistics}
 

### 2018-06-25 ms.tex
added transformed versions of first eigenvectors.

@@
 \includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255_transformed.pdf}
 \includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
-\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
-The first two principal components (Right) do not isolate any separate populations of transits.
+\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Top Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
+The first two principal components (Bottom) do not isolate any separate populations of transits.
 As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}

### 2018-06-26 ms.tex
more thoughts on PC eigenvectors.

@@
 In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
-However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
+However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units (normalized flux).
 If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$ -0.12 to $\sim$0.15).
-The resulting model and residuals shown in Figure \ref{fig:riverPlotsPCA} are much closer to white noise than the model that uses the dot product with the average light curve.
+The model using the first 4 principal components shown in Figure \ref{fig:riverPlotsPCA} better matches the data (with more degrees of freedom) and has residuals much closer to white noise than the model that uses the dot product with the average light curve.
 
@@
 Figure \ref{fig:pcaVectorsComp} shows the first 4 eigenvectors as a function of orbital phase.
-We weight each eigenvectors by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
+For the eigenvectors plot, we weight each eigenvector by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
 The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
-The first eigenvector largely describes extinction from the core of the comet-like tail (modeled in \citet{rappaport}, \citet{brogi2012}, \citet{budaj12} and \citet{vanlieshout2016kic1255}, while the second one corresponds more the forward scattering component.
+The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering whereas the second eigenvector corresponds to models of large dust grains with more forward scattering \citep[e.g.][]{budaj12}.
+
 We also show the first two principal components as a scatter plot in Figure \ref{fig:pcaVectorsComp}.
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
-\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1}
+\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1} show several significant peaks.
 Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
-The peak at 0.654 days is the orbital period.
-The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
+The first principal component's peak at 0.654 days is the orbital period (Left).
+The PC$_1$ peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
+The second principal components shows one dominant peak at 491 days, in addition to the 0.654 orbital period.
 The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}

### 2018-06-27 ms.tex
corrected the transformed PCA eigenvectors plot.

@@
 This dot product is then multiplied by the average transit light curve to create a 2D model grid.
-The residual of this model (Figure \ref{fig:riverPlots}) shows significant $\pm$0.2\% deviations from white noise, indicating that the dusty tail surrounding \sha\ changes in shape with time.
+The residual of this model (Figure \ref{fig:riverPlots}) shows significant $\pm$0.2\% deviations from white noise, indicating that the dusty tail surrounding \sha\ changes in shape (or scattering properties) with time.
 We explore more sophisticated models than the average light curve below that are based on principal component analysis.
 However, this average model serves as a useful comparison to fitting the transit depth for ground-based photometry, as performed in Section \ref{sec:transFitting}.
-The 0.2\% residuals with this average model are comparable with the typical photometric scatter of $\sim$ 0.1 to 0.2\% for 20 minute timescales in this work and \citet{schlawin2016kic1255}.
+The 0.2\% residuals with this average model are comparable with the typical photometric scatter of $\sim$ 0.1\% to 0.2\% for 20 minute timescales in \citet{schlawin2016kic1255} and this work.
 We statistically compare the transit depths from the Kepler mission from 2009 to 2013 to the ground-based measurements from 2013 through 2016 in Section \ref{sec:statistics}.
@@
 Here, we are assuming that the grid of orbital phases (spaced by 15 minutes) contains random correlated variables with different realizations along the transit number axis.
-The first principal component eigenvector is the linear combination of these random variables that maximizes the variance in the data.
+The first principal component eigenvector is the linear combination of these random variables that maximizes the variance in the flux.
 The second principal component eigenvector is the linear combination of these random variables with the next-highest variance while being orthogonal to the first principal component.
@@
 Figure \ref{fig:pcaVectorsComp} shows the first 4 eigenvectors as a function of orbital phase.
-For the eigenvectors plot, we weight each eigenvector by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
+For the eigenvectors plot, we multiply each eigenvector by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
 The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
@@
 In some applications of PCA, separate populations of behaviors can appear in these scatter plots (such as different modes of planet disintegration) but here there is a continuous distribution points.
-We also color the quiescent periods of very little \sha\ disintegration activity (discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots}) and these quiescent periods appear as low values for the first two principal components.
+We also color the quiescent periods of very little disintegration activity (discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots}) and these quiescent periods appear as low values for the first two principal components.
 This indicates that

### 2018-06-28 ms.tex
further edits to PCA time series section.

@@
 \includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255_transformed.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
-\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Top Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
-The first two principal components (Bottom) do not isolate any separate populations of transits.
-As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
+\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
+When the eigenvectors are transformed into light curves, 
+}\label{fig:pcaVectorsComp}
 \end{centering}
@@
 Figure \ref{fig:pcaVectorsComp} shows the first 4 eigenvectors as a function of orbital phase.
-For the eigenvectors plot, we multiply each eigenvector by the square root of the explained variance of each principal component, as is used in meteorology \citep{richman1986pcaRotation}.
-The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points in the phase grid from -0.25 to 0.25.
-The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering whereas the second eigenvector corresponds to models of large dust grains with more forward scattering \citep[e.g.][]{budaj12}.
+For the eigenvectors plot, we multiply each eigenvector by its eigenvalue, as is used in meteorology where the products of the eigenvalues and eigenvectors are sometimes called Empirical Orthogonal Functions \citep{richman1986pcaRotation}.
+The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points (variables) in the phase grid from -0.25 to 0.25.
+We also transform the eigenvectors into light curves by multiplying each eigenvector by the standard deviation of principal components and adding it to the average light curve.
+The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering whereas the second eigenvector corresponds to models of large dust grains with more forward scattering \citep[e.g.
+models from][]{budaj12}.
+The implication of the PCA then is that the dust particle sizes are changing with time.
 
-We also show the first two principal components as a scatter plot in Figure \ref{fig:pcaVectorsComp}.
-In some applications of PCA, separate populations of behaviors can appear in these scatter plots (such as different modes of planet disintegration) but here there is a continuous distribution points.
-We also color the quiescent periods of very little disintegration activity (discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots}) and these quiescent periods appear as low values for the first two principal components.
-This indicates that
-
-Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.
+Figure \ref{fig:tserPC1} shows the time series of the first two principal components.
+We highlight the quiescent periods also discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
+The first principal component largely tracks closely with the dot product of the average light curve.
+The quiescent periods show up as 14 to 36 day long intervals of low amplitude events.
+The second principal component shows some sinusoidal behavior at a $\sim$500 day period, indicating that the large particles may be evolving.
+However, the timescales are much longer than dynamical and sublimation times for this system.
 
@@
 \end{figure*}
+
+%We also show the first two principal components as a scatter plot in Figure \ref{fig:pcaVectorsComp}.
+%In some applications of PCA, separate populations of behaviors can appear in these scatter plots (such as different modes of planet disintegration) but here there is a continuous distribution points.
+%We also color the quiescent periods of very little disintegration activity (discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots}) and these quiescent periods appear as low values for the first two principal components.
 

### 2018-06-29 ms.tex
finished PCA section and now working on statistical comparison section.

@@
 We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K star.
+We apply PCA to the Kepler long cadence data to understand the modes of disintegration.
+There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes.
 \end{abstract}
@@
 We use the Python package \texttt{scikit-learn} \citep{pedregosa2011scikit-learn} to calculate the principal components and eigenvectors.
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
+\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255_transformed.pdf}
+\caption{The principal component eigenvectors scaled by their eigenvalues (Left), shows that the first component largely describes the extinction while the second shows the contributions from forward scattering.
+When the eigenvectors are transformed into light curves (Right), it can be seen that the first component corresponds to small dust particle sizes with negligible forward scattering and that the second component corresponds to large dust particle sizes with pronounced forward scattering before and after the transit mid-point.
+}\label{fig:pcaVectorsComp}
+\end{centering}
+\end{figure*}
 
@@
 
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255_transformed.pdf}
-\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
-When the eigenvectors are transformed into light curves, 
-}\label{fig:pcaVectorsComp}
-\end{centering}
-\end{figure*}
-
 Figure \ref{fig:pcaVectorsComp} shows the first 4 eigenvectors as a function of orbital phase.
-For the eigenvectors plot, we multiply each eigenvector by its eigenvalue, as is used in meteorology where the products of the eigenvalues and eigenvectors are sometimes called Empirical Orthogonal Functions \citep{richman1986pcaRotation}.
+For the eigenvectors plot, we multiply each eigenvector by its eigenvalue to emphasize the covariances between the principal components and phase grid variables.
 The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points (variables) in the phase grid from -0.25 to 0.25.
@@
 
-Figure \ref{fig:tserPC1} shows the time series of the first two principal components.
-We highlight the quiescent periods also discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
-The first principal component largely tracks closely with the dot product of the average light curve.
+Figure \ref{fig:tserPC} shows the time series of the first two principal components.
+We highlight the quiescent periods also discussed in \citet{kawahara2013starspots}, \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
+The first principal component largely tracks closely with the dot product of the average light curve ($A'$).
 The quiescent periods show up as 14 to 36 day long intervals of low amplitude events.
@@
 \includegraphics[width=0.99\textwidth]{images/kepler/pc_tser_w_quiescent.pdf}
-\caption{The first two principal component's time series.}\label{fig:tserPC1}
+\caption{Time series of the transit amplitude and principals components.
+The amplitude is found with a dot product with the average light curve.
+Quiescent intervals with low transit activity are identified from the amplitude.
+The second principal component shows periodicity at 491 days, indicating possible long-term evolution of dust grain particle sizes.}\label{fig:tserPC}
 \end{centering}
@@
 
-In Figure \ref{fig:ampPeriodogram} we show the periodogram of amplitudes that have peaks at 0.654, 22.9, 153 and 750 days.
+In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
+The peaks at 0.654 days in both the first and second principal components are the same as the orbital period and are the same as the sampling interval of the time series.
+The first component, corresponding to the transit depth, has peaks at 22.9, 153 and 750 days.
 The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
 As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
+The second principal component's periodogram has a strong peak at 491 days.
+This singly-peaked periodogram implies that PC$_2$ is nearly sinusoidal.
+As shown in Figure \ref{fig:pcaVectorsComp}, the second principal component resembles models with larger dust grains, so the dust grain sizes could be evolving on long-term 491-day timescales.
+This is much longer than the dynamical and sublimation times of the system, so there is no obvious mechanism for the dust grain size evolution.
 
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
-\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1} show several significant peaks.
-Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
-The first principal component's peak at 0.654 days is the orbital period (Left).
-The PC$_1$ peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
-The second principal components shows one dominant peak at 491 days, in addition to the 0.654 orbital period.
-The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
+\caption{Periodograms of the principal component time series shown in Figure \ref{fig:tserPC}, with peaks marked with red circles.
+The first peak at 0.654 days for both principal components is the orbital period, which is the sampling time for these time series.
+The PC$_1$ also peaks at 153 and 750 days, likely because of the intervals of low disintegration activity.
+The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.
+The second principal components shows one dominant peak at 491 days, in addition to the 0.654 orbital period.}\label{fig:ampPeriodogram}
 \end{centering}
@@
 
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
-\caption{(Left) Histogram of transit amplitudes.
-An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
-A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical photon noise that explains shy some transit depths appear less than 0.
-}\label{fig:histograms}
-\end{centering}
-\end{figure*}
+%\begin{figure*}[!hbtp]
+%\begin{centering}
+%\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
+%\caption{(Left) Histogram of transit amplitudes.
+%An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
+%A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical photon noise that explains shy some transit depths appear less than 0.
+%}\label{fig:histograms}
+%\end{centering}
+%\end{figure*}
 
 \subsection{Statistical Analysis of Ground-based Photometry}\label{sec:statistics}
+We calculate and evalute the Kepler transit amplitudes to better understand the long-term behavior of \sha's disintegration.
+We take the histogram of transit amplitudes as measured by the Kepler light curves (shown in Figure \ref{fig:histoPhot}) and compare these to the ground-based photometry from \citet{schlawin2016kic1255} and this work.
+The histogram of secondary eclipse amplitudes from the Kepler light curves is also shown in \ref{fig:histoPhot}.
+The intrinsic astrophysical variation of the planet disintegration is convolved by this photometric scatter in the data.
+We compare the distribution of amplitudes from \citet{schlawin2016kic1255} from the Kepler long cadence data from 2009 to 2013.
+A Kolmogorov-Smirnov test gives a p value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the Kepler Long Cadence data.
 
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
-\caption{Normalized frequency of 3 different distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 3) the 5 night Kuiper observatory campaign in the summer of 2016.
-The \citet{schlawin2016kic1255} (S16) events give a Kolmogorov Smirnov p value of 0.001 of the null hypothesis that the S16 results are drawn from the same distribution as the Kepler Long Cadence.
-In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.}\label{fig:histoPhot}
+\caption{Normalized frequency of 4 different transit amplitude distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the secondary eclipse amplitudes from the Kepler spacecraft over this same period, 3) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper observatory campaign in the summer of 2016.
+The \citet{schlawin2016kic1255} (S16) events give a KS-test p value of 0.001 of the null hypothesis when comparing to the Kepler data.
+In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.
+This indicates that the transit depths are back to normal and there is no slowdown of disintegration activity over time.}\label{fig:histoPhot}
 \end{centering}

### 2018-07-03 ms.tex
got rid of clear page.
finished the statistical comparison section.

@@
 
-\clearpage
-
 \section{Kepler Re-analysis}\label{sec:Kepler}
@@
 
-Figure \ref{fig:tserPC} shows the time series of the first two principal components.
-We highlight the quiescent periods also discussed in \citet{kawahara2013starspots}, \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
-The first principal component largely tracks closely with the dot product of the average light curve ($A'$).
-The quiescent periods show up as 14 to 36 day long intervals of low amplitude events.
-The second principal component shows some sinusoidal behavior at a $\sim$500 day period, indicating that the large particles may be evolving.
-However, the timescales are much longer than dynamical and sublimation times for this system.
-
 \begin{figure*}[!hbtp]
@@
 
+Figure \ref{fig:tserPC} shows the time series of the first two principal components.
+We highlight the quiescent periods, which are also discussed in \citet{kawahara2013starspots}, \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
+The first principal component largely tracks closely with the dot product of the average light curve ($A'$).
+The quiescent periods show up as 14 to 36 day long intervals of low amplitude events.
+The second principal component shows some sinusoidal behavior at a $\sim$500 day period, indicating that the large particles may be evolving.
+However, the timescales are much longer than dynamical and sublimation times for this system.
+
 %We also show the first two principal components as a scatter plot in Figure \ref{fig:pcaVectorsComp}.
@@
 In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
-The peaks at 0.654 days in both the first and second principal components are the same as the orbital period and are the same as the sampling interval of the time series.
+The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the the sampling cadence of the time series of amplitudes and principal components.
 The first component, corresponding to the transit depth, has peaks at 22.9, 153 and 750 days.
@@
 \caption{Periodograms of the principal component time series shown in Figure \ref{fig:tserPC}, with peaks marked with red circles.
-The first peak at 0.654 days for both principal components is the orbital period, which is the sampling time for these time series.
-The PC$_1$ also peaks at 153 and 750 days, likely because of the intervals of low disintegration activity.
+The first peak at 0.654 days for both principal components is the orbital period, which is the sampling cadence of the principal components' time series.
+PC$_1$ also peaks at 22.9, 153 and 750 days.
 The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.
-The second principal components shows one dominant peak at 491 days, in addition to the 0.654 orbital period.}\label{fig:ampPeriodogram}
+The second principal components shows one dominant peak at 491 days, in addition to the 0.654 orbital period, indicating possible long term evolution of the dust particle sizes.}\label{fig:ampPeriodogram}
 \end{centering}
@@
 \subsection{Statistical Analysis of Ground-based Photometry}\label{sec:statistics}
-We calculate and evalute the Kepler transit amplitudes to better understand the long-term behavior of \sha's disintegration.
+We calculate and evaluate the Kepler transit amplitudes to compare to ground-based results and to understand the long-term behavior of \sha's disintegration.
 We take the histogram of transit amplitudes as measured by the Kepler light curves (shown in Figure \ref{fig:histoPhot}) and compare these to the ground-based photometry from \citet{schlawin2016kic1255} and this work.
-The histogram of secondary eclipse amplitudes from the Kepler light curves is also shown in \ref{fig:histoPhot}.
+The histogram of secondary eclipse amplitudes from the Kepler light curves is also shown in \ref{fig:histoPhot}, which shows the spread due to photon noise.
 The intrinsic astrophysical variation of the planet disintegration is convolved by this photometric scatter in the data.
+
 We compare the distribution of amplitudes from \citet{schlawin2016kic1255} from the Kepler long cadence data from 2009 to 2013.
-A Kolmogorov-Smirnov test gives a p value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the Kepler Long Cadence data.
+A Kolmogorov-Smirnov (KS) test gives a p value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the Kepler Long Cadence data.
+This indicated a possible slowdown of disintegration activity.
+However, the distribution from this work taken in 2016 shows consistency with the Kepler histogram, with the KS test p value of 0.5 of the null hypothesis. 
+We therefore conclude that the disintegration activity is stochastic with no long-term trend measurable from ground-based photometry.
 
@@
 \caption{Normalized frequency of 4 different transit amplitude distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the secondary eclipse amplitudes from the Kepler spacecraft over this same period, 3) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper observatory campaign in the summer of 2016.
-The \citet{schlawin2016kic1255} (S16) events give a KS-test p value of 0.001 of the null hypothesis when comparing to the Kepler data.
-In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.
+The \citet{schlawin2016kic1255} (S16) events give a KS-test p value of 0.001 when comparing to the Kepler data.
+In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5.
 This indicates that the transit depths are back to normal and there is no slowdown of disintegration activity over time.}\label{fig:histoPhot}

### 2018-07-04 ms.tex
wrote a conclusions section.

@@
 
-\shorttitle{KIC 12557548 b back to normal}
+\shorttitle{KIC 12557548 b back to ``normal''}
 \shortauthors{Schlawin et al.}
@@
 
+We obtained ground-based R band photometry from the Kuiper 61-inch observatory to follow up a possible slowdown in disintegration activity observed in 2013 and 2014.
+\citet{schlawin2016kic1255} found shallow transits (all below the Kepler observatory average) in August-September 2013 and August-September 2014.
+One possibility was a long term evolution of the disintegration activity, such as a reduction of available dusty material of the planet or a slowdown in the disintegration mechanism.
+Our transit depths from June-July 2016 are instead consistent with the depths from the Kepler observatory from 2009 to 2013, with a KS-test between the two distributions having a p-value of 0.5 that depths are drawn from the same distribution.
+This indicates that the shallow transit depths observed in August-September 2013 and August-September 2014 likely fell into the 14-36 day long quiescent intervals of disintegration activity as observed in Kepler photometry \citep{kawahara2013starspots,vanWerkhoven2014,croll2015starspots}.
+
+We re-analyze the existing Kepler photometry with PCA to better understand the time dependence and statistics of the light curves.
+We find that the first eigenvector corresponds to models with small sized dust grains whereas the second eigenvector corresponds to models with large-sized dust grains with larger forward scattering.
+The first principal component tracks closely with the transit depths and exhibits modulations at periods of 22.9, 153 and 750 days.
+The second principal component is nearly sinusoidal with a 491 day period, indicating possible long term evolution of the dust particle sizes.
+The 22.9 day period matches the rotation period of the host star, which has previously been used to tie disintegration to stellar activity \citep{kawahara2013starspots} or occultations of star spots \citep{croll2015starspots}.
+The remaining periodicities are longer than the dynamical and sublimation times of the planet and grains, so a different mechanisms would be required to modulate the activity over these timescales.
+
+\citet{vanlieshout2016kic1255} compile the stellar parameters reported in the literature via photometric and spectroscopic methods and note that the high resolution spectrum show that \shStar\ has the gravity of a sub-giant, whereas all other methods find that it is a main sequence star.
+One exciting possibility suggested in \citet{vanlieshout2016kic1255} is that the planet disintegration affects the spectral lines of the star and affects the high resolution spectrum from \citet{kawahara2013starspots}.
+We explore this possibility by examining archival Subaru HDS spectra of \shStar\.
+We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T=4500 $\pm$ 110 K, log(g) = 4.5, [Fe/H]=-0.1$\pm$0.1, M=0.7$\pm$0.1 R$_\odot$ and M=0.7 $\pm$0.1 M$_\odot$.
+Therefore, the optical depth of any gas sublimating of dust grains is too small to affect the high resolution spectrum.
+We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.
+
 \section{Acknowledgements}

### 2018-07-04 ms.tex
added a bunch more references to the intro for KIC 1255's cousins.

@@
 We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K star.
+This disfavors the hypothesis that planet disintegration affected previous high resolution spectra results.
 We apply PCA to the Kepler long cadence data to understand the modes of disintegration.
-There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes.
+There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism is unclear.
 \end{abstract}
@@
 \citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
-KIC 12557548's (hereafter \shStar's) light curve exhibits periodic flux dips with a period of 0.653 days.
+KIC 12557548's (hereafter \shStar's) light curve exhibits flux dips with a period of 0.653 days.
 Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
@@
 
-Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie.
-Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
-KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
-RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planet candidates or structures within a protoplanetary disk.
-RIK-210 could be accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.
+Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no fully agreed-upon explanations: KIC 8462852 (ie.
+Boyajian's star) \citep{boyajian846}, RIK-210/EPIC 205483258 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
+KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
+RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planet candidates or structures within a protoplanetary disk \citep{stauffer2017orbitingClouds,yu2015ptfO8d8695PlanetHypothesisTest}.
+RIK-210 could be accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude, though only portions of the lightcurve are explained this way \citep{barnes2013PTFO8d8695NodalPrecession,yu2015ptfO8d8695PlanetHypothesisTest}.
 

### 2018-07-06 ms.tex
edits to abstract and intro.

@@
 \begin{abstract}
-KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
-Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of disintegration activity in 2013 and 2014.
-Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
+KIC 12557548 b is first of a growing class of intriguing disintegrating planet candidates, which lose mass in the form of dust particles escaping their surface.
+Here, we follow up two perplexing observations of the system: 1) the transits appeared shallower than average in 2013 and 2014 and 2) the parameters derived from a high resolution spectrum of the star differed from other results using photometry and low resolution spectroscopy.
+We observe 5 transits of the system with the 61-inch Kuiper observatory in 2016 and show that they are consistent with photometry from the Kepler spacecraft in 2009-2013.
 We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K star.
@@
 We apply PCA to the Kepler long cadence data to understand the modes of disintegration.
-There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism is unclear.
+There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism on such long timescales remains unclear.
 \end{abstract}
@@
 The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next 0.653 days later.
-This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
+This indicates that dusty material with a projected area $\sim$1\% of the stellar surface is created and cleared in $\lesssim$ 1 day timescales.
 These unusual light curve behaviors are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
@@
 
-The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding planet evolution and composition.
+The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} and KIC 3542116 \citep{rappaport2018exocomets} showed that other systems have similar light curves and that several disintegrating planet systems may be useful laboratories for understanding planet evolution and composition.
 Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
@@
 Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no fully agreed-upon explanations: KIC 8462852 (ie.
-Boyajian's star) \citep{boyajian846}, RIK-210/EPIC 205483258 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
+Boyajian's star) \citep{boyajian846}, RIK-210/EPIC 205483258 \citep{david2017rik210},  and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
 KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
@@
 There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
-A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$, the modeled mass is 0.014 $M_\oplus$.
+A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$, the modeled mass is 0.014 $M_\oplus$ \citep{perez-becker}.
 
@@
 \caption{Cleaned Kepler Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
-The residuals (Right) have $\lesssim 0.1\%$ residuals in contrast to the average-light curve method used in Figure \ref{fig:riverPlots}.
+The residuals (Right) are $\lesssim 0.1\%$, significantly smaller than the $\sim 0.2\%$ residuals when using the average-light curve method shown in Figure \ref{fig:riverPlots}.
 }\label{fig:riverPlotsPCA}
@@
 We obtained ground-based R band photometry from the Kuiper 61-inch observatory to follow up a possible slowdown in disintegration activity observed in 2013 and 2014.
-\citet{schlawin2016kic1255} found shallow transits (all below the Kepler observatory average) in August-September 2013 and August-September 2014.
+\citet{schlawin2016kic1255} found shallow transits that were all below the Kepler observatory average in August-September 2013 and August-September 2014.
 One possibility was a long term evolution of the disintegration activity, such as a reduction of available dusty material of the planet or a slowdown in the disintegration mechanism.

### 2018-07-06 ms.tex
small edits throughout before sending it out.

@@
 These unusual light curve behaviors are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
-The KIC 12557548 system (hereafter \shStar) has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.
+The KIC 12557548/KOI-3794/Kepler-1520 system (hereafter \shStar) has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.
 
@@
 \citet{budaj12} and \citet{brogi2012} find particle sizes $\sim$0.1 to $\sim$1.0$\mu$m in size based on this method.
+The tail length can also be used to constrain the composition of the particles and \citet{vanlieshout2014kic1255comp} find that the sublimation times of corundum and iron-rich silicates are consistent with the observed tail lengths.
+
+Multiple wavelength monitoring can also constrain the dust particle sizes because the scattering by dust is a strong function of wavelength.
+\citet{bochinski2015evolving} observed wavelength dependence in the transits by \sha\ and find that the extinction is similar to the ISM particles with sizes from 0.25 to 1~$\mu$m.
 Subsequently, \citet{croll2014} obtained a $K'$-band light curve simultaneously with the Kepler spacecraft to put a constraint on the dust extinction as a function of wavelength.
@@
 The SpeX/IRTF spectrum, though affected by systematic noise, confirmed the \citet{croll2014} result that particle sizes are $\gtrsim 0.5\%$ for a pyroxene composition.
-\citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
+\citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probability of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
 This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
@@
 where $F(t)$ is the normalized flux at orbital phase $t$, $A$ is the amplitude parameter, $f_{SC}(t)$ is average Kepler short cadence light curve linearly interpolated at an orbital phase $t$, $B$ is the baseline offset and $C$ is the baseline slope.
-We construct $f_{SC}(t)$ by phasing the Kepler time series with Equation \ref{eq:ephem}, normalizing by the median, removing a quadratic baseline from each transit, averaging the results and subtracting 1.0 to get the differential flux.
+We construct $f_{SC}(t)$ by phasing the Kepler time series with Equation \ref{eq:ephem}, dividing by a quadratic baseline from each transit, averaging the results and subtracting 1.0 to get the differential flux.
 We use the Markov Chain Monte Carlo (MCMC) package \texttt{emcee} \citep{foreman-mackey2013emcee} to find the transit depth amplitude and uncertainty.
@@
 The transit depths listed in Table \ref{tab:photSummary} are ``back to normal'' in that they are consistent with the Kepler results.
-We will revisit the statistics of these events in Section \ref{sec:Kepler}.
+We will revisit the statistics of these events in Section \ref{sec:statistics}.
 
@@
 
-We examine the 17 total quarters of Kepler data for three purposes:
-\begin{enumerate}
-	\item To understand the statistics of the transits and put the 2013-2016 observations in context. Mainly, how likely/unlikely were the weak transits observed in 2013-2014?
-	\item To measure the radius of the planet or put an upper limit on its radius by examining any possible transit beneath the dust signal
-	\item Identify any new patterns or observations from the Kepler data that might occur along the way
-\end{enumerate}
-
+We examine the 17 total quarters of Kepler data to understand the statistics of the transits and put the 2013-2016 observations in context.
+Mainly, we sought to evaluate how likely/unlikely were the weak transits observed in 2013-2014 and normal transits in 2016.
 We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.
@@
 We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected at $\lesssim 50$~ppm, seen in Figure \ref{fig:secEclipse}. 
-We then use the secondary eclipses as a way to characterize the noise of the primary eclipses.
+We then use the secondary eclipses as a way to characterize the noise of the primary transits.
 Both have the same quadratic baseline removal process over the same time intervals.
@@
 If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$ -0.12 to $\sim$0.15).
-The model using the first 4 principal components shown in Figure \ref{fig:riverPlotsPCA} better matches the data (with more degrees of freedom) and has residuals much closer to white noise than the model that uses the dot product with the average light curve.
+The model using the first 4 principal components shown in Figure \ref{fig:riverPlotsPCA} better matches the data and has residuals much closer to white noise than the model that uses the dot product with the average light curve.
 
 Figure \ref{fig:pcaVectorsComp} shows the first 4 eigenvectors as a function of orbital phase.
-For the eigenvectors plot, we multiply each eigenvector by its eigenvalue to emphasize the covariances between the principal components and phase grid variables.
+For the eigenvectors plot, we multiply each eigenvector by its eigenvalue to emphasize the relative covariances between the principal components and phase grid variables.
 The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points (variables) in the phase grid from -0.25 to 0.25.
@@
 models from][]{budaj12}.
-The implication of the PCA then is that the dust particle sizes are changing with time.
+The implication of the PCA then is that the dust particle sizes may be changing with time.
 
@@
 However, the distribution from this work taken in 2016 shows consistency with the Kepler histogram, with the KS test p value of 0.5 of the null hypothesis. 
-We therefore conclude that the disintegration activity is stochastic with no long-term trend measurable from ground-based photometry.
+We therefore conclude that the disintegration activity is stochastic with no long-term slowdown measurable from ground-based photometry.
 
@@
 \citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
-They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
+\citet{vanlieshout2016kic1255} suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
 If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
@@
 All telluric emission features and outliers are masked in this analysis to remove these components.
-Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
+Time-variable outliers, such as cosmic rays, are removed by measuring deviations from the median spectrum for the night.
 The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
@@
 To combine the observations, we found the median spectrum for UT dates 2015 Aug 28 and 2015 Aug 29 to robustly combine the data.
-This median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
+%This median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
 
@@
 We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
-
 We performed wavelength calibration with a Thorium Argon reference spectrum.
@@
 \begin{centering}
-\includegraphics[width=0.7\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
-\caption{Median spectrum of \shStar\ \citep{masuda2018rvKIC1255} near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
+\includegraphics[width=0.49\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\caption{Median spectrum of \shStar\ \citep{masuda2018rvKIC1255} near the Mg triplet (green) compared to 4500 K BOSZ models with two different log(g)s (blue and orange).
+The standard error in the mean is shown at an arbitrary Y location as a red line.}\label{fig:mgTripletBOSZ}
 \end{centering}
 \end{figure}
-
-We explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
-The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
-For each parameter, we change the models by about 2 steps in the BOSZ grid.
-For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
-The errors are estimated from the standard deviation of the spectra over the night.
-
-%A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.
 
@@
 \end{figure*}
+
+We explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
+The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
+For each parameter, we change the models by about 2 steps in the BOSZ grid.
+For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
+The errors are estimated from the standard deviation of the spectra over the night.
+
+%A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.
 
@@
 One possibility was a long term evolution of the disintegration activity, such as a reduction of available dusty material of the planet or a slowdown in the disintegration mechanism.
-Our transit depths from June-July 2016 are instead consistent with the depths from the Kepler observatory from 2009 to 2013, with a KS-test between the two distributions having a p-value of 0.5 that depths are drawn from the same distribution.
+Our transit depths from June-July 2016 are instead consistent with the depths from the Kepler observatory from 2009 to 2013, with a KS-test between the two distributions resulting in a p-value of 0.5 that depths are drawn from the same distribution.
 This indicates that the shallow transit depths observed in August-September 2013 and August-September 2014 likely fell into the 14-36 day long quiescent intervals of disintegration activity as observed in Kepler photometry \citep{kawahara2013starspots,vanWerkhoven2014,croll2015starspots}.
@@
 We re-analyze the existing Kepler photometry with PCA to better understand the time dependence and statistics of the light curves.
-We find that the first eigenvector corresponds to models with small sized dust grains whereas the second eigenvector corresponds to models with large-sized dust grains with larger forward scattering.
+We find that the first eigenvector corresponds to the overall transit depth whereas the second eigenvector corresponds to models of forward-scattering from  large-sized dust grains.
 The first principal component tracks closely with the transit depths and exhibits modulations at periods of 22.9, 153 and 750 days.
@@
 One exciting possibility suggested in \citet{vanlieshout2016kic1255} is that the planet disintegration affects the spectral lines of the star and affects the high resolution spectrum from \citet{kawahara2013starspots}.
-We explore this possibility by examining archival Subaru HDS spectra of \shStar\.
+We explore this possibility by examining archival Subaru HDS spectra of \shStar.
 We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T=4500 $\pm$ 110 K, log(g) = 4.5, [Fe/H]=-0.1$\pm$0.1, M=0.7$\pm$0.1 R$_\odot$ and M=0.7 $\pm$0.1 M$_\odot$.

### 2018-07-17 ms.tex
updated facilities and removed unused appendix.
JKT's suggestions on abstract.

@@
 \newcommand{\shStar}{KIC 1255}
+\newcommand{\kepler}{{\it Kepler}}
 
@@
 
-%\author{Kento Masuda?}
-%\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
-
 \author{Teruyuki Hirano}
@@
 
-\author{Johanna Teske?}
-\affiliation{Department of Terrestrial Magnetism, Carnegie Institution for Science, 5241 Broad Branch Road, NW, Washington, DC 20015}
+\author{Johanna Teske}
+\altaffiliation{Hubble Fellow, jteske@carnegiescience.edu} 
+\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara Street, Pasadena, CA 91101}
 
@@
 
-\author{Jonathan Fraine?}
+\author{Jonathan Fraine}
 \affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
 
-\author{Rafia Bushra?}
+\author{Rafia Bushra}
 \affiliation{Steward Observatory, Tucson AZ 85721}
@@
 Here, we follow up two perplexing observations of the system: 1) the transits appeared shallower than average in 2013 and 2014 and 2) the parameters derived from a high resolution spectrum of the star differed from other results using photometry and low resolution spectroscopy.
-We observe 5 transits of the system with the 61-inch Kuiper observatory in 2016 and show that they are consistent with photometry from the Kepler spacecraft in 2009-2013.
-We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K star.
-This disfavors the hypothesis that planet disintegration affected previous high resolution spectra results.
-We apply PCA to the Kepler long cadence data to understand the modes of disintegration.
+We observe 5 transits of the system with the 61-inch Kuiper telescope in 2016 and show that they are consistent with photometry from the \kepler\ spacecraft in 2009-2013.
+We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_{eff}$=4500 $\pm$110 K star.
+This disfavors the hypothesis that planet disintegration affected the analysis of prior high resolution spectra of this star.
+We apply Principal Component Analysis to the \kepler\ long cadence data to understand the modes of disintegration.
 There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism on such long timescales remains unclear.
@@
 \section{Introduction}
-\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
+\citet{rappaport} first reported the discovery of a highly unusual stellar system in the \kepler\ field.
 KIC 12557548's (hereafter \shStar's) light curve exhibits flux dips with a period of 0.653 days.
@@
 \citet{masuda2018rvKIC1255} find that the upper limit on the radial velocity semi-amplitude is 86 m/s corresponding to a planet mass $\lesssim 0.28 M_{\mathrm Jup}$ using the Subaru High Dispersion Spectrometer (HDS).
-There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
+There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the \kepler\ bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
 A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$, the modeled mass is 0.014 $M_\oplus$ \citep{perez-becker}.
@@
 
-The Kepler spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
+The \kepler\ spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
 During this time, the transit depths averaged around $\sim$0.6\% but varied stochastically from just one 15.7 hour orbit to the next.
@@
 
-The Kepler data was used to put constraints on the particle size distribution and composition of the dust particles.
+The \kepler\ data was used to put constraints on the particle size distribution and composition of the dust particles.
 \citet{budaj12} and \citet{brogi2012} modeled the light curve, which includes a slight increase in flux prior before the transit begins.
@@
 \citet{bochinski2015evolving} observed wavelength dependence in the transits by \sha\ and find that the extinction is similar to the ISM particles with sizes from 0.25 to 1~$\mu$m.
-Subsequently, \citet{croll2014} obtained a $K'$-band light curve simultaneously with the Kepler spacecraft to put a constraint on the dust extinction as a function of wavelength.
+Subsequently, \citet{croll2014} obtained a $K'$-band light curve simultaneously with the \kepler\ spacecraft to put a constraint on the dust extinction as a function of wavelength.
 \citet{croll2014} find a particle size distribution of $\gtrsim 0.5\mu$m.
@@
 The SpeX/IRTF spectrum, though affected by systematic noise, confirmed the \citet{croll2014} result that particle sizes are $\gtrsim 0.5\%$ for a pyroxene composition.
-\citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probability of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
-This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
-We performed follow-up $R$ band photometry of the \shStar\ system to explore these two hypotheses and see if the the disintegration has returned to the levels found in the Kepler mission.
+\citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probability of this randomly occurring based on random behavior from \kepler\ statistics was around 0.2\%.
+This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 \kepler\ quarter analysis) or that the disintegration activity was falling off with time.
+We performed follow-up $R$ band photometry of the \shStar\ system to explore these two hypotheses and see if the the disintegration has returned to the levels found in the \kepler\ mission.
 
@@
 \enddata
-\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper observatory.
+\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper telescope.
 The seeing is expressed as the median FWHM for the night in arcseconds.}
@@
 \section{Photometric Observations}
-We attempted to observe 6 transit events of \sha\ with the Mont4k imager on the 61-inch Kuiper observatory located on Mt Bigelow, Arizona on UT using the f/13.5 Cassegrain focus.
+We attempted to observe 6 transit events of \sha\ with the Mont4k imager on the 61-inch Kuiper telescope located on Mt Bigelow, Arizona on UT using the f/13.5 Cassegrain focus.
 On all nights we used 90 second exposures using a Harris-R filter to best approximate the $r'$ filter used in \citet{schlawin2016kic1255}.
@@
 Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all nights.
-We use the planet transit ephemeris from \citet{croll2015starspots} where the Kepler flux minimum is the ``transit center'':
+We use the planet transit ephemeris from \citet{croll2015starspots} where the \kepler\ flux minimum is the ``transit center'':
 \begin{equation}\label{eq:ephem}
@@
 The expected transit epochs from the ephemeris in \citep{vanWerkhoven2014} are shown for reference as vertical red bars.
-Typical uncertainties for the Kepler ephemeris are $\sim$ 1 minute at these dates due to the large number of transits measured by the Kepler observatory over nearly 4 years.
-The ``transit duration'' from Kepler light curves is about 0.06 days\footnote{We define the transit duration as the point at which the average light curve measured by the Kepler spacecraft drops below 99.95\% of the normalized flux as in \citet{schlawin2016kic1255}}, which is consistent with these transit durations.
+Typical uncertainties for the \kepler\ ephemeris are $\sim$ 1 minute at these dates due to the large number of transits measured by the \kepler\ observatory over nearly 4 years.
+The ``transit duration'' from \kepler\ light curves is about 0.06 days\footnote{We define the transit duration as the point at which the average light curve measured by the \kepler\ spacecraft drops below 99.95\% of the normalized flux as in \citet{schlawin2016kic1255}}, which is consistent with these transit durations.
 
-We find the best fit to each light curve using the average Kepler short cadence light curve as a model.
+We find the best fit to each light curve using the average \kepler\ short cadence light curve as a model.
 We include a linear baseline so that the model is
@@
 \end{equation}
-where $F(t)$ is the normalized flux at orbital phase $t$, $A$ is the amplitude parameter, $f_{SC}(t)$ is average Kepler short cadence light curve linearly interpolated at an orbital phase $t$, $B$ is the baseline offset and $C$ is the baseline slope.
-We construct $f_{SC}(t)$ by phasing the Kepler time series with Equation \ref{eq:ephem}, dividing by a quadratic baseline from each transit, averaging the results and subtracting 1.0 to get the differential flux.
+where $F(t)$ is the normalized flux at orbital phase $t$, $A$ is the amplitude parameter, $f_{SC}(t)$ is average \kepler\ short cadence light curve linearly interpolated at an orbital phase $t$, $B$ is the baseline offset and $C$ is the baseline slope.
+We construct $f_{SC}(t)$ by phasing the \kepler\ time series with Equation \ref{eq:ephem}, dividing by a quadratic baseline from each transit, averaging the results and subtracting 1.0 to get the differential flux.
 We use the Markov Chain Monte Carlo (MCMC) package \texttt{emcee} \citep{foreman-mackey2013emcee} to find the transit depth amplitude and uncertainty.
@@
 Orange squares mark 20 minute flux bins.
-The expected transit epochs from the Kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
-We also show the average Short Cadence Kepler light curves for each of the transit events for comparison with the average.
+The expected transit epochs from the \kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
+We also show the average Short Cadence \kepler\ light curves for each of the transit events for comparison with the average.
 Transits are clearly visible for all five nights except for UT2016-06-14.}\label{fig:allNightrefCorrect}
@@
 
-In contrast to \citet{schlawin2016kic1255}, the transit depths in 2016 June and 2016 July are similar to the distribution measured by the Kepler spacecraft from 2009 to 2013.
-\citet{schlawin2016kic1255} found significantly weaker transit depths that the Kepler spacecraft in 2013 Aug-Sep and 2014 Aug-Sep, which indicated that either disintegration activity was slowing down or that there were quiescent periods during those observations.
-The transit depths listed in Table \ref{tab:photSummary} are ``back to normal'' in that they are consistent with the Kepler results.
+In contrast to \citet{schlawin2016kic1255}, the transit depths in 2016 June and 2016 July are similar to the distribution measured by the \kepler\ spacecraft from 2009 to 2013.
+\citet{schlawin2016kic1255} found significantly weaker transit depths that the \kepler\ spacecraft in 2013 Aug-Sep and 2014 Aug-Sep, which indicated that either disintegration activity was slowing down or that there were quiescent periods during those observations.
+The transit depths listed in Table \ref{tab:photSummary} are ``back to normal'' in that they are consistent with the \kepler\ results.
 We will revisit the statistics of these events in Section \ref{sec:statistics}.
 
-\section{Kepler Re-analysis}\label{sec:Kepler}
+\section{\kepler\ Re-analysis}\label{sec:Kepler}
 
-We examine the 17 total quarters of Kepler data to understand the statistics of the transits and put the 2013-2016 observations in context.
+We examine the 17 total quarters of \kepler\ data to understand the statistics of the transits and put the 2013-2016 observations in context.
 Mainly, we sought to evaluate how likely/unlikely were the weak transits observed in 2013-2014 and normal transits in 2016.
-We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.
-The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
+We downloaded all 17 quarters of \kepler\ Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.
+The \kepler\ data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
 A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 phase window.
@@
 
-\subsection{Kepler Secondary Eclipse}
+\subsection{\kepler\ Secondary Eclipse}
 
@@
 \includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
-\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
+\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of \kepler\ Long Cadence data.
 Here, the data are binned to orbital phases of 0.1 (1.5 minutes) and errors calculated from the standard error in the mean of the data within a bin.
@@
 \includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
-\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
+\caption{Cleaned \kepler\ Long-cadence data (Left) and model fit using the average light curve (Middle).
 (Right) The residuals show significant deviations near phases of -0.5 and 0.05.
@@
 In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
-We linearly interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 15 minutes (to Nyquist sample the 30 minute observation cadence) and put together all the time series that have no gaps into this two dimensional grid.
-This cleaned Kepler long-cadence array is shown in Figure \ref{fig:riverPlots}.
+We linearly interpolated the \kepler\ long-cadence data set onto a fixed phase grid with a spacing of 15 minutes (to Nyquist sample the 30 minute observation cadence) and put together all the time series that have no gaps into this two dimensional grid.
+This cleaned \kepler\ long-cadence array is shown in Figure \ref{fig:riverPlots}.
 
@@
 The 0.2\% residuals with this average model are comparable with the typical photometric scatter of $\sim$ 0.1\% to 0.2\% for 20 minute timescales in \citet{schlawin2016kic1255} and this work.
-We statistically compare the transit depths from the Kepler mission from 2009 to 2013 to the ground-based measurements from 2013 through 2016 in Section \ref{sec:statistics}.
+We statistically compare the transit depths from the \kepler\ mission from 2009 to 2013 to the ground-based measurements from 2013 through 2016 in Section \ref{sec:statistics}.
 
@@
 \includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
-\caption{Cleaned Kepler Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
+\caption{Cleaned \kepler\ Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
 The residuals (Right) are $\lesssim 0.1\%$, significantly smaller than the $\sim 0.2\%$ residuals when using the average-light curve method shown in Figure \ref{fig:riverPlots}.
@@
 \subsection{Statistical Analysis of Ground-based Photometry}\label{sec:statistics}
-We calculate and evaluate the Kepler transit amplitudes to compare to ground-based results and to understand the long-term behavior of \sha's disintegration.
-We take the histogram of transit amplitudes as measured by the Kepler light curves (shown in Figure \ref{fig:histoPhot}) and compare these to the ground-based photometry from \citet{schlawin2016kic1255} and this work.
-The histogram of secondary eclipse amplitudes from the Kepler light curves is also shown in \ref{fig:histoPhot}, which shows the spread due to photon noise.
+We calculate and evaluate the \kepler\ transit amplitudes to compare to ground-based results and to understand the long-term behavior of \sha's disintegration.
+We take the histogram of transit amplitudes as measured by the \kepler\ light curves (shown in Figure \ref{fig:histoPhot}) and compare these to the ground-based photometry from \citet{schlawin2016kic1255} and this work.
+The histogram of secondary eclipse amplitudes from the \kepler\ light curves is also shown in \ref{fig:histoPhot}, which shows the spread due to photon noise.
 The intrinsic astrophysical variation of the planet disintegration is convolved by this photometric scatter in the data.
 
-We compare the distribution of amplitudes from \citet{schlawin2016kic1255} from the Kepler long cadence data from 2009 to 2013.
-A Kolmogorov-Smirnov (KS) test gives a p value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the Kepler Long Cadence data.
+We compare the distribution of amplitudes from \citet{schlawin2016kic1255} from the \kepler\ long cadence data from 2009 to 2013.
+A Kolmogorov-Smirnov (KS) test gives a p value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the \kepler\ Long Cadence data.
 This indicated a possible slowdown of disintegration activity.
-However, the distribution from this work taken in 2016 shows consistency with the Kepler histogram, with the KS test p value of 0.5 of the null hypothesis. 
+However, the distribution from this work taken in 2016 shows consistency with the \kepler\ histogram, with the KS test p value of 0.5 of the null hypothesis. 
 We therefore conclude that the disintegration activity is stochastic with no long-term slowdown measurable from ground-based photometry.
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
-\caption{Normalized frequency of 4 different transit amplitude distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the secondary eclipse amplitudes from the Kepler spacecraft over this same period, 3) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper observatory campaign in the summer of 2016.
-The \citet{schlawin2016kic1255} (S16) events give a KS-test p value of 0.001 when comparing to the Kepler data.
-In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5.
+\caption{Normalized frequency of 4 different transit amplitude distributions: 1) all of the \kepler\ Long Cadence data from 2009 to 2013, 2) the secondary eclipse amplitudes from the \kepler\ spacecraft over this same period, 3) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper telescope campaign in the summer of 2016.
+The \citet{schlawin2016kic1255} (S16) events give a KS-test p value of 0.001 when comparing to the \kepler\ data.
+In contrast, the 2016 photometric results in this work are consistent with the \kepler\ Long Cadence data, giving a  p value of 0.5.
 This indicates that the transit depths are back to normal and there is no slowdown of disintegration activity over time.}\label{fig:histoPhot}
@@
 The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
-The second set of observations happened after the reaction wheel failure on 2013 May 11\footnote{\url{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy to assess disintegration activity preceding or following the spectra.
+The second set of observations happened after the reaction wheel failure on 2013 May 11\footnote{\url{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main \kepler\ field, so no simultaneous \kepler\ photometry was available with the high dispersion spectroscopy to assess disintegration activity preceding or following the spectra.
 None of the observations was timed during a primary transit (phase = 0.0) or secondary eclipse (phase = 0.5 for a circular orbit).
@@
 
-We obtained ground-based R band photometry from the Kuiper 61-inch observatory to follow up a possible slowdown in disintegration activity observed in 2013 and 2014.
-\citet{schlawin2016kic1255} found shallow transits that were all below the Kepler observatory average in August-September 2013 and August-September 2014.
+We obtained ground-based R band photometry from the Kuiper 61-inch telescope to follow up a possible slowdown in disintegration activity observed in 2013 and 2014.
+\citet{schlawin2016kic1255} found shallow transits that were all below the \kepler\ observatory average in August-September 2013 and August-September 2014.
 One possibility was a long term evolution of the disintegration activity, such as a reduction of available dusty material of the planet or a slowdown in the disintegration mechanism.
-Our transit depths from June-July 2016 are instead consistent with the depths from the Kepler observatory from 2009 to 2013, with a KS-test between the two distributions resulting in a p-value of 0.5 that depths are drawn from the same distribution.
-This indicates that the shallow transit depths observed in August-September 2013 and August-September 2014 likely fell into the 14-36 day long quiescent intervals of disintegration activity as observed in Kepler photometry \citep{kawahara2013starspots,vanWerkhoven2014,croll2015starspots}.
+Our transit depths from June-July 2016 are instead consistent with the depths from the \kepler\ observatory from 2009 to 2013, with a KS-test between the two distributions resulting in a p-value of 0.5 that depths are drawn from the same distribution.
+This indicates that the shallow transit depths observed in August-September 2013 and August-September 2014 likely fell into the 14-36 day long quiescent intervals of disintegration activity as observed in \kepler\ photometry \citep{kawahara2013starspots,vanWerkhoven2014,croll2015starspots}.
 
-We re-analyze the existing Kepler photometry with PCA to better understand the time dependence and statistics of the light curves.
+We re-analyze the existing \kepler\ photometry with PCA to better understand the time dependence and statistics of the light curves.
 We find that the first eigenvector corresponds to the overall transit depth whereas the second eigenvector corresponds to models of forward-scattering from  large-sized dust grains.
@@
 %Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
-%Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the 61-inch Kuiper telescope on Mt Bigelow.
 %MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
@@
 
-\facility{Subaru}
+\facility{Subaru, SO:Kuiper, Kepler}
 
@@
 
-\appendix
+%\appendix
 

### 2018-07-17 ms.tex
JKT comments on intro.

@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:Intro}
 \citet{rappaport} first reported the discovery of a highly unusual stellar system in the \kepler\ field.
@@
 
-The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} and KIC 3542116 \citep{rappaport2018exocomets} showed that other systems have similar light curves and that several disintegrating planet systems may be useful laboratories for understanding planet evolution and composition.
-Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
+After the discovery of K1255, other systems were found to show similar light curve behavior: K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} and KIC 3542116 \citep{rappaport2018exocomets}.
+A collection, albeit small, of several different disintegrating planet systems makes for a useful laboratory for understanding planet evolution and composition.
+Multi-wavelength light curve measurements show that the dust particles inferred to be escaping from these objects can have wavelength-dependent transmission, as predicted for sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
 
@@
 Boyajian's star) \citep{boyajian846}, RIK-210/EPIC 205483258 \citep{david2017rik210},  and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
-KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
-RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planet candidates or structures within a protoplanetary disk \citep{stauffer2017orbitingClouds,yu2015ptfO8d8695PlanetHypothesisTest}.
+KIC 8462852 may be a family of comets from one or more parent bodies that recently broke apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
+RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr, respectively), so they may be proto-planet candidates or structures within a protoplanetary disk \citep{stauffer2017orbitingClouds,yu2015ptfO8d8695PlanetHypothesisTest}.
 RIK-210 could be accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude, though only portions of the lightcurve are explained this way \citep{barnes2013PTFO8d8695NodalPrecession,yu2015ptfO8d8695PlanetHypothesisTest}.
+
+The \kepler\ spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
+During this time, the transit depths averaged around $\sim$0.6\% but varied stochastically from just one 15.7 hour orbit to the next.
+\citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
+There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month in duration.
 
@@
 There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the \kepler\ bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
-A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$, the modeled mass is 0.014 $M_\oplus$ \citep{perez-becker}.
+A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$ (determined by the mass of dust needed to absorb and scatter 10$^{-2}$ of star light per orbit), the modeled mass is 0.014 $M_\oplus$ \citep{perez-becker}.
 
-One possible explanation of for the planet disintegration is that it is tied to stellar activity.
-\citet{kawahara2013starspots} found an anti-correlation between stellar flux and the depth of transit events, which suggested that the alignment of the planet's position (true anomaly) causes disintegration.
+One possible explanation for the planet disintegration is that it is tied to stellar activity.
+\citet{kawahara2013starspots} found an anti-correlation between stellar flux and the depth of transit events and suggested that the alignment of the planet's position (true anomaly) with active regions on the star causes disintegration.
 The alignment of spots and disintegration activity could be due to XUV photoevaporation or magnetic reconnection events.
 The anti-correlation between stellar flux and transit depth was confirmed by \citet{croll2015starspots} though they find that occultations of star spots can also modulate the transit depth at the 22.9 day rotation period of the star.
-
-The \kepler\ spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
-During this time, the transit depths averaged around $\sim$0.6\% but varied stochastically from just one 15.7 hour orbit to the next.
-\citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
-There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month in duration.
 
@@
 This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 \kepler\ quarter analysis) or that the disintegration activity was falling off with time.
-We performed follow-up $R$ band photometry of the \shStar\ system to explore these two hypotheses and see if the the disintegration has returned to the levels found in the \kepler\ mission.
+We performed follow-up $R$ band photometry of the \shStar\ system to explore these two hypotheses and see if the the disintegration has returned to the levels found in the \kepler\ mission and discuss this in Section \ref{sec:photObs}.
+We also re-analyze the \kepler\ photometry in order to quantify the light curve behavior in Section \ref{sec:Kepler}.
 
@@
 This would enable compositional and kinematic studies of the disintegrating planet.
-Here, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
+In Section \ref{sec:SubaruDescrip}, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
 
@@
 
-\section{Photometric Observations}
+\section{Photometric Observations}\label{sec:photObs}
 We attempted to observe 6 transit events of \sha\ with the Mont4k imager on the 61-inch Kuiper telescope located on Mt Bigelow, Arizona on UT using the f/13.5 Cassegrain focus.

### 2018-07-18 ms.tex
JKT comments on section 2.

@@
 \startdata
-2016 Jun 10 & Clouds	& \nodata & \nodata &  \nodata \\
+2016 Jun 10 & Cloudy	& \nodata & \nodata &  \nodata \\
 2016 Jun 12 & Clear 	& 1.29 $\rightarrow$ 1.06 $\rightarrow$ 1.10	& 1.3 &	0.94 $\pm$ 0.16 \\
@@
 \caption{Reference-corrected time series photometry \shStar\ for all nights (blue circles).
-Orange squares mark 20 minute flux bins.
+Orange squares mark 20 minute flux bins for visual clarity.
 The expected transit epochs from the \kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
-We also show the average Short Cadence \kepler\ light curves for each of the transit events for comparison with the average.
-Transits are clearly visible for all five nights except for UT2016-06-14.}\label{fig:allNightrefCorrect}
+We also fit each light curve with a model that scales the average \kepler\ short cadence data (Equation \ref{eq:transFitting}) shown in green.
+Transits are clearly visible for all nights except for UT 2016 Jun 14.}\label{fig:allNightrefCorrect}
 \end{centering}
@@
 To ease the visual comparison of the models and measured data, we bin the 61-inch Mont4K data into 20 minute long bins, shown in Figure \ref{fig:allNightrefCorrect}.
-Obvious cosmic ray outliers were discarded by removing points with fluxes below 0.98 and above 1.02 times the median flux.
+Obvious cosmic ray outliers were discarded by removing points (at any epoch within the reference-corrected time series) with fluxes below 0.98 and above 1.02 times the median flux for the night.
 The error bars for the binned data are calculated from the standard error in the mean for each bin.
@@
 We examine the 17 total quarters of \kepler\ data to understand the statistics of the transits and put the 2013-2016 observations in context.
-Mainly, we sought to evaluate how likely/unlikely were the weak transits observed in 2013-2014 and normal transits in 2016.
+Mainly, we sought to evaluate the likelihood of the weak transits observed in 2013-2014 and normal transits in 2016.
 We downloaded all 17 quarters of \kepler\ Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.

### 2018-07-19 ms.tex
added a few senences on the transit light source effect.

@@
 The alignment of spots and disintegration activity could be due to XUV photoevaporation or magnetic reconnection events.
-The anti-correlation between stellar flux and transit depth was confirmed by \citet{croll2015starspots} though they find that occultations of star spots can also modulate the transit depth at the 22.9 day rotation period of the star.
+The anti-correlation between stellar flux and transit depth was confirmed by \citet{croll2015starspots}, though the authors find that occultations of star spots can also modulate the transit depth at the 22.9 day rotation period of the star.
+Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths exoplanets of M stars, the ``transit source light effect.''
+For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can vary by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin Rackham, private communication, 2018}
+The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage.
 
@@
 Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
+Thanks to Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star.
 

### 2018-07-20 ms.tex
finished JKT's comments.

@@
 \includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255_transformed.pdf}
-\caption{The principal component eigenvectors scaled by their eigenvalues (Left), shows that the first component largely describes the extinction while the second shows the contributions from forward scattering.
-When the eigenvectors are transformed into light curves (Right), it can be seen that the first component corresponds to small dust particle sizes with negligible forward scattering and that the second component corresponds to large dust particle sizes with pronounced forward scattering before and after the transit mid-point.
+\caption{The principal component eigenvectors scaled by their eigenvalues (Left), shows that the first eigenvector largely describes the extinction while the second shows the contributions from forward scattering.
+When the eigenvectors are transformed into light curves (Right), it can be seen that the first eigenvector corresponds to small dust particle sizes with negligible forward scattering \citep[dash-dot purple model][]{budaj12}.
+The second eigenvector resembles models with large dust particle sizes with pronounced forward scattering before and after the transit mid-point \citep[dashed brown model][]{budaj12}.
+The models are offset vertically for clarity.
 }\label{fig:pcaVectorsComp}
@@
 We use a covariance matrix as opposed to correlation matrix to calculate the principal component eigenvectors.
-In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
+In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component eigenvectors \citep{jolliffe2002pca}.
 However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units (normalized flux).
@@
 We also transform the eigenvectors into light curves by multiplying each eigenvector by the standard deviation of principal components and adding it to the average light curve.
-The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering whereas the second eigenvector corresponds to models of large dust grains with more forward scattering \citep[e.g.
-models from][]{budaj12}.
+
+The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering so that the light curve is dominated by the extinction \citep{budaj12}.
+We also note that the second eigenvector resembles models of large dust grains from \citet{budaj12}, where the forward scattering from particles that are a similar order of magnitude as the wavelength cause a pronounced pre-ingress flux increase.
+The fact that the pre-ingress flux increase is not found in the first eigenvector and instead is pronounced in orthogonal eigenvectors suggests that the dust particle sizes may be changing in time.
+We would expect that a dust cloud that only varies in the number of particles but not in grain size would be exhibit a forward scattering in the first principal component because the forward scattering flux increase goes up with the number of particles.
+
 The implication of the PCA then is that the dust particle sizes may be changing with time.
@@
 
-Figure \ref{fig:tserPC} shows the time series of the first two principal components.
+Figure \ref{fig:tserPC} shows the time series of the first two principal components (PC$_1$ and PC$_2$).
 We highlight the quiescent periods, which are also discussed in \citet{kawahara2013starspots}, \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
@@
 We take the histogram of transit amplitudes as measured by the \kepler\ light curves (shown in Figure \ref{fig:histoPhot}) and compare these to the ground-based photometry from \citet{schlawin2016kic1255} and this work.
-The histogram of secondary eclipse amplitudes from the \kepler\ light curves is also shown in \ref{fig:histoPhot}, which shows the spread due to photon noise.
+The histogram of secondary eclipse amplitudes from the \kepler\ light curves is also shown in Figure \ref{fig:histoPhot}, which shows the spread due to photon noise.
 The intrinsic astrophysical variation of the planet disintegration is convolved by this photometric scatter in the data.
@@
 We compare the distribution of amplitudes from \citet{schlawin2016kic1255} from the \kepler\ long cadence data from 2009 to 2013.
-A Kolmogorov-Smirnov (KS) test gives a p value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the \kepler\ Long Cadence data.
+A Kolmogorov-Smirnov (KS) test gives a $p$ value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the \kepler\ Long Cadence data.
 This indicated a possible slowdown of disintegration activity.
-However, the distribution from this work taken in 2016 shows consistency with the \kepler\ histogram, with the KS test p value of 0.5 of the null hypothesis. 
+However, the distribution from this work taken in 2016 shows consistency with the \kepler\ histogram, with the KS test $p$ value of 0.5 of the null hypothesis. 
 We therefore conclude that the disintegration activity is stochastic with no long-term slowdown measurable from ground-based photometry.
@@
 \caption{Normalized frequency of 4 different transit amplitude distributions: 1) all of the \kepler\ Long Cadence data from 2009 to 2013, 2) the secondary eclipse amplitudes from the \kepler\ spacecraft over this same period, 3) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper telescope campaign in the summer of 2016.
-The \citet{schlawin2016kic1255} (S16) events give a KS-test p value of 0.001 when comparing to the \kepler\ data.
-In contrast, the 2016 photometric results in this work are consistent with the \kepler\ Long Cadence data, giving a  p value of 0.5.
+The \citet{schlawin2016kic1255} (S16) events give a KS-test $p$ value of 0.001 when comparing to the \kepler\ data.
+In contrast, the 2016 photometric results in this work are consistent with the \kepler\ Long Cadence data, giving a  $p$ value of 0.5.
 This indicates that the transit depths are back to normal and there is no slowdown of disintegration activity over time.}\label{fig:histoPhot}
@@
 The second set of observations happened after the reaction wheel failure on 2013 May 11\footnote{\url{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main \kepler\ field, so no simultaneous \kepler\ photometry was available with the high dispersion spectroscopy to assess disintegration activity preceding or following the spectra.
-None of the observations was timed during a primary transit (phase = 0.0) or secondary eclipse (phase = 0.5 for a circular orbit).
+None of the observations were timed during a primary transit (phase = 0.0) or secondary eclipse (phase = 0.5 for a circular orbit).
 
@@
 \subsection{Data Reduction}
-For the 2015 data, we use the same spectra as in \citep{masuda2018rvKIC1255}.
+For the 2015 data, we use the same spectra, as in \citet{masuda2018rvKIC1255}.
 All telluric emission features and outliers are masked in this analysis to remove these components.
@@
 All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
-To combine the observations, we found the median spectrum for UT dates 2015 Aug 28 and 2015 Aug 29 to robustly combine the data.
+We combined the normalized spectra from UT dates 2015 Aug 28 and 2015 Aug 29 with a median in the time direction, which is more robust to cosmic rays than an average.
 %This median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
@@
 We performed wavelength calibration with a Thorium Argon reference spectrum.
-The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
+The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in the x direction and 4th order in the y direction.
 This polynomial fit has a RMS error of 0.02$\AA$.
@@
 \subsection{Comparison to BOSZ}
-We first evaluate stellar parameters by comparing to the high resolving power ($R=100,000$) BOSZ grids of ATLAS-APOGEE ATLAS9 models \citep{bohlin2017bosz} to the median spectrum from 2015.
+We first evaluate stellar parameters by comparing the high resolving power ($R=100,000$) BOSZ grids of ATLAS-APOGEE ATLAS9 models \citep{bohlin2017bosz} to the median spectrum from 2015.
 Since the discrepancies in the literature are mostly differences in the surface gravity (see Table \ref{tab:stellObsParams}), we study the gravity-sensitive Mg triplet near 517 nm.
 The $R=100,000$ models are convolved with a Gaussian kernel that has a standard deviation $\sigma_K = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
-This was a smaller we expected from combining inverse resolving powers in quadrature, which would imply that an $R=75,000 $ kernel convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
+This was smaller than we expected from combining inverse resolving powers in quadrature, which would imply that an $R=75,000 $ kernel convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
 We start by comparing the measured spectrum with two BOSZ models in Figure \ref{fig:mgTripletBOSZ}.
@@
 
-\begin{figure}[!hbtp]
+\begin{figure*}[!hbtp]
 \begin{centering}
-\includegraphics[width=0.49\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\includegraphics[width=0.85\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
 \caption{Median spectrum of \shStar\ \citep{masuda2018rvKIC1255} near the Mg triplet (green) compared to 4500 K BOSZ models with two different log(g)s (blue and orange).
@@
 \end{centering}
-\end{figure}
+\end{figure*}
 
@@
 
-After initial constraints on the models from the sensitivity to parameters search, we downloaded a grid of BOSZ models with temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
-We found the model with the  $\chi^2$ statistic over the Mg triple lines from 5160 to 51690 $\AA$
+After initial constraints on the models from the sensitivity to parameters search, we downloaded a grid of BOSZ models with effective temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
+We found the model with the  $\chi^2$ statistic over the Mg triple lines from 5160 to 5190 $\AA$
 As discussed above, we use an approximate $\chi^2$ statistic over the wavelength range covering the Mg triplet (5160 $\AA$ to 5190 $\AA$).
-The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
-This is similar to the log(g)$\approx$4.6, T=4500 stellar parameters derived from photometry and low resolution spectroscopy listed in Table \ref{tab:stellObsParams}.
+The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T$_{eff}$=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
+This is similar to the log(g)$\approx$4.6, T$_{eff}$=4500 stellar parameters derived from photometry and low resolution spectroscopy listed in Table \ref{tab:stellObsParams}.
 
@@
 The resulting best-fit parameters from \texttt{SpecMatch-Emp} are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$ and Mass=0.7 $\pm 0.1 $M$_\odot$.
-The output \texttt{SpecMatch-Emp} age constraint of 9.6 $\pm$ 0.2 Gyr is likely an underestimated error in the age.
 Figure \ref{fig:SpecMatch-EmpComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{SpecMatch-Emp}.
@@
 We explore this possibility by examining archival Subaru HDS spectra of \shStar.
-We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T=4500 $\pm$ 110 K, log(g) = 4.5, [Fe/H]=-0.1$\pm$0.1, M=0.7$\pm$0.1 R$_\odot$ and M=0.7 $\pm$0.1 M$_\odot$.
+We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4500 $\pm$ 110 K, log(g) = 4.5, [Fe/H]=-0.1$\pm$0.1, M=0.7$\pm$0.1 R$_\odot$ and M=0.7 $\pm$0.1 M$_\odot$.
 Therefore, the optical depth of any gas sublimating of dust grains is too small to affect the high resolution spectrum.

### 2018-07-20 ms.tex
a few corrections from BG and TH.

@@
 
-\author{Betsy Green?}
+\author{Elizabeth Green}
 \affiliation{Steward Observatory, Tucson AZ 85721}
@@
 12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
-The reference stars are identified Figure \ref{fig:refStars} across the 9.8\arcmin $\times$ 9.8 \arcmin\ Mont4K field of view.
+The reference stars are identified Figure \ref{fig:refStars} across the 9.7\arcmin $\times$ 9.7 \arcmin\ Mont4K field of view.
 These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \shStar.
@@
 \includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
-\caption{Time series photometry for all stars and all nights nights.
+\caption{Time series photometry for all stars and all nights.
 The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.

### 2018-07-21 ms.tex
wording suggestions from TH and RB.

@@
 \citet{rappaport} first reported the discovery of a highly unusual stellar system in the \kepler\ field.
-KIC 12557548's (hereafter \shStar's) light curve exhibits flux dips with a period of 0.653 days.
-Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
+KIC 12557548's light curve exhibits flux dips with a period of 0.653 days.
+Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$0\% to $\sim$1.2\%.
 The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next 0.653 days later.
-This indicates that dusty material with a projected area $\sim$1\% of the stellar surface is created and cleared in $\lesssim$ 1 day timescales.
-These unusual light curve behaviors are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
+This is radially different from a transiting planet, where the planet absorbs the same amount of light from the star each orbit and does so symmetrically about the star, modulo stellar inhomogenities.
+The time variability of the flux dips indicates that material with a projected area $\sim$1\% of the stellar surface is created and cleared in $\lesssim$ 1 day timescales in order to extinct $\sim$1.2\% of starlight at one epoch and $\sim$0\% at another.
+These unusual light curve behaviors are best explained as dust extinction from a comet-like tail of material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
+The comet-like shape of the dust explains the asymmetric shape of the light curve profile.
 The KIC 12557548/KOI-3794/Kepler-1520 system (hereafter \shStar) has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.
@@
 The \kepler\ data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
-A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 phase window.
+A quadratic baseline is fit to all the points before a phase of -0.12 and after a phase of 0.15 within the $\pm$ 0.28 phase window.
+The -0.12 and 0.28 phases are set from the points within the average \kepler\ light curve that are within $\pm$ 200 ppm from the median out-of-transit flux.
 All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
@@
 
-We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected at $\lesssim 50$~ppm, seen in Figure \ref{fig:secEclipse}. 
+We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected at f$_p$/f$_*$ $\lesssim 50$~ppm, seen in Figure \ref{fig:secEclipse}, where f$_p$/f$_*$ is the relative flux of the planet to star in the Kepler bandpass.
 We then use the secondary eclipses as a way to characterize the noise of the primary transits.
@@
 \includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
-\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of \kepler\ Long Cadence data.
+\caption{No secondary eclipse (f$_p$/f$_*$ $\lesssim$ 50 ppm) is detected from a phase range of 0.25 to 0.75, even with 17 quarters (4 years) of \kepler\ Long Cadence data.
 Here, the data are binned to orbital phases of 0.1 (1.5 minutes) and errors calculated from the standard error in the mean of the data within a bin.
@@
 \caption{Cleaned \kepler\ Long-cadence data (Left) and model fit using the average light curve (Middle).
-(Right) The residuals show significant deviations near phases of -0.5 and 0.05.
+(Right) The residuals show significant deviations near phases of -0.05 and 0.05.
 }\label{fig:riverPlots}
@@
 The second principal component shows some sinusoidal behavior at a $\sim$500 day period, indicating that the large particles may be evolving.
-However, the timescales are much longer than dynamical and sublimation times for this system.
+However, the timescale of these sinusoidal modulations of PC$_2$ is much longer than dynamical time (t$_{dyn} \sim$ P = 0.65 days) and sublimation times \citep[$t_{sub} \sim$1 day][]{rappaport} for this system.
 
@@
 We find no statistically significant differences between the 2013 and 2015 spectra, as shown in Figure \ref{fig:spec2013vs2015}.
-We then proceed with the 2015 data to constrain stellar models since it has 6.7 hours of total exposure time compared (compared to 1.5 hours in 2013).
+We then proceed with the 2015 data to constrain stellar models since it has 6.7 hours of total exposure time (compared to 1.5 hours in 2013).
 
@@
 
-We re-analyze the existing \kepler\ photometry with PCA to better understand the time dependence and statistics of the light curves.
-We find that the first eigenvector corresponds to the overall transit depth whereas the second eigenvector corresponds to models of forward-scattering from  large-sized dust grains.
+We re-analyzed the existing \kepler\ photometry with PCA to better understand the time dependence and statistics of the light curves.
+We found that the first eigenvector corresponds to the overall transit depth whereas the second eigenvector corresponds to models of forward-scattering from  large-sized dust grains.
 The first principal component tracks closely with the transit depths and exhibits modulations at periods of 22.9, 153 and 750 days.
@@
 The 22.9 day period matches the rotation period of the host star, which has previously been used to tie disintegration to stellar activity \citep{kawahara2013starspots} or occultations of star spots \citep{croll2015starspots}.
-The remaining periodicities are longer than the dynamical and sublimation times of the planet and grains, so a different mechanisms would be required to modulate the activity over these timescales.
+The remaining periodicities are longer than the dynamical and sublimation times of the planet and grains, so a different mechanism would be required to modulate the activity over these timescales.
 
-\citet{vanlieshout2016kic1255} compile the stellar parameters reported in the literature via photometric and spectroscopic methods and note that the high resolution spectrum show that \shStar\ has the gravity of a sub-giant, whereas all other methods find that it is a main sequence star.
+\citet{vanlieshout2016kic1255} compiled the stellar parameters reported in the literature via photometric and spectroscopic methods and note that the high resolution spectrum show that \shStar\ has the gravity of a sub-giant, whereas all other methods find that it is a main sequence star.
 One exciting possibility suggested in \citet{vanlieshout2016kic1255} is that the planet disintegration affects the spectral lines of the star and affects the high resolution spectrum from \citet{kawahara2013starspots}.

### 2018-07-21 ms.tex
some corrections from BG.

@@
 We observe 5 transits of the system with the 61-inch Kuiper telescope in 2016 and show that they are consistent with photometry from the \kepler\ spacecraft in 2009-2013.
-We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_{eff}$=4500 $\pm$110 K star.
+We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_{eff}$=4500 $\pm$110 K star in agreement with the photometry and low resolution spectroscopy.
 This disfavors the hypothesis that planet disintegration affected the analysis of prior high resolution spectra of this star.
@@
 The \kepler\ data was used to put constraints on the particle size distribution and composition of the dust particles.
-\citet{budaj12} and \citet{brogi2012} modeled the light curve, which includes a slight increase in flux prior before the transit begins.
+\citet{budaj12} and \citet{brogi2012} modeled the light curve, which includes a slight increase in flux before the transit begins.
 This pre-ingress flux increase is caused by forward scattering dust particles and the scattering function is sensitive to particle size modulo composition.
@@
 Thanks to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
-Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
+Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
 Thanks to Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star.

### 2018-07-24 ms.tex
updated the 2013 spectrum w/ better wavelength solution and corrected bin size in sec. eclipse caption.

@@
 Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths exoplanets of M stars, the ``transit source light effect.''
-For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can vary by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin Rackham, private communication, 2018}
+For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can vary by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
+Rackham, private communication, 2018}
 The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage.
@@
 This would enable compositional and kinematic studies of the disintegrating planet.
-In Section \ref{sec:SubaruDescrip}, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
+In Section \ref{sec:stellarCharacterization}, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
+We conclude in Section \ref{sec:conclusions}.
 
@@
 
-We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected at f$_p$/f$_*$ $\lesssim 50$~ppm, seen in Figure \ref{fig:secEclipse}, where f$_p$/f$_*$ is the relative flux of the planet to star in the Kepler bandpass.
+We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected at f$_p$/f$_*$ $\lesssim 50$~ppm, where f$_p$/f$_*$ is the relative flux of the planet to star in the Kepler bandpass, as seen in Figure \ref{fig:secEclipse}.
 We then use the secondary eclipses as a way to characterize the noise of the primary transits.
@@
 \caption{No secondary eclipse (f$_p$/f$_*$ $\lesssim$ 50 ppm) is detected from a phase range of 0.25 to 0.75, even with 17 quarters (4 years) of \kepler\ Long Cadence data.
-Here, the data are binned to orbital phases of 0.1 (1.5 minutes) and errors calculated from the standard error in the mean of the data within a bin.
+Here, the data are binned to orbital phases of 0.016 (15 minutes) and errors calculated from the standard error in the mean of the data within a bin.
 }\label{fig:secEclipse}
@@
 
-\section{Stellar Characterization}
+\section{Stellar Characterization}\label{sec:stellarCharacterization}
 \subsection{Previous Observations}
@@
 We performed wavelength calibration with a Thorium Argon reference spectrum.
-The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in the x direction and 4th order in the y direction.
-This polynomial fit has a RMS error of 0.02$\AA$.
+The final wavelength calibration fit was performed with a chebyshev polynomial, 5th order in the x direction and 3th order in the y direction.
+This polynomial fit has a RMS error of 0.002$\AA$.
 

### 2018-07-24 ms.tex
several clarifications, included to the PCA section.

@@
 The first 4 eigenvectors explain 62\%, 12\%, 6\% and 3\% of the variance (a total of 84\%) for the 32 points (variables) in the phase grid from -0.25 to 0.25.
-We also transform the eigenvectors into light curves by multiplying each eigenvector by the standard deviation of principal components and adding it to the average light curve.
+We also transform the eigenvectors into light curves by multiplying each eigenvector by the standard deviation of principal components and adding it to the average light curve, as shown in the right side of Figure \ref{fig:pcaVectorsComp}.
 
-The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering so that the light curve is dominated by the extinction \citep{budaj12}.
-We also note that the second eigenvector resembles models of large dust grains from \citet{budaj12}, where the forward scattering from particles that are a similar order of magnitude as the wavelength cause a pronounced pre-ingress flux increase.
+The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering so that the light curve is dominated by extinction \citep{budaj12,brogi2012}.
+We also note that the second eigenvector resembles models of large dust grains of pyroxene from \citet{budaj12}, where the particles that are a similar order of magnitude as the wavelength exhibit forward scattering, which causes a pronounced pre-ingress flux increase.
 The fact that the pre-ingress flux increase is not found in the first eigenvector and instead is pronounced in orthogonal eigenvectors suggests that the dust particle sizes may be changing in time.
-We would expect that a dust cloud that only varies in the number of particles but not in grain size would be exhibit a forward scattering in the first principal component because the forward scattering flux increase goes up with the number of particles.
-
+We would expect that a dust tail with a variable number of of particles but a constant grain size would be exhibit a forward scattering in the first principal component because the forward scattering flux would scale proportionally with the number of particles and transit depth.
 The implication of the PCA then is that the dust particle sizes may be changing with time.
@@
 The second principal component's periodogram has a strong peak at 491 days.
-This singly-peaked periodogram implies that PC$_2$ is nearly sinusoidal.
+This singly-peaked periodogram (other than the 0.654 day sampling period) implies that PC$_2$ is nearly sinusoidal.
 As shown in Figure \ref{fig:pcaVectorsComp}, the second principal component resembles models with larger dust grains, so the dust grain sizes could be evolving on long-term 491-day timescales.
@@
 There is one set of data taken on 2013 June 22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
-For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
+For these 2013 exposures, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
 Additionally, there are two sets of observations from 2015 Aug 28 (UT) and 2015 Aug 29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
@@
 None of the observations were timed during a primary transit (phase = 0.0) or secondary eclipse (phase = 0.5 for a circular orbit).
+Future high resolution spectroscopy at an orbital phase of 0.0 may be useful for searching for gaseous planetary debris.
 

### 2018-07-25 ms.tex
added the Ground-based time series to the Kepler amplitude + PC time series.

@@
 We also note that the second eigenvector resembles models of large dust grains of pyroxene from \citet{budaj12}, where the particles that are a similar order of magnitude as the wavelength exhibit forward scattering, which causes a pronounced pre-ingress flux increase.
+The second eigenvector has a broader forward scattering peak than the \citet{budaj12} models, so it may be the result of a broader distribution of particles.
 The fact that the pre-ingress flux increase is not found in the first eigenvector and instead is pronounced in orthogonal eigenvectors suggests that the dust particle sizes may be changing in time.
@@
 \caption{Time series of the transit amplitude and principals components.
-The amplitude is found with a dot product with the average light curve.
+The amplitude is found with a dot product with the average light curve for the Kepler data (left 3 panels) and with a scaled model for the ground-based data (right plot).
 Quiescent intervals with low transit activity are identified from the amplitude.
+The first principal component tracks closely with the amplitude.
 The second principal component shows periodicity at 491 days, indicating possible long-term evolution of dust grain particle sizes.}\label{fig:tserPC}

### 2018-07-27 ms.tex
correctly accounted for all barycentric and systematic velocity offsets in all plots.

@@
 There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the \kepler\ bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
-A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$ (determined by the mass of dust needed to absorb and scatter 10$^{-2}$ of star light per orbit), the modeled mass is 0.014 $M_\oplus$ \citep{perez-becker}.
+A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$ (determined by the mass of dust needed to absorb and scatter 10$^{-2}$ of star light per orbit), the modeled mass is 0.014~$M_\oplus$ \citep{perez-becker}.
 
@@
 All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
+The wavelength of each spectrum is shifted to correct for the observatory's motion about the Solar Systems barycenter as well as the systematic -36.3 km/s velocity \citep{croll2014}.
 We combined the normalized spectra from UT dates 2015 Aug 28 and 2015 Aug 29 with a median in the time direction, which is more robust to cosmic rays than an average.

### 2018-07-30 ms.tex
tiny clarification on future high res transit observations.
a few clarifications to abstract and intro.

@@
 \section{Introduction}\label{sec:Intro}
-\citet{rappaport} first reported the discovery of a highly unusual stellar system in the \kepler\ field.
-KIC 12557548's light curve exhibits flux dips with a period of 0.653 days.
+\citet{rappaport} first reported the discovery of a highly unusual system in the \kepler\ field, KIC 12557548.
+Its light curve exhibits flux dips with a period of 0.653 days.
 Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$0\% to $\sim$1.2\%.
@@
 This is radially different from a transiting planet, where the planet absorbs the same amount of light from the star each orbit and does so symmetrically about the star, modulo stellar inhomogenities.
-The time variability of the flux dips indicates that material with a projected area $\sim$1\% of the stellar surface is created and cleared in $\lesssim$ 1 day timescales in order to extinct $\sim$1.2\% of starlight at one epoch and $\sim$0\% at another.
+The time variability of the flux dips indicates that material with a projected area $\sim$1\% of the stellar surface is created and cleared in $\lesssim$ 1 day timescales in order to extinct $\sim$1\% of starlight at one epoch and $\sim$0\% at another.
 These unusual light curve behaviors are best explained as dust extinction from a comet-like tail of material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
@@
 Rackham, private communication, 2018}
-The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage.
+The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
 
@@
 None of the observations were timed during a primary transit (phase = 0.0) or secondary eclipse (phase = 0.5 for a circular orbit).
-Future high resolution spectroscopy at an orbital phase of 0.0 may be useful for searching for gaseous planetary debris.
+Future high resolution spectroscopy at an orbital phase of 0.0 may be useful for searching for gaseous planetary debris in absorption against the star.
 

### 2018-07-30 ms.tex
This is draft 7 that I'm sending out before submitting. Corrected some typos and wording after an out-loud read through.

@@
 We observe 5 transits of the system with the 61-inch Kuiper telescope in 2016 and show that they are consistent with photometry from the \kepler\ spacecraft in 2009-2013.
-We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_{eff}$=4500 $\pm$110 K star in agreement with the photometry and low resolution spectroscopy.
+We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_{eff}$=4440 $\pm$70 K star in agreement with the photometry and low resolution spectroscopy.
 This disfavors the hypothesis that planet disintegration affected the analysis of prior high resolution spectra of this star.
@@
 
-The \kepler\ spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
+The \kepler\ spacecraft performed near-continuous long cadence photometry of KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
 During this time, the transit depths averaged around $\sim$0.6\% but varied stochastically from just one 15.7 hour orbit to the next.
@@
 Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths exoplanets of M stars, the ``transit source light effect.''
-For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can vary by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
+For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
 Rackham, private communication, 2018}
@@
 \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
-The SpeX/IRTF spectrum, though affected by systematic noise, confirmed the \citet{croll2014} result that particle sizes are $\gtrsim 0.5\%$ for a pyroxene composition.
+The SpeX/IRTF spectrum, though affected by systematic noise, confirmed the \citet{croll2014} result that particle sizes are $\gtrsim 0.5$~$\mu$m for a pyroxene composition.
 \citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probability of this randomly occurring based on random behavior from \kepler\ statistics was around 0.2\%.
@@
 We performed follow-up $R$ band photometry of the \shStar\ system to explore these two hypotheses and see if the the disintegration has returned to the levels found in the \kepler\ mission and discuss this in Section \ref{sec:photObs}.
-We also re-analyze the \kepler\ photometry in order to quantify the light curve behavior in Section \ref{sec:Kepler}.
+We also re-analyzed the \kepler\ photometry in order to quantify the light curve behavior in comparison to ground-based photometry in Section \ref{sec:Kepler}.
 
-The high resolution spectrum of \shStar\ \citep{kawahara2013starspots} showed a different temperature and gravity than photometric methods \cite[e.g.][]{brown2011kic}.
+The high resolution spectrum of \shStar\ \citep{kawahara2013starspots} showed a different temperature and gravity than photometric methods \cite[e.g.][]{brown2011kic,huber2014kicprop}.
 \citet{vanlieshout2016kic1255} suggest that one exciting possibility is that gases from the disintegrating planet contaminate the high resolution spectrum.
@@
 \section{Photometric Observations}\label{sec:photObs}
-We attempted to observe 6 transit events of \sha\ with the Mont4k imager on the 61-inch Kuiper telescope located on Mt Bigelow, Arizona on UT using the f/13.5 Cassegrain focus.
+We attempted to observe 6 transit events of \sha\ with the Mont4k imager on the 61-inch Kuiper telescope located on Mt Bigelow, Arizona in 2016 using the f/13.5 Cassegrain focus.
 On all nights we used 90 second exposures using a Harris-R filter to best approximate the $r'$ filter used in \citet{schlawin2016kic1255}.
 5 of the 6 nights were clear with the exception of a few passing clouds on UT 2016 Jul 14.
-Cloudy skies on UT 2016 Jun 10 that prevented high precision time series.
+Cloudy skies on UT 2016 Jun 10 prevented high precision time series.
 Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
@@
 where $T_0 = 2 454 968.982 0 \pm 0.000 7$ BJD$_{TDB}$ and $P = 0.653 553 4 \pm 0.000 000 2$ days.
-The expected transit epochs from the ephemeris in \citep{vanWerkhoven2014} are shown for reference as vertical red bars.
+The expected transit epochs from this ephemeris are shown for reference as vertical red bars.
 Typical uncertainties for the \kepler\ ephemeris are $\sim$ 1 minute at these dates due to the large number of transits measured by the \kepler\ observatory over nearly 4 years.
@@
 \includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
-\caption{Reference-corrected time series photometry \shStar\ for all nights (blue circles).
+\caption{Reference-corrected time series photometry of \shStar\ for all nights (blue circles).
 Orange squares mark 20 minute flux bins for visual clarity.
-The expected transit epochs from the \kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
+The expected transit epochs from the \kepler-based ephemeris \citep{croll2015starspots} are shown as vertical red bars.
 We also fit each light curve with a model that scales the average \kepler\ short cadence data (Equation \ref{eq:transFitting}) shown in green.
@@
 \caption{Cleaned \kepler\ Long-cadence data (Left) and model fit using the average light curve (Middle).
-(Right) The residuals show significant deviations near phases of -0.05 and 0.05.
+The residuals (Right) show significant deviations near phases of -0.05 and 0.05.
 }\label{fig:riverPlots}
@@
 \caption{Cleaned \kepler\ Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
-The residuals (Right) are $\lesssim 0.1\%$, significantly smaller than the $\sim 0.2\%$ residuals when using the average-light curve method shown in Figure \ref{fig:riverPlots}.
+The residuals are $\lesssim 0.1\%$ (Right), significantly smaller than the $\sim 0.2\%$ residuals when using the average-light curve method shown in Figure \ref{fig:riverPlots}.
 }\label{fig:riverPlotsPCA}
@@
 \includegraphics[width=0.99\textwidth]{images/kepler/pc_tser_w_quiescent.pdf}
-\caption{Time series of the transit amplitude and principals components.
-The amplitude is found with a dot product with the average light curve for the Kepler data (left 3 panels) and with a scaled model for the ground-based data (right plot).
+\caption{Time series of the transit amplitude and principals components of the Kepler data (Left panel).
+We also show the ground-based photometry from \citet{schlawin2016kic1255} and this work (Right upper plot).
 Quiescent intervals with low transit activity are identified from the amplitude.
@@
 In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
-The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the the sampling cadence of the time series of amplitudes and principal components.
+The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the sampling cadence of the time series of amplitudes and principal components.
 The first component, corresponding to the transit depth, has peaks at 22.9, 153 and 750 days.
@@
 This is much longer than the dynamical and sublimation times of the system, so there is no obvious mechanism for the dust grain size evolution.
+It is also possible that red noise such as 1/$f$ noise contributes to these long term oscillations.
 
@@
 We take the histogram of transit amplitudes as measured by the \kepler\ light curves (shown in Figure \ref{fig:histoPhot}) and compare these to the ground-based photometry from \citet{schlawin2016kic1255} and this work.
-The histogram of secondary eclipse amplitudes from the \kepler\ light curves is also shown in Figure \ref{fig:histoPhot}, which shows the spread due to photon noise.
+The histogram of secondary eclipse amplitudes from the \kepler\ light curves is also plotted in Figure \ref{fig:histoPhot}, which shows the spread due to photon noise.
 The intrinsic astrophysical variation of the planet disintegration is convolved by this photometric scatter in the data.
@@
 \includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
-\caption{Normalized frequency of 4 different transit amplitude distributions: 1) all of the \kepler\ Long Cadence data from 2009 to 2013, 2) the secondary eclipse amplitudes from the \kepler\ spacecraft over this same period, 3) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper telescope campaign in the summer of 2016.
+\caption{Normalized frequency of 4 different amplitude distributions: 1) all of the \kepler\ Long Cadence data during transit from 2009 to 2013, 2) the secondary eclipse amplitudes from the \kepler\ spacecraft over this same period, 3) the 8 night ground-based IRTF transit campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper telescope transit campaign in the summer of 2016.
 The \citet{schlawin2016kic1255} (S16) events give a KS-test $p$ value of 0.001 when comparing to the \kepler\ data.
@@
   \citet{vanlieshout2016kic1255} & 		& $\gtrsim 4.4$	& main-sequence star	& transit light curve \\
-  This work - Specmatch	& 4500 $\pm$110 	& 4.63 $\pm$ 0.1 & main-sequence star & high-resolution spectroscopy\\
+  This work - Specmatch	& 4440 $\pm$70 	& 4.63 $\pm$ 0.12 & main-sequence star & high-resolution spectroscopy\\
   This work - BOSZ		& 4500	& 4.5		& main-sequence star & high-resolution spectroscopy\\
 \enddata
-\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
+\tablenotetext{}{While photometry and low-resolution spectroscopy indicated surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicated a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
 \end{deluxetable*}
@@
 
-We evaluate the stellar parameters by examining the archival spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
+We evaluate the stellar parameters by examining the archival spectra taken with the High Definition Spectrograph (HDS) on the Subaru telescope \citep{noguchi2002hds}.
 An observing log of the 3 nights is summarized in Table \ref{tab:specObs}.
@@
 We first evaluate stellar parameters by comparing the high resolving power ($R=100,000$) BOSZ grids of ATLAS-APOGEE ATLAS9 models \citep{bohlin2017bosz} to the median spectrum from 2015.
-Since the discrepancies in the literature are mostly differences in the surface gravity (see Table \ref{tab:stellObsParams}), we study the gravity-sensitive Mg triplet near 517 nm.
+Because the discrepancies in the literature are mostly differences in the surface gravity (see Table \ref{tab:stellObsParams}), we study the gravity-sensitive Mg triplet near 517 nm.
 The $R=100,000$ models are convolved with a Gaussian kernel that has a standard deviation $\sigma_K = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
@@
 
-%A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.
-
 After initial constraints on the models from the sensitivity to parameters search, we downloaded a grid of BOSZ models with effective temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
-We found the model with the  $\chi^2$ statistic over the Mg triple lines from 5160 to 5190 $\AA$
-As discussed above, we use an approximate $\chi^2$ statistic over the wavelength range covering the Mg triplet (5160 $\AA$ to 5190 $\AA$).
-The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T$_{eff}$=4500 K, Log(g)=4.5, M/H=0.0, C/M=0.0, $\alpha=-0.25$.
+We found the model with the  $\chi^2$ statistic over the Mg I triplet lines from 5160 to 5190 $\AA$
+The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T$_{eff}$=4500 K, Log(g)=4.5, [M/H]=0.0, [C/M]=0.0, $\alpha=-0.25$.
 This is similar to the log(g)$\approx$4.6, T$_{eff}$=4500 stellar parameters derived from photometry and low resolution spectroscopy listed in Table \ref{tab:stellObsParams}.
@@
 \texttt{SpecMatch-Emp} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
-%The median spectrum from 2015 has a resolution of $R=60,000$, which is close to the \texttt{SpecMatch-Emp} grid of $R=55,000$, so we do not convolve the input data for \texttt{SpecMatch-Emp}.
-We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.
+We cut the default HIRES library and Subaru spectra to the wavelengths from 5000~$\AA$ to 5900~$\AA$, which includes the gravity-sensitive Mg I triplet.
 
@@
 However, the metallicity is less well constrained.
-The resulting best-fit parameters from \texttt{SpecMatch-Emp} are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$ and Mass=0.7 $\pm 0.1 $M$_\odot$.
-Figure \ref{fig:SpecMatch-EmpComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{SpecMatch-Emp}.
+The resulting best-fit parameters from \texttt{SpecMatch-Emp} are T$_{eff}$=4440 K $\pm$ 70 K, [Fe/H]=-0.08$\pm$0.09, log(g)=4.63$\pm$0.12, R=0.69 $\pm$ 0.10 R$_\odot$ and Mass=0.70 $\pm 0.08~$M$_\odot$.
+Figure \ref{fig:SpecMatch-EmpComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{SpecMatch-Emp} over a subset of the wavelengths near the Mg I triplet.
 
@@
 \includegraphics[width=0.8\textwidth]{images/subaru/lincomb_kic1255.pdf}
-\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:SpecMatch-EmpComb}
+\caption{Linear combination of templates that best matches KIC 1255 near the Mg I triplet.}\label{fig:SpecMatch-EmpComb}
 \end{centering}
@@
 We explore this possibility by examining archival Subaru HDS spectra of \shStar.
-We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4500 $\pm$ 110 K, log(g) = 4.5, [Fe/H]=-0.1$\pm$0.1, M=0.7$\pm$0.1 R$_\odot$ and M=0.7 $\pm$0.1 M$_\odot$.
+We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, M=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
 Therefore, the optical depth of any gas sublimating of dust grains is too small to affect the high resolution spectrum.
@@
 %MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
-Thanks to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
+The authors thank to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
 Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
-Thanks to Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star.
+The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.
 

### 2018-08-01 ms.tex
added reference to ridden-harper paper.
moved all figures to base directory in order to submit to aas journals.

@@
 \citet{croll2014} find a particle size distribution of $\gtrsim 0.5\mu$m.
+Recent modeling by \citet{ridden-harper2018chromaticKIC1255} shows that the wavelength-dependent extinction function could be due to the tail's changing optical thickness.
 
@@
 \begin{centering}
-\includegraphics[width=0.49\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
-\includegraphics[width=0.49\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
+\includegraphics[width=0.49\textwidth]{figure_index_152.pdf}
+\includegraphics[width=0.49\textwidth]{stamps_kic1255_UT2016_07_14.pdf}
 \caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of Mont4K.
@@
 \begin{centering}
-\includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
+\includegraphics[width=0.8\textwidth]{all_kic1255_allstar.pdf}
 \caption{Time series photometry for all stars and all nights.
@@
 \begin{centering}
-\includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
+\includegraphics[width=0.8\textwidth]{all_kic1255_refcor.pdf}
 \caption{Reference-corrected time series photometry of \shStar\ for all nights (blue circles).
@@
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
+\includegraphics[width=0.45\textwidth]{secondary_eclipse.pdf}
 \caption{No secondary eclipse (f$_p$/f$_*$ $\lesssim$ 50 ppm) is detected from a phase range of 0.25 to 0.75, even with 17 quarters (4 years) of \kepler\ Long Cadence data.
@@
 \begin{centering}
-\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{photometry_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{model_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{residual_riverplot.pdf}
 \caption{Cleaned \kepler\ Long-cadence data (Left) and model fit using the average light curve (Middle).
@@
 \begin{centering}
-\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
-\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
+\includegraphics[width=0.32\textwidth]{photometry_riverplot.pdf}
+\includegraphics[width=0.32\textwidth]{pca_model_2D.pdf}
+\includegraphics[width=0.32\textwidth]{pca_resid_2D.pdf}
 \caption{Cleaned \kepler\ Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
@@
 \begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255_transformed.pdf}
+\includegraphics[width=0.49\textwidth]{pca_k1255.pdf}
+\includegraphics[width=0.49\textwidth]{pca_k1255_transformed.pdf}
 \caption{The principal component eigenvectors scaled by their eigenvalues (Left), shows that the first eigenvector largely describes the extinction while the second shows the contributions from forward scattering.
@@
 \begin{centering}
-\includegraphics[width=0.99\textwidth]{images/kepler/pc_tser_w_quiescent.pdf}
+\includegraphics[width=0.99\textwidth]{pc_tser_w_quiescent.pdf}
 \caption{Time series of the transit amplitude and principals components of the Kepler data (Left panel).
@@
 \begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/pc1_periodogram.pdf}
-\includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
+\includegraphics[width=0.49\textwidth]{pc1_periodogram.pdf}
+\includegraphics[width=0.49\textwidth]{pc2_periodogram.pdf}
 \caption{Periodograms of the principal component time series shown in Figure \ref{fig:tserPC}, with peaks marked with red circles.
@@
 \end{figure*}
-
-%\begin{figure*}[!hbtp]
-%\begin{centering}
-%\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
-%\caption{(Left) Histogram of transit amplitudes.
-%An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
-%A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical photon noise that explains shy some transit depths appear less than 0.
-%}\label{fig:histograms}
-%\end{centering}
-%\end{figure*}
 
@@
 \begin{centering}
-\includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
+\includegraphics[width=0.49\textwidth]{amp_distributions_comparison.pdf}
 \caption{Normalized frequency of 4 different amplitude distributions: 1) all of the \kepler\ Long Cadence data during transit from 2009 to 2013, 2) the secondary eclipse amplitudes from the \kepler\ spacecraft over this same period, 3) the 8 night ground-based IRTF transit campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper telescope transit campaign in the summer of 2016.
@@
 \begin{centering}
-\includegraphics[width=1.0\textwidth]{images/subaru/2013_vs_2015/2013_vs_2015_spec.pdf}
+\includegraphics[width=1.0\textwidth]{2013_vs_2015_spec.pdf}
 \caption{Comparison between the 2013 spectrum and 2015 median spectrum of \shStar\ near the Mg I triplet. The two are consistent within the larger noise of the 2013 data.}\label{fig:spec2013vs2015}
@@
 \begin{centering}
-\includegraphics[width=0.85\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
+\includegraphics[width=0.85\textwidth]{bosz_mg_triplet_median_spec_w_5000.pdf}
 \caption{Median spectrum of \shStar\ \citep{masuda2018rvKIC1255} near the Mg triplet (green) compared to 4500 K BOSZ models with two different log(g)s (blue and orange).
@@
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/T_EFF_exploration.pdf}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/LOGG_exploration}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/MH_exploration.pdf}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/ALPHA_exploration.pdf}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/CM_exploration.pdf}
-\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/FINAL_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{T_EFF_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{LOGG_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{MH_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{ALPHA_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{CM_exploration.pdf}
+\includegraphics[width=0.45\textwidth]{FINAL_exploration.pdf}
 \caption{The BOSZ models are explored over the parameter space to search for a best fit as well as visualize how much each parameter affects the spectrum.
@@
 \begin{centering}
-\includegraphics[width=0.8\textwidth]{images/subaru/spec_chi_min.pdf}
+\includegraphics[width=0.8\textwidth]{spec_chi_min.pdf}
 \caption{$\chi^2$ as a function of stellar parameters found by \texttt{SpecMatch-Emp}.
@@
 \begin{centering}
-\includegraphics[width=0.8\textwidth]{images/subaru/lincomb_kic1255.pdf}
+\includegraphics[width=0.8\textwidth]{lincomb_kic1255.pdf}
 \caption{Linear combination of templates that best matches KIC 1255 near the Mg I triplet.}\label{fig:SpecMatch-EmpComb}
@@
 We therefore conclude that the noise in the spectrum affected the stellar parameters rather than gas absorption from sublimating dust grains.
-
-%\begin{figure*}[!hbtp]
-%\begin{centering}
-%\includegraphics[width=0.99\textwidth]{images/kepler/phase_shifts.pdf}
-%\caption{Time Series of phase shifts.}\label{fig:phaseShift}
-%\end{centering}
-%\end{figure*}
-%
-%
-%\begin{figure*}[!hbtp]
-%\begin{centering}
-%\includegraphics[width=0.49\textwidth]{images/kepler/phase_shift_vs_amplitude.pdf}
-%\includegraphics[width=0.49\textwidth]{images/kepler/phase_shifts_periodogram.pdf}
-%\caption{Phase shifts versus amplitude (left) and phase shift periodogram (right).}\label{fig:phaseShift}
-%\end{centering}
-%\end{figure*}
 

### 2018-09-14 ms.tex
Started editing after the referee report from the first submission. I started making some tiny tweaks on the minor points.

@@
 
-\title{Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b}
+\title{Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}}
 
@@
 We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, M=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
-Therefore, the optical depth of any gas sublimating of dust grains is too small to affect the high resolution spectrum.
+Therefore, the optical depth of any gas sublimating off dust grains is too small to affect the high resolution spectrum.
 We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.

### 2018-09-14 ms.tex
clarified the optical depth in the high res spectrum and also turned on track changes.

@@
 %\documentclass[12pt,preprint]{aastex}
-\documentclass[preprint]{aastex61}
+\documentclass[preprint,trackchanges]{aastex61}
 %\documentclass[iop]{emulateapj}
@@
 We summarize these \texttt{SpecMatch-Emp} and BOSZ results in Table \ref{tab:stellObsParams}, which both favor a main-sequence log(g) $\approx$ 4.6 star.
-Our analysis of the median 2015 spectrum therefore indicates that the stellar spectrum shows no strong contamination from planet disintegration activity.
+Our analysis of the median 2015 spectrum therefore indicates that the stellar spectrum shows no strong contamination from planet disintegration activity \added{at the level where it would affect the derived stellar parameters}.
 Unfortunately, this makes diagnosing the gaseous material evaporating from sublimated dust grains challenging to detect.
@@
 We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, M=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
-Therefore, the optical depth of any gas sublimating off dust grains is too small to affect the high resolution spectrum.
+Therefore, the optical depth of any gas sublimating \replaced{of}{off} dust grains is too small to affect \added{the parameters derived from} the high resolution spectrum.
 We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.

### 2018-09-15 ms.tex
a few more minor comments from referee.

@@
 \begin{abstract}
-KIC 12557548 b is first of a growing class of intriguing disintegrating planet candidates, which lose mass in the form of dust particles escaping their surface.
+KIC 12557548 b is first of a growing class of intriguing disintegrating planet candidates, which lose mass in the form of \added{a metal rich vapor that condenses into} dust particles escaping their surface.
 Here, we follow up two perplexing observations of the system: 1) the transits appeared shallower than average in 2013 and 2014 and 2) the parameters derived from a high resolution spectrum of the star differed from other results using photometry and low resolution spectroscopy.
@@
 
-After the discovery of K1255, other systems were found to show similar light curve behavior: K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} and KIC 3542116 \citep{rappaport2018exocomets}.
+After the discovery of K1255, other systems were found to show similar light curve behavior: K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating} \replaced{,}{and} KOI 2700 \citep{rappaport2014KOI2700} \deleted{and KIC 3542116 \citep{rappaport2018exocomets}}.
 A collection, albeit small, of several different disintegrating planet systems makes for a useful laboratory for understanding planet evolution and composition.
@@
 KIC 8462852 may be a family of comets from one or more parent bodies that recently broke apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
+\added{Similarly, a new system (KIC 3542116) has been discovered that has a light curve explained by extrasolar comets that produce transits in the broadband optical  \citep{rappaport2018exocomets}.}
 RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr, respectively), so they may be proto-planet candidates or structures within a protoplanetary disk \citep{stauffer2017orbitingClouds,yu2015ptfO8d8695PlanetHypothesisTest}.
@@
 
+\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data}.
+
 \section{Conclusions}\label{sec:conclusions}

### 2018-09-16 ms.tex
adjusted the periodograms to only show periods greater than 2X the sampling rate and removed associated text about the P=0.65 sampling.

@@
 KIC 8462852 may be a family of comets from one or more parent bodies that recently broke apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
-\added{Similarly, a new system (KIC 3542116) has been discovered that has a light curve explained by extrasolar comets that produce transits in the broadband optical  \citep{rappaport2018exocomets}.}
+\added{Similarly, a new system (KIC 3542116) has been discovered that has a light curve explained by extrasolar comets that produce transits in broadband optical light \citep{rappaport2018exocomets}.}
 RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr, respectively), so they may be proto-planet candidates or structures within a protoplanetary disk \citep{stauffer2017orbitingClouds,yu2015ptfO8d8695PlanetHypothesisTest}.
@@
 In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
-The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the sampling cadence of the time series of amplitudes and principal components.
+\deleted{The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the sampling cadence of the time series of amplitudes and principal components.}
 The first component, corresponding to the transit depth, has peaks at 22.9, 153 and 750 days.
@@
 The second principal component's periodogram has a strong peak at 491 days.
-This singly-peaked periodogram (other than the 0.654 day sampling period) implies that PC$_2$ is nearly sinusoidal.
+This singly-peaked periodogram \deleted{(other than the 0.654 day sampling period)} implies that PC$_2$ is nearly sinusoidal.
 As shown in Figure \ref{fig:pcaVectorsComp}, the second principal component resembles models with larger dust grains, so the dust grain sizes could be evolving on long-term 491-day timescales.
@@
 \caption{Periodograms of the principal component time series shown in Figure \ref{fig:tserPC}, with peaks marked with red circles.
-The first peak at 0.654 days for both principal components is the orbital period, which is the sampling cadence of the principal components' time series.
-PC$_1$ also peaks at 22.9, 153 and 750 days.
+\deleted{The first peak at 0.654 days for both principal components is the orbital period, which is the sampling cadence of the principal components' time series.}
+PC$_1$ \deleted{also} peaks at 22.9, 153 and 750 days.
 The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.
-The second principal components shows one dominant peak at 491 days, in addition to the 0.654 orbital period, indicating possible long term evolution of the dust particle sizes.}\label{fig:ampPeriodogram}
+The second principal components shows one dominant peak at 491 days, \deleted{in addition to the 0.654 orbital period,} indicating possible long term evolution of the dust particle sizes.}\label{fig:ampPeriodogram}
 \end{centering}

### 2018-09-19 ms.tex
added a few statements about the line spread function and convolution.

@@
 The $R=100,000$ models are convolved with a Gaussian kernel that has a standard deviation $\sigma_K = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
-This was smaller than we expected from combining inverse resolving powers in quadrature, which would imply that an $R=75,000 $ kernel convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
+This was \replaced{smaller}{broader} than we expected from combining inverse resolving powers in quadrature, which would imply that an $R=75,000 $ kernel \added{$\sigma_\mathrm{expected} = 1/176,610$} convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
+\added{This is likely because of the non-Gaussian nature of the Subaru line spread function.}
 We start by comparing the measured spectrum with two BOSZ models in Figure \ref{fig:mgTripletBOSZ}.

### 2018-09-19 ms.tex
a short adjustment about the Gaussian kernel (sigma versus FWHM).

--- 2018-09-16 ms.tex
@@
 The $R=100,000$ models are convolved with a Gaussian kernel that has a standard deviation $\sigma_K = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
-This was smaller than we expected from combining inverse resolving powers in quadrature, which would imply that an $R=75,000 $ kernel convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
+This was \replaced{smaller}{slightly broader} than we expected from combining inverse resolving powers in quadrature, which would imply that an \replaced{$R=75,000$}{$R_{expected} = 75,000$} kernel \added{($\sigma_{expected} = \lambda/176,600$)} convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
+\added{We suspect that the non-Gaussian shape of the line spread function is the cause of this discrepancy.}
 We start by comparing the measured spectrum with two BOSZ models in Figure \ref{fig:mgTripletBOSZ}.

### 2018-09-19 ms.tex

@@
 \added{We suspect that the non-Gaussian shape of the line spread function is the cause of this discrepancy.}
+
 We start by comparing the measured spectrum with two BOSZ models in Figure \ref{fig:mgTripletBOSZ}.

### 2018-09-20 ms.tex
added typical error bars to time series.

@@
 We also show the ground-based photometry from \citet{schlawin2016kic1255} and this work (Right upper plot).
-Quiescent intervals with low transit activity are identified from the amplitude.
+Quiescent intervals with low transit activity are identified from the amplitude \added{and highlighted in orange. 
+Typical (median) error bars for the time series are shown as red error bars at arbitrary positions.}
 The first principal component tracks closely with the amplitude.
-The second principal component shows periodicity at 491 days, indicating possible long-term evolution of dust grain particle sizes.}\label{fig:tserPC}
+The second principal component shows periodicity at 491 days, indicating possible long-term evolution of dust grain particle sizes.
+}\label{fig:tserPC}
 \end{centering}

### 2018-09-20 ms.tex
put in typical error bars for Kepler too.

@@
 \includegraphics[width=0.99\textwidth]{pc_tser_w_quiescent.pdf}
-\caption{Time series of the transit amplitude and principals components of the Kepler data (Left panel).
+\caption{Time series of the transit amplitude and principals components of the \replaced{Kepler}{{\it Kepler}} data (Left panel).
 We also show the ground-based photometry from \citet{schlawin2016kic1255} and this work (Right upper plot).
 Quiescent intervals with low transit activity are identified from the amplitude \added{and highlighted in orange. 
-Typical (median) error bars for the time series are shown as red error bars at arbitrary positions.}
+Typical (median) error bars for the time series are shown as red error bars at arbitrary vertical positions.}
 The first principal component tracks closely with the amplitude.

### 2018-09-21 ms.tex
started moving the stellar activity discussion to a new section.

--- 2018-09-20 ms.tex
@@
 The anti-correlation between stellar flux and transit depth was confirmed by \citet{croll2015starspots}, though the authors find that occultations of star spots can also modulate the transit depth at the 22.9 day rotation period of the star.
-Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths exoplanets of M stars, the ``transit source light effect.''
-For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
+\added{We will revisit stellar activity in Section \ref{sec:activity}.}
+\deleted{Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths exoplanets of M stars, the ``transit source light effect.''
+For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.%\footnote{Benjamin V.
 Rackham, private communication, 2018}
-The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
+The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.}
 
@@
 In Section \ref{sec:stellarCharacterization}, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
+\added{In Section \ref{sec:activity}, we examine the activity of the star from the H$\alpha$ line and also discuss how starspots can affect the light curves.}
 We conclude in Section \ref{sec:conclusions}.
@@
 \includegraphics[width=0.99\textwidth]{pc_tser_w_quiescent.pdf}
-\caption{Time series of the transit amplitude and principals components of the Kepler data (Left panel).
+\caption{Time series of the transit amplitude and principals components of the \replaced{Kepler}{{\it Kepler}} data (Left panel).
 We also show the ground-based photometry from \citet{schlawin2016kic1255} and this work (Right upper plot).
@@
 \added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data}.
+
+\added{
+\section{Stellar Activity}\label{sec:activity}
+Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
+For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
+Rackham, private communication, 2018}
+The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
+}
 

### 2018-09-21 ms.tex
added a plot to show H-alpha line w/ Subaru."

@@
 \section{Stellar Activity}\label{sec:activity}
+
+The high resolution spectrum of \shStar\ allows us to measure the H$\alpha$ line, which is an indicator of stellar activity.
+Figure \ref{fig:Halpha}, shows the Subaru HDS spectrum for
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.8\textwidth]{h_alpha_subaru.pdf}
+\caption{H$\alpha$ line as measured by Subaru HDS on two adjacent nights in 2015.
+The line's core changes noticeably between the two nights.}\label{fig:Halpha}
+\end{centering}
+\end{figure*}
+
 Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.

### 2018-09-22 ms.tex
more on stellar activity and spots.

@@
 
-Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
+As discussed in Section \ref{sec:intro}, \citet{kawahara2013starspots} first noted an anti-correlation between the transit depths of \sha\ and the flux of its host star.
+This correlation implies that the planet disintegration is regulated by the high energy radiation or magnetic energy associated with star spots and that the planet's passage over the spot can increase the disintegration activity.
+\citet{croll2015starspots} confirm this anti-correlation but offer a different explanation: occulted dark spots on the stellar surface can decrease the transit depth because the planetary debris extincts less total starlight.
+If there is a localized grouping of spots that the planet's transit chord passes through, this could create a positive correlation of transit depth with stellar flux.
+\citet{croll2015starspots} note that the spots could have a complicated distribution and that a separate set of spots on the other side of the star could dominate the overall light curve rotational modulation but be at a different latitude from the transit chord, thus creating an anti-correlation between transit depth and stellar flux.
+\citet{croll2015starspots} calculate that unocculted spots
+
+Recently, \citet{rackham2018transitSourceEffect} have studied, in detail, the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
+One commonly held assumption is that there is a linear relation between the amplitude of variability and the spot covering fraction.
+Instead, \citet{rackham2018transitSourceEffect} use more realistic simulations of spot covering and light curve modulations and find that the amplitude of variability is proportional to $\sqrt{f_S}$, where $f_S$ is the spot covering fraction.
+
 For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
@@
 The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
+Also, the bias in transit depth is different from the transit depth variations, which would be un-affacted by a polar spot.
+Therefore, the conclusion from \citet{croll2015starspots} that unocculted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
 }

### 2018-09-23 ms.tex
added Gaia DR2 calculation.

@@
 
-\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data}.
+\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data.
+The GAIA DR2 parallax of 618 $\pm$ 12 pc can be used with the bolometric flux and effective temperature to estimate the stellar radius \citep[e.g.][]{stassun2017gaiaRadiiMasses}.
+We estimate a radius of 0.7 R$_\odot$, which is consistent with a main-sequence star.
+}.
 

### 2018-09-23 ms.tex
added a placeholder note about the WISE band 4 flux excess.

@@
 We estimate a radius of 0.7 R$_\odot$, which is consistent with a main-sequence star.
+
+While examining the bolometric flux from all available data, we notice that the WISE band 4 flux is in excess of a \citet{castelli2004models} stellar model.
+This is also true of the disintegrating system K2-22 b.
+These infrared fluxes may arise from dust created by the disintegrating planet and pushed out to a larger radius to form a disk or ring.
 }.

### 2018-09-25 sync_bib.sh
updated the sync bib path.

@@ -1,0 +1,1 @@
+cp /Users/everettschlawin/IDrive-Sync/evmemo_folder/pdfs/master_bib_file/master_biblio.bib ms.bib

### 2018-09-25 ms.tex
more on Gaia DR2 result.

--- 2018-09-22 ms.tex
@@
 The anti-correlation between stellar flux and transit depth was confirmed by \citet{croll2015starspots}, though the authors find that occultations of star spots can also modulate the transit depth at the 22.9 day rotation period of the star.
-\added{We will revisit stellar activity in Section \ref{sec:activity}.}
-\deleted{Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths exoplanets of M stars, the ``transit source light effect.''
-For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.%\footnote{Benjamin V.
+Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths exoplanets of M stars, the ``transit source light effect.''
+For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
 Rackham, private communication, 2018}
-The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.}
+The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
 
@@
 In Section \ref{sec:stellarCharacterization}, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
-\added{In Section \ref{sec:activity}, we examine the activity of the star from the H$\alpha$ line and also discuss how starspots can affect the light curves.}
 We conclude in Section \ref{sec:conclusions}.
@@
 \includegraphics[width=0.99\textwidth]{pc_tser_w_quiescent.pdf}
-\caption{Time series of the transit amplitude and principals components of the \replaced{Kepler}{{\it Kepler}} data (Left panel).
+\caption{Time series of the transit amplitude and principals components of the Kepler data (Left panel).
 We also show the ground-based photometry from \citet{schlawin2016kic1255} and this work (Right upper plot).
-Quiescent intervals with low transit activity are identified from the amplitude \added{and highlighted in orange. 
-Typical (median) error bars for the time series are shown as red error bars at arbitrary positions.}
+Quiescent intervals with low transit activity are identified from the amplitude.
 The first principal component tracks closely with the amplitude.
-The second principal component shows periodicity at 491 days, indicating possible long-term evolution of dust grain particle sizes.
-}\label{fig:tserPC}
+The second principal component shows periodicity at 491 days, indicating possible long-term evolution of dust grain particle sizes.}\label{fig:tserPC}
 \end{centering}
@@
 
-\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data}.
-
-\added{
-\section{Stellar Activity}\label{sec:activity}
-
-The high resolution spectrum of \shStar\ allows us to measure the H$\alpha$ line, which is an indicator of stellar activity.
-Figure \ref{fig:Halpha}, shows the Subaru HDS spectrum for
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.8\textwidth]{h_alpha_subaru.pdf}
-\caption{H$\alpha$ line as measured by Subaru HDS on two adjacent nights in 2015.
-The line's core changes noticeably between the two nights.}\label{fig:Halpha}
-\end{centering}
-\end{figure*}
-
-As discussed in Section \ref{sec:intro}, \citet{kawahara2013starspots} first noted an anti-correlation between the transit depths of \sha\ and the flux of its host star.
-This correlation implies that the planet disintegration is regulated by the high energy radiation or magnetic energy associated with star spots and that the planet's passage over the spot can increase the disintegration activity.
-\citet{croll2015starspots} confirm this anti-correlation but offer a different explanation: occulted dark spots on the stellar surface can decrease the transit depth because the planetary debris extincts less total starlight.
-If there is a localized grouping of spots that the planet's transit chord passes through, this could create a positive correlation of transit depth with stellar flux.
-\citet{croll2015starspots} note that the spots could have a complicated distribution and that a separate set of spots on the other side of the star could dominate the overall light curve rotational modulation but be at a different latitude from the transit chord, thus creating an anti-correlation between transit depth and stellar flux.
-\citet{croll2015starspots} calculate that unocculted spots
-
-Recently, \citet{rackham2018transitSourceEffect} have studied, in detail, the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
-One commonly held assumption is that there is a linear relation between the amplitude of variability and the spot covering fraction.
-Instead, \citet{rackham2018transitSourceEffect} use more realistic simulations of spot covering and light curve modulations and find that the amplitude of variability is proportional to $\sqrt{f_S}$, where $f_S$ is the spot covering fraction.
-
-For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
-Rackham, private communication, 2018}
-The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
-Also, the bias in transit depth is different from the transit depth variations, which would be un-affacted by a polar spot.
-Therefore, the conclusion from \citet{croll2015starspots} that unocculted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
+\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 pc.
+We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
+For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model.
+We also assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting and a photometric error of 5\%, assumed to be dominated by photometric systematics.
+Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
 }
@@
 We explore this possibility by examining archival Subaru HDS spectra of \shStar.
-We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, M=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
+We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, \replaced{M}{R}=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
 Therefore, the optical depth of any gas sublimating \replaced{of}{off} dust grains is too small to affect \added{the parameters derived from} the high resolution spectrum.
@@
 The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.
+\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.}
 

### 2018-09-25 ms.tex

--- 2018-09-23 ms.tex
@@
 
-\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data.
-The GAIA DR2 parallax of 618 $\pm$ 12 pc can be used with the bolometric flux and effective temperature to estimate the stellar radius \citep[e.g.][]{stassun2017gaiaRadiiMasses}.
-We estimate a radius of 0.7 R$_\odot$, which is consistent with a main-sequence star.
+\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 pc.
+We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
+For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model.
+We also assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting and a photometric error of 5\%, assumed to be dominated by photometric systematics.
+Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
 
@@
 \citet{croll2015starspots} calculate that unocculted spots 
+>>>>>>> 5cf2b3b9d0cb4ff5d079f02e7c26986a56147bb5
 

### 2018-09-25 ms.tex
finished up sentence on Croll et al. conclusion on unocculted spots.
added a figure, citations and plot of the spectral energy distributions.

@@
 \documentclass[preprint,trackchanges]{aastex61}
+
 %\documentclass[iop]{emulateapj}
@@
 
-\section{Introduction}\label{sec:Intro}
+\section{Introduction}\label{sec:intro}
 \citet{rappaport} first reported the discovery of a highly unusual system in the \kepler\ field, KIC 12557548.
@@
 
-\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 pc.
-We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
-For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model.
-We also assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting and a photometric error of 5\%, assumed to be dominated by photometric systematics.
-Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
-
-While examining the bolometric flux from all available data, we notice that the WISE band 4 flux is in excess of a \citet{castelli2004models} stellar model.
-This is also true of the disintegrating system K2-22 b.
-These infrared fluxes may arise from dust created by the disintegrating planet and pushed out to a larger radius to form a disk or ring.
-}.
-
 \added{
@@
 \citet{croll2015starspots} note that the spots could have a complicated distribution and that a separate set of spots on the other side of the star could dominate the overall light curve rotational modulation but be at a different latitude from the transit chord, thus creating an anti-correlation between transit depth and stellar flux.
-\citet{croll2015starspots} calculate that unocculted spots 
->>>>>>> 5cf2b3b9d0cb4ff5d079f02e7c26986a56147bb5
+\citet{croll2015starspots} calculate that unocculted spots have a minimal impact on the transit depth variations.
 
@@
 }
+
+\added{
+\section{Spectral Energy Distribution and Parallax}\label{sec:SED}
+
+We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 pc \citep{gaia2016mission,gaia2018dr2,luri2018parallaxes}.
+We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
+For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model and a (E-B)=0.05 diffuse Milky Way extinction model \citep{cardelli1989}.
+We use the \texttt{pysynphot} tool \citep{lim2015pysynphot} to calculate the model and extinction.
+We note that the exact stellar model used is less important than finding a function to fit the Spectral Energy Distribution.
+When inverting the Stefan-Boltzman law, we assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting and a photometric error of 5\%, assumed to be dominated by photometric systematics.
+Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
+
+While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m are significantly in excess of a \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
+This is also true of the disintegrating system K2-22 b.
+These infrared fluxes may arise from dust created by the disintegrating planet and pushed out to a larger radius to form a disk or ring.
+Further investigation of the infrared excesses should be explored observationally and theoretically.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.8\textwidth]{kic1255_sed.pdf}
+\caption{\added{The spectral Energy distribution from VizieR \citep{ochsenbein2000vizieR}.
+The photometry is fit in order to estimate the stellar bolometric flux and derive a stellar radius of 0.72 $\pm$ 0.03 R$_\odot$.
+We note that the WISE Band 3 and Band 4 excess may arise from a dusty ring or disk of material from the planet, warranting further investigation.}}\label{fig:SED}
+\end{centering}
+\end{figure*}
+}.
 
@@
 The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.
-\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.}
+\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.
+This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
+Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.}
 
@@
 	\texttt{iraf},
-	\texttt{SpecMatch-Emp} \citep{yee2017specMatch} 
+	\texttt{SpecMatch-Emp} \citep{yee2017specMatch},
          \texttt{emcee} \citep{foreman-mackey2013emcee}, 
+         \added{ \texttt{pysynphot} \citep{lim2015pysynphot}}
           }

### 2018-09-25 ms.tex
explicitly cited WISE.

@@
 
-While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m are significantly in excess of a \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
+While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m \citep{wright2010wise} are significantly in excess of a \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
 This is also true of the disintegrating system K2-22 b.
@@
 This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
-Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.}
+Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
+This publication makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.}
 

### 2018-09-25 ms.tex
neatened up the SED plot.

@@
 The photometry is fit in order to estimate the stellar bolometric flux and derive a stellar radius of 0.72 $\pm$ 0.03 R$_\odot$.
-We note that the WISE Band 3 and Band 4 excess may arise from a dusty ring or disk of material from the planet, warranting further investigation.}}\label{fig:SED}
+We note that the WISE Band 3 and Band 4 excess at 12$\mu$m and 22 $\mu$m may arise from a dusty ring or disk of material from the planet, warranting further investigation.}}\label{fig:SED}
 \end{centering}

### 2018-09-26 ms.tex
switched the SED an stellar activity sections.
a few more thoughts on SED and stellar activity.

@@
 We therefore conclude that the noise in the spectrum affected the stellar parameters rather than gas absorption from sublimating dust grains.
-
-\added{
-\section{Stellar Activity}\label{sec:activity}
-
-The high resolution spectrum of \shStar\ allows us to measure the H$\alpha$ line, which is an indicator of stellar activity.
-Figure \ref{fig:Halpha}, shows the Subaru HDS spectrum for
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.8\textwidth]{h_alpha_subaru.pdf}
-\caption{H$\alpha$ line as measured by Subaru HDS on two adjacent nights in 2015.
-The line's core changes noticeably between the two nights.}\label{fig:Halpha}
-\end{centering}
-\end{figure*}
-
-As discussed in Section \ref{sec:intro}, \citet{kawahara2013starspots} first noted an anti-correlation between the transit depths of \sha\ and the flux of its host star.
-This correlation implies that the planet disintegration is regulated by the high energy radiation or magnetic energy associated with star spots and that the planet's passage over the spot can increase the disintegration activity.
-\citet{croll2015starspots} confirm this anti-correlation but offer a different explanation: occulted dark spots on the stellar surface can decrease the transit depth because the planetary debris extincts less total starlight.
-If there is a localized grouping of spots that the planet's transit chord passes through, this could create a positive correlation of transit depth with stellar flux.
-\citet{croll2015starspots} note that the spots could have a complicated distribution and that a separate set of spots on the other side of the star could dominate the overall light curve rotational modulation but be at a different latitude from the transit chord, thus creating an anti-correlation between transit depth and stellar flux.
-\citet{croll2015starspots} calculate that unocculted spots have a minimal impact on the transit depth variations.
-
-Recently, \citet{rackham2018transitSourceEffect} have studied, in detail, the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
-One commonly held assumption is that there is a linear relation between the amplitude of variability and the spot covering fraction.
-Instead, \citet{rackham2018transitSourceEffect} use more realistic simulations of spot covering and light curve modulations and find that the amplitude of variability is proportional to $\sqrt{f_S}$, where $f_S$ is the spot covering fraction.
-
-For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
-Rackham, private communication, 2018}
-The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
-Also, the bias in transit depth is different from the transit depth variations, which would be un-affacted by a polar spot.
-Therefore, the conclusion from \citet{croll2015starspots} that unocculted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
-}
-
 \added{
@@
 
-We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 pc \citep{gaia2016mission,gaia2018dr2,luri2018parallaxes}.
+We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 mas \citep{gaia2016mission,gaia2018dr2,luri2018parallaxes}.
 We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
@@
 
+\added{
+\section{Stellar Activity}\label{sec:activity}
+
+The high resolution spectrum of \shStar\ allows us to measure the H$\alpha$ line, which is an indicator of stellar activity.
+Figure \ref{fig:Halpha}, shows the Subaru HDS spectrum for 2015 Aug 28 and 2015 Aug 29.
+We note that the strong emission feature at the core of the H$\alpha$ line is visible for one night but not the other, confirming the activity of the star already known from the rotational modulations \citep{kawahara2013starspots}.
+
+\begin{figure*}[!hbtp]
+\begin{centering}
+\includegraphics[width=0.8\textwidth]{h_alpha_subaru.pdf}
+\caption{H$\alpha$ line as measured by Subaru HDS on two adjacent nights in 2015.
+The line's core changes noticeably between the two nights.}\label{fig:Halpha}
+\end{centering}
+\end{figure*}
+
+As discussed in Section \ref{sec:intro}, \citet{kawahara2013starspots} first noted an anti-correlation between the transit depths of \sha\ and the flux of its host star.
+This correlation implies that the planet disintegration is regulated by the high energy radiation or magnetic energy associated with star spots and that the planet's passage over the spot can increase the disintegration activity.
+\citet{croll2015starspots} confirm this anti-correlation but offer a different explanation: occulted dark spots on the stellar surface can decrease the transit depth because the planetary debris extincts less total starlight.
+If there is a localized grouping of spots that the planet's transit chord passes through, this could create a positive correlation of transit depth with stellar flux.
+\citet{croll2015starspots} note that the spots could have a complicated distribution and that a separate set of spots on the other side of the star could dominate the overall light curve rotational modulation but be at a different latitude from the transit chord, thus creating an anti-correlation between transit depth and stellar flux.
+\citet{croll2015starspots} calculate that unocculted spots have a minimal impact on the transit depth variations.
+
+Recently, \citet{rackham2018transitSourceEffect} have studied in detail the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
+One commonly held assumption is that there is a linear relation between the amplitude of variability and the spot covering fraction.
+Instead, \citet{rackham2018transitSourceEffect} use more realistic simulations of spot covering and light curve modulations and find that the amplitude of variability is proportional to $\sqrt{f_S}$, where $f_S$ is the spot covering fraction.
+
+For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
+Rackham, private communication, 2018}
+The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
+Also, the bias in transit depth is different from the transit depth variations, which would be un-affacted by a polar spot.
+Therefore, the conclusion from \citet{croll2015starspots} that unocculted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
+}
+
 \section{Conclusions}\label{sec:conclusions}
@@
 Therefore, the optical depth of any gas sublimating \replaced{of}{off} dust grains is too small to affect \added{the parameters derived from} the high resolution spectrum.
+\added{We also confirm the main-sequence radius of the star using the Gaia DR2 parallax.
+While fitting the Spectral Energy Distribution to estimate the bolometric flux, we notice that there is an infrared excess in WISE Bands 3 and 4 that warrants further study.}
 We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.

### 2018-09-27 ms.tex
somre more speculation on the long timescale evolution of the tail.

@@
 
-%We also show the first two principal components as a scatter plot in Figure \ref{fig:pcaVectorsComp}.
-%In some applications of PCA, separate populations of behaviors can appear in these scatter plots (such as different modes of planet disintegration) but here there is a continuous distribution points.
-%We also color the quiescent periods of very little disintegration activity (discussed in \citet{vanWerkhoven2014} and \citet{croll2015starspots}) and these quiescent periods appear as low values for the first two principal components.
-
 In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
@@
 \end{figure*}
+
+\added{
+We note that the long-term evolution of the transit depths and shape may be similar to the trends observed on WD1145+017 \citep{gary2017photometricObsWD1145p017,rappaport2018opticalActivityWD1145p017}.
+WD1145+017 also changes its transit activity on $\sim$ month long timescales.
+These trends in transit activity are explained by either random collisions of asteroids or variable dust emission of asteroids.
+We suspect that sublimating asteroids around WD1145+017, the \sha\ and K2-22 b could have long term behavior determined by surface features.
+If alternating layers of rocky material have different composition, sublimation temperatures or albedos, they could provide a natural way to regulate.
+Alternatively, the chance alignment of starspots with the planet could regulate the planet disintegration \citep{kawahara2013starspots} and create periodic behaviors.
+}
 

### 2018-09-28 ms.tex
added Ben's suggestions and made him a co-author.

@@
 \author{Elizabeth Green}
+\affiliation{Steward Observatory, Tucson AZ 85721}
+
+\author{Benjamin V. Rackham}
 \affiliation{Steward Observatory, Tucson AZ 85721}
@@
 Recently, \citet{rackham2018transitSourceEffect} have studied in detail the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
+Using a suite of model rotating photospheres with active regions added successively at random positions, they explored the dependence of observed brightness variations with spot and faculae covering fractions.
 One commonly held assumption is that there is a linear relation between the amplitude of variability and the spot covering fraction.
-Instead, \citet{rackham2018transitSourceEffect} use more realistic simulations of spot covering and light curve modulations and find that the amplitude of variability is proportional to $\sqrt{f_S}$, where $f_S$ is the spot covering fraction.
+Instead, \citet{rackham2018transitSourceEffect} find that the amplitude of variability is proportional to $\sqrt{f_S}$, where $f_S$ is the spot covering fraction.
+They also find that large ranges of $f_{S}$ are consistent with a given amplitude of variability, leading to a correspondingly large range of transit depth changes possible for a given stellar variability amplitude.
 
-For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V.
-Rackham, private communication, 2018}
-The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
-Also, the bias in transit depth is different from the transit depth variations, which would be un-affacted by a polar spot.
+Extending the analysis to spectral types F5V to K9V, which display larger spot contrasts \citep{berdyugina2005spots} and lower typical rotational variabilities than M dwarfs \citep{mcquillan2014rotationPeriodsAutoC}, \citet{rackham2018activityFGKsubmitted} find the observed variabilities of FGK dwarfs point to relatively low spot coverages and transit depth biases.
+Their scaling relations suggest that the observed amplitude variations of 0.8\% \citep{kawahara2013starspots} for a K4 dwarf correspond to $f_{S}=3^{+5}_{-2}\%$, indicating that transit depths of exoplanets can be biased by $3^{+3}_{-2}\%$ at optical wavelengths depending on the distribution and sizes of spots and that the transit chord is completely devoid of spots.
+
+High values of $f_S$ are possible for longitudinally symmetric distributions of active regions, such as a latitudinal band or polar spot.
+Polar spots are indeed observed on rapidly rotating stars via Doppler imaging \citep{strassmeier2009starspots}; however, one would be unlikely on \sha, given its relatively long rotation period.
+Additionally, the large physical size of \sha, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and thus this diminish the transit source effect further.
+In this light, \sha's 30\% observed transit depth variation would require a pathological distribution of stellar activity to be explained by un-occulted spots.
+If the spot distribution is polar or distributed in a latitudinal band, this would produce a bias at all epochs, unlike the time-dependent transit depth variations observed in \sha.
 Therefore, the conclusion from \citet{croll2015starspots} that unocculted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
@@
 Therefore, the optical depth of any gas sublimating \replaced{of}{off} dust grains is too small to affect \added{the parameters derived from} the high resolution spectrum.
+We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.
 \added{We also confirm the main-sequence radius of the star using the Gaia DR2 parallax.
-While fitting the Spectral Energy Distribution to estimate the bolometric flux, we notice that there is an infrared excess in WISE Bands 3 and 4 that warrants further study.}
-We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.
+While fitting the Spectral Energy Distribution to estimate the bolometric flux, we notice that there is an infrared excess in WISE Bands 3 and 4 that warrants further study.
+
+We examine the effect of un-occulted spots on the transit depth behavior in light of recent research by \citet{rackham2018transitSourceEffect} that star spot coverage can be underestimated by a linear scaling with stellar flux variability amplitude.
+Even when accounting for the larger coverage of starspots by this effect, we confirm the conclusion from \citet{croll2015starspots} that {\it un-occulted} spots are unlikely to explain the correlation between transit depth and stellar flux.
+It is still possible that \sha's disintegration is regulated by stellar activity or that {\it occulted} spots account for this correlation.}
 
@@
 Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
-The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.
+\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
 \added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.

### 2018-10-01 ms.tex
a little more comparison with WD 1145+017.

@@
 These trends in transit activity are explained by either random collisions of asteroids or variable dust emission of asteroids.
-We suspect that sublimating asteroids around WD1145+017, the \sha\ and K2-22 b could have long term behavior determined by surface features.
-If alternating layers of rocky material have different composition, sublimation temperatures or albedos, they could provide a natural way to regulate.
-Alternatively, the chance alignment of starspots with the planet could regulate the planet disintegration \citep{kawahara2013starspots} and create periodic behaviors.
+
+We suspect that sublimating asteroids around WD1145+017, the \sha\ and K2-22 b have long term behavior determined by surface features.
+If alternating layers of rocky material have different composition, sublimation temperatures or albedos, they could provide a natural way to regulate the sublimation rate of the surface.
+Alternatively, the chance alignment of starspots with the planet could regulate the planet disintegration \citep{kawahara2013starspots} and create periodic behaviors depending on the alignment of stellar rotation with the planet's position within its orbit.
+\sha\ exhibits large stochastic variance that occasionally shuts off during quiescent intervals.
+The transit activity level of WD1145+017's exhibits more complicated time dependence because there are many separate planetesimals or recently broken-up fragments that can serve as sources of dust \citep{vanderburg2015wdDisintegrating}.
 }

### 2018-10-01 ms.tex
added a sentence in the abstract about WISE infrared excess.

@@
 There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism on such long timescales remains unclear.
+\added{Another area to be explored is the WISE band 3 and 4 infrared excess in the spectral energy distribution, probably arising for a dust ring or disk.}
 \end{abstract}
@@
 This is also true of the disintegrating system K2-22 b.
-These infrared fluxes may arise from dust created by the disintegrating planet and pushed out to a larger radius to form a disk or ring.
+These infrared fluxes may arise from dust created by the disintegrating planet and radiatively pushed out to a larger radius to form a disk or ring.
 Further investigation of the infrared excesses should be explored observationally and theoretically.

### 2018-10-03 ms.tex
justified choice of number of PCs.

@@
 If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$ -0.12 to $\sim$0.15).
-The model using the first 4 principal components shown in Figure \ref{fig:riverPlotsPCA} better matches the data and has residuals much closer to white noise than the model that uses the dot product with the average light curve.
+
+\added{We model the 2D {\it Kepler} flux grid shown in Figure \ref{fig:riverPlotsPCA} (Left) with a set of principal components and examine the residuals to evaluate the number of principal components to keep.
+We begin with 1 principal component and progressively added one at at time until the residuals along the transit number axis of Figure \ref{fig:riverPlotsPCA} are the same as the out-of-transit flux.
+We find that after 4 eigenvectors, the in-transit (with phases between -0.12 and 0.15) matches the out-of-transit standard deviation of $\sim 0.05\%$.}
+The model using the first 4 principal components shown in Figure \ref{fig:riverPlotsPCA} \added{(Right)} better matches the data and has residuals much closer to white noise than the model that uses the dot product with the average light curve.
 

### 2018-10-04 ms.tex
added false alarm levels to periodograms.

@@
 The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.
-The second principal components shows one dominant peak at 491 days, \deleted{in addition to the 0.654 orbital period,} indicating possible long term evolution of the dust particle sizes.}\label{fig:ampPeriodogram}
+The second principal components shows one dominant peak at 491 days, \deleted{in addition to the 0.654 orbital period,} indicating possible long term evolution of the dust particle sizes.
+\added{False alarm levels with probabilities of 0.05 and $10^{-4}$ are shown as orange horizontal lines.}}\label{fig:ampPeriodogram}
 \end{centering}

### 2018-10-04 ms.tex
false alarm probabilties, this finished referees comments.

@@
 The implication of the PCA then is that the dust particle sizes may be changing with time.
+\added{We assess the uncertainty of this conclusion through the time series of the principal components.}
 
@@
 Quiescent intervals with low transit activity are identified from the amplitude \added{and highlighted in orange. 
-Typical (median) error bars for the time series are shown as red error bars at arbitrary positions.}
+Typical error bars for the time series are shown as red error bars at arbitrary positions.}
 The first principal component tracks closely with the amplitude.
@@
 We highlight the quiescent periods, which are also discussed in \citet{kawahara2013starspots}, \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
+\added{We estimate the errors in the principal components by measuring the dot product with the secondary eclipse light curve and calculating its standard deviation.}
 The first principal component largely tracks closely with the dot product of the average light curve ($A'$).
@@
 In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
+\added{We also show the formal false alarm levels of $5 \times 10^{-2}$ and $10^{-4}$ for the periodograms.}
 \deleted{The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the sampling cadence of the time series of amplitudes and principal components.}
@@
 The second principal components shows one dominant peak at 491 days, \deleted{in addition to the 0.654 orbital period,} indicating possible long term evolution of the dust particle sizes.
-\added{False alarm levels with probabilities of 0.05 and $10^{-4}$ are shown as orange horizontal lines.}}\label{fig:ampPeriodogram}
+\added{False alarm levels with probabilities of $5 \times 10^{-2}$ and $10^{-4}$ are shown as orange horizontal lines.}}\label{fig:ampPeriodogram}
 \end{centering}

### 2018-10-04 ms.tex
some proofreading of the red text.

@@
 \added{
-\section{Spectral Energy Distribution and Parallax}\label{sec:SED}
+\subsection{Spectral Energy Distribution and Parallax}\label{sec:SED}
 
@@
 We note that the exact stellar model used is less important than finding a function to fit the Spectral Energy Distribution.
-When inverting the Stefan-Boltzman law, we assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting and a photometric error of 5\%, assumed to be dominated by photometric systematics.
+When inverting the Stefan-Boltzman law, we assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting in Section \ref{sec:SpecMatch-Emp} and a photometric error of 5\%, assumed to be dominated by photometric systematics.
 Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
 
-While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m \citep{wright2010wise} are significantly in excess of a \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
+While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m \citep{wright2010wise} are significantly in excess of the \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
 This is also true of the disintegrating system K2-22 b.
@@
 Polar spots are indeed observed on rapidly rotating stars via Doppler imaging \citep{strassmeier2009starspots}; however, one would be unlikely on \sha, given its relatively long rotation period.
-Additionally, the large physical size of \sha, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and thus this diminish the transit source effect further.
-In this light, \sha's 30\% observed transit depth variation would require a pathological distribution of stellar activity to be explained by un-occulted spots.
+Additionally, the large physical size of \sha, as indicated by a transit duration longer than the time to cross the star, meaning that spots are likely to be crossed and thus diminish the transit source effect further.
+In this light, \sha's $\sim$30\% observed transit depth variation at a $\sim$ 22 day period would require a pathological distribution of stellar activity to be explained by un-occulted spots.
 If the spot distribution is polar or distributed in a latitudinal band, this would produce a bias at all epochs, unlike the time-dependent transit depth variations observed in \sha.

### 2018-10-06 ms.tex
minor typo corrections after reading red sections aloud.

@@
 There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism on such long timescales remains unclear.
-\added{Another area to be explored is the WISE band 3 and 4 infrared excess in the spectral energy distribution, probably arising for a dust ring or disk.}
+\added{Another area to be explored is the WISE band 3 and 4 infrared excess in the spectral energy distribution, probably arising from a dust ring or disk.}
 \end{abstract}
@@
 We begin with 1 principal component and progressively added one at at time until the residuals along the transit number axis of Figure \ref{fig:riverPlotsPCA} are the same as the out-of-transit flux.
-We find that after 4 eigenvectors, the in-transit (with phases between -0.12 and 0.15) matches the out-of-transit standard deviation of $\sim 0.05\%$.}
+We find that after 4 eigenvectors, the in-transit (with phases between -0.12 and 0.15) matches the out-of-transit standard deviation of $\sim 0.05\%$, also found in the secondary eclipse 2D flux grid.}
 The model using the first 4 principal components shown in Figure \ref{fig:riverPlotsPCA} \added{(Right)} better matches the data and has residuals much closer to white noise than the model that uses the dot product with the average light curve.
@@
 \citet{croll2015starspots} note that the spots could have a complicated distribution and that a separate set of spots on the other side of the star could dominate the overall light curve rotational modulation but be at a different latitude from the transit chord, thus creating an anti-correlation between transit depth and stellar flux.
-\citet{croll2015starspots} calculate that unocculted spots have a minimal impact on the transit depth variations.
+\citet{croll2015starspots} calculate that un-occulted spots have a minimal impact on the transit depth variations.
 
@@
 If the spot distribution is polar or distributed in a latitudinal band, this would produce a bias at all epochs, unlike the time-dependent transit depth variations observed in \sha.
-Therefore, the conclusion from \citet{croll2015starspots} that unocculted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
+Therefore, the conclusion from \citet{croll2015starspots} that un-occulted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
 }

### 2018-10-06 ms.tex
a few edits from Teru's comments.

@@
 \newcommand{\lbol}{$\log_{10}{L_{bol}/L_{\sun}}$}
-\newcommand{\teff}{T$_{eff}$}
+\newcommand{\teff}{T$_\mathrm{eff}$}
 \newcommand{\logg}{$\log{g}$}
@@
 Here, we follow up two perplexing observations of the system: 1) the transits appeared shallower than average in 2013 and 2014 and 2) the parameters derived from a high resolution spectrum of the star differed from other results using photometry and low resolution spectroscopy.
-We observe 5 transits of the system with the 61-inch Kuiper telescope in 2016 and show that they are consistent with photometry from the \kepler\ spacecraft in 2009-2013.
-We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_{eff}$=4440 $\pm$70 K star in agreement with the photometry and low resolution spectroscopy.
+We observe 5 transits of the system with the 61-inch Kuiper telescope in 2016 and show that they are consistent with photometry from the \kepler\ spacecraft in 2009-2013\added{, suggesting that the dusty tail has returned to normal length and mass}.
+We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_\mathrm{eff}$=4440 $\pm$70 K star in agreement with the photometry and low resolution spectroscopy.
 This disfavors the hypothesis that planet disintegration affected the analysis of prior high resolution spectra of this star.
@@
 
-After the discovery of K1255, other systems were found to show similar light curve behavior: K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating} \replaced{,}{and} KOI 2700 \citep{rappaport2014KOI2700} \deleted{and KIC 3542116 \citep{rappaport2018exocomets}}.
+After the discovery of \replaced{K1255}{\shStar}, other systems were found to show similar light curve behavior: K2-22\deleted{b} \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating} \replaced{,}{and} KOI 2700 \citep{rappaport2014KOI2700} \deleted{and KIC 3542116 \citep{rappaport2018exocomets}}.
 A collection, albeit small, of several different disintegrating planet systems makes for a useful laboratory for understanding planet evolution and composition.
@@
 \added{We model the 2D {\it Kepler} flux grid shown in Figure \ref{fig:riverPlotsPCA} (Left) with a set of principal components and examine the residuals to evaluate the number of principal components to keep.
-We begin with 1 principal component and progressively added one at at time until the residuals along the transit number axis of Figure \ref{fig:riverPlotsPCA} are the same as the out-of-transit flux.
+We begin with 1 principal component and progressively added one at time until the residuals along the transit number axis of Figure \ref{fig:riverPlotsPCA} are the same as the out-of-transit flux.
 We find that after 4 eigenvectors, the in-transit (with phases between -0.12 and 0.15) matches the out-of-transit standard deviation of $\sim 0.05\%$, also found in the secondary eclipse 2D flux grid.}
@@
 The fact that the pre-ingress flux increase is not found in the first eigenvector and instead is pronounced in orthogonal eigenvectors suggests that the dust particle sizes may be changing in time.
-We would expect that a dust tail with a variable number of of particles but a constant grain size would be exhibit a forward scattering in the first principal component because the forward scattering flux would scale proportionally with the number of particles and transit depth.
+We would expect that a dust tail with a variable number of of particles but a constant grain size would \deleted{be} exhibit a forward scattering in the first principal component because the forward scattering flux would scale proportionally with the number of particles and transit depth.
 The implication of the PCA then is that the dust particle sizes may be changing with time.
@@
 \colhead{Reference} &
-\colhead{$ T_{eff,*} $} &
+\colhead{$ T_\mathrm{eff,*} $} &
 \colhead{$\log(g)$} &
@@
 
-We explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
+We explore the 5 parameters in the BOSZ models: T$_\mathrm{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
 The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
@@
 We found the model with the  $\chi^2$ statistic over the Mg I triplet lines from 5160 to 5190 $\AA$
-The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T$_{eff}$=4500 K, Log(g)=4.5, [M/H]=0.0, [C/M]=0.0, $\alpha=-0.25$.
-This is similar to the log(g)$\approx$4.6, T$_{eff}$=4500 stellar parameters derived from photometry and low resolution spectroscopy listed in Table \ref{tab:stellObsParams}.
+The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T$_\mathrm{eff}$=4500 K, Log(g)=4.5, [M/H]=0.0, [C/M]=0.0, $\alpha=-0.25$.
+This is similar to the log(g)$\approx$4.6, T$_\mathrm{eff}$=4500 stellar parameters derived from photometry and low resolution spectroscopy listed in Table \ref{tab:stellObsParams}.
 
@@
 However, the metallicity is less well constrained.
-The resulting best-fit parameters from \texttt{SpecMatch-Emp} are T$_{eff}$=4440 K $\pm$ 70 K, [Fe/H]=-0.08$\pm$0.09, log(g)=4.63$\pm$0.12, R=0.69 $\pm$ 0.10 R$_\odot$ and Mass=0.70 $\pm 0.08~$M$_\odot$.
+The resulting best-fit parameters from \texttt{SpecMatch-Emp} are T$_\mathrm{eff}$=4440 K $\pm$ 70 K, [Fe/H]=-0.08$\pm$0.09, log(g)=4.63$\pm$0.12, R=0.69 $\pm$ 0.10 R$_\odot$ and Mass=0.70 $\pm 0.08~$M$_\odot$.
 Figure \ref{fig:SpecMatch-EmpComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{SpecMatch-Emp} over a subset of the wavelengths near the Mg I triplet.
@@
 We explore this possibility by examining archival Subaru HDS spectra of \shStar.
-We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, \replaced{M}{R}=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
+We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_\mathrm{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, \replaced{M}{R}=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
 Therefore, the optical depth of any gas sublimating \replaced{of}{off} dust grains is too small to affect \added{the parameters derived from} the high resolution spectrum.
@@
 Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
+\added{This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.}
 \replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor

### 2018-10-07 ms.tex
removed th SED stuff now that I realize the WISE band 3 and 4 fluxes are just upper limits.

@@
 There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism on such long timescales remains unclear.
-\added{Another area to be explored is the WISE band 3 and 4 infrared excess in the spectral energy distribution, probably arising from a dust ring or disk.}
 \end{abstract}
 
-%\keywords{stars: atmospheres -- stars: individual (\objectname{KIC 12557548}) -- stars: variables: general}
+\keywords{stars: atmospheres -- stars: individual (\objectname{KIC 12557548}, \objectname{KOI-3794}, \objectname{Kepler-1520}) -- stars: variables: general}
 
@@
 This was \replaced{smaller}{slightly broader} than we expected from combining inverse resolving powers in quadrature, which would imply that an \replaced{$R=75,000$}{$R_{expected} = 75,000$} kernel \added{($\sigma_{expected} = \lambda/176,600$)} convolved with an $R=100,000$ spectrum would result in a $R=60,000$ spectrum.
-\added{We suspect that the non-Gaussian shape of the line spread function is the cause of this discrepancy.}
+\added{We suspect that the non-Gaussian shape of the instrumental line broadening is the cause of this discrepancy.}
 
@@
 Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
-
-While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m \citep{wright2010wise} are significantly in excess of the \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
-This is also true of the disintegrating system K2-22 b.
-These infrared fluxes may arise from dust created by the disintegrating planet and radiatively pushed out to a larger radius to form a disk or ring.
-Further investigation of the infrared excesses should be explored observationally and theoretically.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.8\textwidth]{kic1255_sed.pdf}
-\caption{\added{The spectral Energy distribution from VizieR \citep{ochsenbein2000vizieR}.
-The photometry is fit in order to estimate the stellar bolometric flux and derive a stellar radius of 0.72 $\pm$ 0.03 R$_\odot$.
-We note that the WISE Band 3 and Band 4 excess at 12$\mu$m and 22 $\mu$m may arise from a dusty ring or disk of material from the planet, warranting further investigation.}}\label{fig:SED}
-\end{centering}
-\end{figure*}
-}.
+}
 
@@
 Figure \ref{fig:Halpha}, shows the Subaru HDS spectrum for 2015 Aug 28 and 2015 Aug 29.
+
 We note that the strong emission feature at the core of the H$\alpha$ line is visible for one night but not the other, confirming the activity of the star already known from the rotational modulations \citep{kawahara2013starspots}.
@@
 \added{We also confirm the main-sequence radius of the star using the Gaia DR2 parallax.
-While fitting the Spectral Energy Distribution to estimate the bolometric flux, we notice that there is an infrared excess in WISE Bands 3 and 4 that warrants further study.
-
 We examine the effect of un-occulted spots on the transit depth behavior in light of recent research by \citet{rackham2018transitSourceEffect} that star spot coverage can be underestimated by a linear scaling with stellar flux variability amplitude.

### 2018-10-08 ms.tex
Ben Rackham's comments.

@@
 Additionally, the large physical size of \sha, as indicated by a transit duration longer than the time to cross the star, meaning that spots are likely to be crossed and thus diminish the transit source effect further.
-In this light, \sha's $\sim$30\% observed transit depth variation at a $\sim$ 22 day period would require a pathological distribution of stellar activity to be explained by un-occulted spots.
+In this light, \sha's $\sim$30\% observed transit depth variation at a $\sim$ 22 day period would require a pathological distribution of magnetically active regions to be explained by un-occulted spots.
 If the spot distribution is polar or distributed in a latitudinal band, this would produce a bias at all epochs, unlike the time-dependent transit depth variations observed in \sha.

### 2018-10-08 ms.tex
added Johanna's acknowledgement.

@@
 Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
-\added{This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.}
+\added{This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
+Support for this work was provided by NASA through Hubble Fellowship grant HST-HF2-51399.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.}
 \replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor

### 2018-10-09 ms.tex
removed the H-alpha stuff because now we realize the spike was an artifact of the data cleaning.

@@
 In Section \ref{sec:stellarCharacterization}, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
-\added{In Section \ref{sec:activity}, we examine the activity of the star from the H$\alpha$ line and also discuss how starspots can affect the light curves.}
+\added{In Section \ref{sec:activity}, we examine how un-occulted starspots can affect the transit depth behavior.}
 We conclude in Section \ref{sec:conclusions}.
@@
 
-The high resolution spectrum of \shStar\ allows us to measure the H$\alpha$ line, which is an indicator of stellar activity.
-Figure \ref{fig:Halpha}, shows the Subaru HDS spectrum for 2015 Aug 28 and 2015 Aug 29.
-
-We note that the strong emission feature at the core of the H$\alpha$ line is visible for one night but not the other, confirming the activity of the star already known from the rotational modulations \citep{kawahara2013starspots}.
-
-\begin{figure*}[!hbtp]
-\begin{centering}
-\includegraphics[width=0.8\textwidth]{h_alpha_subaru.pdf}
-\caption{H$\alpha$ line as measured by Subaru HDS on two adjacent nights in 2015.
-The line's core changes noticeably between the two nights.}\label{fig:Halpha}
-\end{centering}
-\end{figure*}
-
 As discussed in Section \ref{sec:intro}, \citet{kawahara2013starspots} first noted an anti-correlation between the transit depths of \sha\ and the flux of its host star.

### 2018-10-11 ms.tex
added short acknowledgement for Ben W.

@@
 Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
-\added{This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
+\added{Thanks to Ben Weiner for some useful discussion on the high resolution spectroscopy.
+This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
 Support for this work was provided by NASA through Hubble Fellowship grant HST-HF2-51399.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.}

### 2018-10-13 ms.tex
minor typos fixed after reading aloud.

--- 2018-10-09 ms.tex
@@
 \citet{rappaport} first reported the discovery of a highly unusual system in the \kepler\ field, KIC 12557548.
-Its light curve exhibits flux dips with a period of 0.653 days.
+Its light curve exhibits flux dips with a period of \replaced{0.653}{0.654} days.
 Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$0\% to $\sim$1.2\%.
-The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next 0.653 days later.
-This is radially different from a transiting planet, where the planet absorbs the same amount of light from the star each orbit and does so symmetrically about the star, modulo stellar inhomogenities.
+The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next \replaced{0.653}{0.654} days later.
+This is \replaced{radially}{radically} different from a transiting planet, where the planet absorbs the same amount of light from the star each orbit and does so symmetrically about the star, modulo stellar inhomogenities.
 The time variability of the flux dips indicates that material with a projected area $\sim$1\% of the stellar surface is created and cleared in $\lesssim$ 1 day timescales in order to extinct $\sim$1\% of starlight at one epoch and $\sim$0\% at another.
@@
 Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no fully agreed-upon explanations: KIC 8462852 (ie.
-Boyajian's star) \citep{boyajian846}, RIK-210/EPIC 205483258 \citep{david2017rik210},  and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
+Boyajian's star) \citep{boyajian846}, RIK-210/EPIC 205483258 \citep{david2017rik210}  and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
 KIC 8462852 may be a family of comets from one or more parent bodies that recently broke apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
@@
 \includegraphics[width=0.49\textwidth]{stamps_kic1255_UT2016_07_14.pdf}
-\caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of Mont4K.
+\caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of \added{the} Mont4K \added{imager}.
 {\it Right:} Postage stamp zoom-ins for the source and reference stars show the point spread functions for each star.
@@
 The fact that the pre-ingress flux increase is not found in the first eigenvector and instead is pronounced in orthogonal eigenvectors suggests that the dust particle sizes may be changing in time.
-We would expect that a dust tail with a variable number of of particles but a constant grain size would \deleted{be} exhibit a forward scattering in the first principal component because the forward scattering flux would scale proportionally with the number of particles and transit depth.
+We would expect that a dust tail with a variable number of \deleted{of} particles but a constant grain size would \deleted{be} exhibit a forward scattering in the first principal component because the forward scattering flux would scale proportionally with the number of particles and transit depth.
 The implication of the PCA then is that the dust particle sizes may be changing with time.
@@
 
-We suspect that sublimating asteroids around WD1145+017, the \sha\ and K2-22 b have long term behavior determined by surface features.
+We suspect that sublimating asteroids around WD1145+017, \sha\ and K2-22 b have long term behavior determined by surface features.
 If alternating layers of rocky material have different composition, sublimation temperatures or albedos, they could provide a natural way to regulate the sublimation rate of the surface.
@@
 \citet{vanlieshout2016kic1255} suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
-If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
+If true, high resolution spectra would be \added{a} valuable tool to study the composition and dynamics of the material escaping \sha.
 In this section, we analyze archival high resolution spectra to put new constraints on the stellar temperature and surface gravity.
@@
 After initial constraints on the models from the sensitivity to parameters search, we downloaded a grid of BOSZ models with effective temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
-We found the model with the  $\chi^2$ statistic over the Mg I triplet lines from 5160 to 5190 $\AA$
+We found the model with the  $\chi^2$ statistic over the Mg I triplet lines from 5160 to 5190 $\AA$.
 The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T$_\mathrm{eff}$=4500 K, Log(g)=4.5, [M/H]=0.0, [C/M]=0.0, $\alpha=-0.25$.
@@
 We note that the exact stellar model used is less important than finding a function to fit the Spectral Energy Distribution.
-When inverting the Stefan-Boltzman law, we assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting in Section \ref{sec:SpecMatch-Emp} and a photometric error of 5\%, assumed to be dominated by photometric systematics.
+When inverting the Stefan-Boltzman law, we assume an effective temperature of 4440 $\pm$ 70 K from our spectral fitting in Section \ref{sec:SpecMatch-Emp} and a photometric error of 5\%, assumed to be dominated by photometric systematics.
 Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
@@
 Polar spots are indeed observed on rapidly rotating stars via Doppler imaging \citep{strassmeier2009starspots}; however, one would be unlikely on \sha, given its relatively long rotation period.
-Additionally, the large physical size of \sha, as indicated by a transit duration longer than the time to cross the star, meaning that spots are likely to be crossed and thus diminish the transit source effect further.
+Additionally, the large physical size of \sha's tail, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and this diminishes the transit source effect further.
 In this light, \sha's $\sim$30\% observed transit depth variation at a $\sim$ 22 day period would require a pathological distribution of magnetically active regions to be explained by un-occulted spots.
@@
 Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
-\added{This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
+\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
+\added{Thanks to Ben Weiner for some useful discussion on high resolution spectroscopy.
+This work was supported by the Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
 Support for this work was provided by NASA through Hubble Fellowship grant HST-HF2-51399.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.}
-\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
 \added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.

### 2018-10-13 ms.tex
Re-submission to AAS Journals (AJ) after tweaking first sentence of abstract.

@@
 \begin{abstract}
-KIC 12557548 b is first of a growing class of intriguing disintegrating planet candidates, which lose mass in the form of \added{a metal rich vapor that condenses into} dust particles escaping their surface.
+KIC 12557548 b is first of a growing class of intriguing disintegrating planet candidates, which lose mass in the form of \added{a metal rich vapor that condenses into} dust particles \deleted{escaping their surface}.
 Here, we follow up two perplexing observations of the system: 1) the transits appeared shallower than average in 2013 and 2014 and 2) the parameters derived from a high resolution spectrum of the star differed from other results using photometry and low resolution spectroscopy.

### 2018-11-11 ms.tex
Kite referece, updated authors, affiliations and figure sizes to match arXiv version.

@@
 
-\author{E. Schlawin}
+\author[0000-0001-8291-6490]{Everett Schlawin}
 \affiliation{Steward Observatory, Tucson AZ 85721}
@@
 
-\author{Hajima Kawahara}
+\author{Hajime Kawahara}
 \affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan}
+\affiliation{Research Center for the Early Universe, School of Science, The University of Tokyo, Tokyo 113-0033, Japan}
 
@@
 
-\author{Elizabeth Green}
+\author{Elizabeth M. Green}
 \affiliation{Steward Observatory, Tucson AZ 85721}
 
-\author{Benjamin V. Rackham}
+\author[0000-0002-3627-1676]{Benjamin V. Rackham}
 \affiliation{Steward Observatory, Tucson AZ 85721}
+\affiliation{Earths in Other Solar Systems Team, NASA Nexus for Exoplanet System Science.}
 
@@
 
-\begin{deluxetable}{lrrrr}
+\begin{deluxetable*}{lrrrr}
 \tablecaption{List of photometric observations}\label{tab:photSummary}
@@
 The seeing is expressed as the median FWHM for the night in arcseconds.}
-\end{deluxetable}
+\end{deluxetable*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{centering}
@@
 This is much longer than the dynamical and sublimation times of the system, so there is no obvious mechanism for the dust grain size evolution.
+\added{However, this timescale is close to the overturning timescale for a magma pool \citep{kite2016atmInteriorExchange}, which could control the source of metal rich vapor that creates grains.} 
 It is also possible that red noise such as 1/$f$ noise contributes to these long term oscillations.
@@
 
-\begin{deluxetable}{cccccccc}
+\begin{deluxetable*}{cccccccc}
 \tablecaption{List of Spectroscopic Observations}
@@
 \tablenotetext{}{Observing log of the Subaru HDS spectroscopic observations.}\label{tab:specObs}
-\end{deluxetable}
+\end{deluxetable*}
 
@@
 This publication makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.}
+The results reported herein benefited from collaborations and/or information exchange within NASA?s Nexus for Exoplanet System Science (NExSS) research coordination network sponsored by NASA?s Science Mission Directorate.
 
